### 2023-12-07 analysis/new_analysis.qmd
new analysis

---
title: "Horse Racing Analysis"
author: "MC"
format:
  html:
    theme: flatly
    date: last-modified
    smooth-scroll: true
    cap-location: top
    code-fold: true
execute:
  warning: false
---

This is a quick attempt to (re-)analyse the horse-racing data from Badaya, Hartsuiker, Corley.  Prompted by the fact that Espe's original analysis (see [github.com/erbadaya/horse-race-task](https://github.com/erbadaya/horse-race-task)) produced a graph that looked like an interaction, but the analysis suggested that there were only main (or simple?) effects.

## Setup, Data Wrangling

All parts of this analysis are loosely based on Espe's code.  Here we load some relevant libraries, read in the experimental data, and get it broadly into shape.

```{r}
#| label: setup
library(tidyverse)
library(lme4)
library(here)

rawData <- here("data/horse_race_exp1_rawdata.csv")
df <- read_csv(rawData) |> select(-`...1`)

# function to ensure we have up-to-date bets for all horses

df_cond <- df |>
  filter (overbet=="no") |>
  select(ppt,horse,delivery,speaker) |>
  mutate(horseN=rep(c("horse0","horse1","horse2","horse3"),max(ppt)))

df_money <- df |> select(ppt,starts_with("horse")) |>
  group_by(ppt) |>
  filter(row_number()==1) |> select(-horse) |>
  pivot_longer(cols=starts_with("horse"),names_to="horseN",values_to="BET")

df_ready <- left_join(df_cond,df_money)
```
OK, so (see code above) `df_ready` is now a simple dataframe with the betting data.

We have to parse the questionnaire data, at least to take out people with dodgy audio(?) and also those highly familiar with horse-racing.  At the moment I'm not going to attempt a full analysis of the questionnaire data.  So to match Espe's criteria, we need to identify the questionnaire responses with "naturalness" in them, and extract scores for 3 values I think:  `naturalness_native`, `naturalness_nonnative`, and `P1_Q5` which is apparently betting expertise.

```{r}

rPatterns <- c(
  '.*P1_Q5":',
  gambling='\\d+',
  '.*naturalness_native":',
  natnat='\\d+',
  '.*naturalness_nonnative":',
  natnon='\\d+',
  '.*'
)

df_q <- df |> filter(str_detect(response,"country_native")) |>
  select(ppt,response) |>
  separate_wider_regex(response,patterns=rPatterns)

df_q <- df_q |> mutate(
  outAudio=ifelse(natnat<4 | natnon <4,"OUT","in"),
  outBetting=ifelse(gambling > 3, "OUT", "in")) |>
  select(-c(gambling,natnat,natnon))

```

Now we need to take out the 9 participants identified by Espe from comments:

```{r}
df_q <- df_q |> mutate(
  outVarious=case_when(
    ppt == 12 ~ "OUT", 
    ppt == 23 ~ "OUT",
    ppt == 40 ~ "OUT", 
    ppt == 46 ~ "OUT", 
    ppt == 279 ~ "OUT", 
    ppt == 334 ~ "OUT", 
    ppt == 505 ~ "OUT", 
    ppt == 586 ~ "OUT", 
    ppt == 617 ~ "OUT",  
    TRUE  ~ "in"
  )
)
```

> `r sum(df_q$outAudio=='OUT')` participants were excluded from
> the analysis because
> they detected that the audio had been manipulated.
> A further `r sum(df_q$outBetting=='OUT' & df_q$outAudio!='OUT')` were
> removed due to expertise in horse racing.
> 
> Finally, `r sum(df_q$outVarious=='OUT' & df_q$outBetting!='OUT' & df_q$outAudio!='OUT')` additional
> participants were removed because their feedback
> suggested that they had responded strategically during the
> study.

Last bit of data-munging: Remove participants from the "master" dataframe, and set contrasts for the experimental conditions.

```{r}
df_ready <- left_join(df_ready,df_q)
df_ready <- df_ready |> filter(outAudio=='in' &
                               outBetting=='in' &
                               outVarious=='in') |>
  select(-starts_with("out"))

df_ready <- df_ready |> mutate(delivery=factor(delivery,levels=c('fluent','disfluent')),
       speaker=factor(speaker)) # native comes before non
contrasts(df_ready$delivery) <- c(-.5,5)
contrasts(df_ready$speaker) <- c(-.5,5)
```

Finally, make one more column which is a "normalised bet" column (we act as if everyone had bet out of 100).

**In doing this, I noticed that (at least) one participant had bet zero on all horses, so let's remove them.**

```{r}
df_ready <- df_ready |> group_by(ppt) |>
  mutate(sum=sum(BET)) |> ungroup()

p_gone=sum(df_ready$sum==0)/4

df_ready <- df_ready |> filter(sum>0) |>
  select(-sum) |>
  group_by(ppt) |> mutate(BET100=BET*100/sum(BET))
```

> `r p_gone` remaining participants bet no money on any horse, and were removed
> from the analysis.

## Results!

Now draw a graph.  NB., we have two options here:  Either we scale up all of the bets so that they're "out of 100" or we leave as-is.  Starting with as-is:

```{r}
df_ready |> ggplot(aes(x=delivery,y=BET100,fill=speaker)) +
  geom_bar(position="dodge",stat="summary",fun.y="mean")
```

### 2023-12-15 analysis/new_analysis.qmd
ready for merge

@@
     code-fold: true
+    embed-resources: true
 execute:
@@
 library(tidyverse)
-library(lme4)
+#library(lme4)
+library(buildmer)
 library(here)
@@
 
-Now draw a graph.  NB., we have two options here:  Either we scale up all of the bets so that they're "out of 100" or we leave as-is.  Starting with as-is:
+So I'm as sure as I can be that these data are the same (or at least created to the same standards) as Espe's.
+Now draw a graph.
+NB., we have two options here:  Either we scale up all of the bets so that they're "out of 100" or we leave as-is.
+As-is is on the left, scaled bet is on the right.
 
 ```{r}
+#| layout-ncol: 2
+
+df_plot <- df_ready |> group_by(delivery,speaker) |> summarise(mb=mean_se(BET),mb100=mean_se(BET100))
+
+df_plot |> ggplot(aes(x=delivery,y=mb$y,fill=speaker)) +
+  geom_bar(position="dodge",stat="identity") +
+  geom_errorbar(aes(ymin=mb$ymin,ymax=mb$ymax),width=.4,position=position_dodge(.9))
+df_plot |> ggplot(aes(x=delivery,y=mb100$y,fill=speaker)) +
+  geom_bar(position="dodge",stat="identity") +
+  geom_errorbar(aes(ymin=mb100$ymin,ymax=mb100$ymax),width=.4,position=position_dodge(.9))
+```
+
+Perhaps violin plots might make the distributions a bit clearer:
+
+```{r}
+#| layout-ncol: 2
+df_ready |> ggplot(aes(x=delivery,y=BET,fill=speaker)) +
+  geom_violin(alpha=.5) +
+  geom_boxplot(width=.2,position=position_dodge(.9)) 
 df_ready |> ggplot(aes(x=delivery,y=BET100,fill=speaker)) +
-  geom_bar(position="dodge",stat="summary",fun.y="mean")
+    geom_violin(alpha=.5) +
+    geom_boxplot(width=.2,position=position_dodge(.9))
 ```
+
+### Analysis
+
+Let's fit the maximal possible model to the data:
+
+```{r}
+#| output: false
+modB <- buildmer(
+  BET ~ delivery * speaker +
+    (delivery * speaker | ppt) +
+    (delivery * speaker | horse),
+  buildmerControl=buildmerControl(direction='order',
+    args=list(control=lme4::lmerControl(optimizer='bobyqa'))),
+  data = df_ready
+)
+```
+OK, so the maximal converging model is **`r deparse1(formula(modB@model))`**.  Coefficents are shown below.
+
+```{r}
+library(gtsummary)
+tbl_regression(modB@model,intercept=TRUE)
+```
+
+Now let's repeat the analysis, using the DV in which all bets are scaled to a total of 100.
+
+```{r}
+#| output: false
+modB1 <- buildmer(
+  BET100 ~ delivery * speaker +
+    (delivery * speaker | ppt) +
+    (delivery * speaker | horse),
+  buildmerControl=buildmerControl(direction='order',
+    args=list(control=lme4::lmerControl(optimizer='bobyqa'))),
+  data = df_ready
+)
+```
+
+The maximal converging model is **`r deparse1(formula(modB1@model))`**. Coefficients:
+
+```{r}
+tbl_regression(modB1@model,intercept=TRUE)
+```
+
+---
+
+That's as far as I got, but it seems to confirm Espe's original findings.  Perhaps the violin plots above give some clues as to why there is no interaction?

### 2023-12-15 analysis/new_analysis.qmd
wee typo fixed
contrast coding for .5 missing a period, now all results converge

@@
        speaker=factor(speaker)) # native comes before non
-contrasts(df_ready$delivery) <- c(-.5,5)
-contrasts(df_ready$speaker) <- c(-.5,5)
+contrasts(df_ready$delivery) <- c(-.5,.5)
+contrasts(df_ready$speaker) <- c(-.5,.5)
 ```

### 2024-09-09 manuscript/manuscript_eb.Rmd
write up & posters

---
title             : "Same as always: I suck at titles"
shorttitle        : "Horse race experiment"

author: 
  - name          : "Esperanza Badaya"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "esperanza.badaya@ugent.be"
  - name          : "Robert J. Hartsuiker"
    affiliation   : "1"
    - name          : "Martin Corley"
    affiliation   : "2"
affiliation:
  - id            : "1"
    institution   : "Department of Experimental Psychology, Ghent University, Ghent, Belgium."
  - id            : "2"
    institution   : "Department of Psychology, University of Edinburgh, Edinburgh, United Kingdom."

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Impressions of other people arise naturally and automatically [@ulemanetal2008]. Speakers can be evaluated not only by what they say but how they say it. For example, vocal features of speech can affect perceptions of confidence and persuasion [], status and solidarity [], and even attractiveness []. One repeately reported feature of speech said to bias listeners' evaluations is its fluency. Disfluencies, such as _uh_ or _um_ in English can lead to poorer evaluations of the speaker in terms of intelligence [], competence [], and certainty of their own knowledge []. Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (e.g., [], [], [], []). In this study, however, we explore a rather counterintuitive approach: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2024-09-09 manuscript/manuscript_eb.Rmd
copy & paste methods from overleaf
to do: change them to papaja

@@
 # Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+
+All experimental stimuli can be found at OSF.
 
@@
 
-## Material
+We conducted a sensitivity power analysis via data simulation following [].
+We explored the required number of participants for a study with a power higher than .8 for the interaction between fluency and speaker identity.
+We conducted a 1000 simulations per different combinations of the effect size (ranging from small to medium) and the standard deviation of the residuals.
+In this analysis, we assumed a medium effect size of fluency and no effect of speaker identity.
+This analysis showed that a sample size of 360 participants ensured enough power to detect a medium or greater effect size.
+
+In our pre-registration, we set that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study.
+Further, we would exclude from analysis data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four, or considered themselves experts in horse races.
+This meant that we recruited 641 participants for a sample of 360.
+Participants were recruited via the online platform Prolific, and were reimbursed 1.50 pounds for a 10-minutes experiment.
+
+## Visual stimuli
+
+We selected a set of eight images of racehorses from the web.
+The selected images each featured only one racehorse in the foreground, in motion, ridden by a jockey, and the horses all took up approximately the same proportion of the image.
+To ensure that the pictures did not bias participants' bets, we recruited ten participants on Prolific, who did not take part in the main study, and asked them to rate on a 10-point scale how likely each horse was to win a hypothetical race and to rank the horses in the order they thought they would cross the finish line, in exchange for 0.45 pounds.
+
+A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (F(7) = 0.5, _p_ = .83).
+An ordinal logistic regression showed that none of the horses were more likely to be ranked differently from the others (all |t| < 2).
+We therefore selected four out of the eight images as visual stimuli.
+
+## Auditory stimuli
+
+We used four descriptions of racing horses from _The Racing Post_, retrieved on October 2018, originally edited and used by [].
+Each passage consisted of three to four sentences describing a horse and its performance in previous races.
+30 British English speakers, who did not participate in the final experiment, rated these passages to ensure that all descriptions were perceived as equally likely to describe a winning horse.
+Participants rated on a 10-point scale how likely they thought each horse was to win a race individually, and then ranked all the horses, in exchange for 0.50 pounds.
+
+Based on these results, we further edited the descriptions as some descriptions were more likely to be rated as winning horses.
+A new sample fo 30 British English speaker rated the edited passages.
+A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, \textit{p} = .52), nor in the order in which they were ranked (all $|t|$ $<$ 2).
+The final set of descriptions for the experiment can be found in Table \ref{tab:Horse descriptions}.
+Each description was paired with one of the four visual stimuli.
+
+We then recorded a British English native speaker and a non-native (L1: Italian) English speaker to create the auditory stimuli.
+Both speakers were female.
+Passages were recorded one at a time.
+To elicit naturally disfluent recordings, both speakers were instructed to read the passages silently and then were recorded as they tried to recall the passage from memory.
+To avoid differences between the descriptions provided by the speakers, they were allowed to look at the descriptions as they spoke if they could not remember the continuation.
+We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (see \ref{tab:Horse disfluent descriptions}).
+To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the `Tempo' function.
+The final auditory experimental stimuli consisted, for each speaker, of two descriptions of each horse (one disfluent, one fluent), resulting in sixteen recordings.
+Description, fluency, speaker, and order of presentation were counterbalanced in a Latin Square design, resulting in 24 lists.
+
+To ensure that the resulting descriptions were perceived to be natural (i.e., our edited `fluent' audios were not clearly edited) and that they were perceived as differing in fluency (i.e., disfluent and `fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
+Participants were allocated to one of the 24 experimental lists, to ensure that our validation procedure was similar to how participants encountered stimuli in the actual experiment.
+Following [] procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
+We instructed participants to rate fluency by considering silent and filled pauses, speed of speech, and repairs, and to ignore speakers' accents and the content of their speech.
+Participants additionally rated on a 9-point scale each recording's naturalness (defined as how likely it was that the audio had been recorded in one go; 1: not unlikely at all; 9: very likely), and accentedness (while ignoring the perceived speaker's proficiency in the language; 1: not accented at all, 9: very accented).
+We additionally asked participants to guess the speakers' country of origin.
+At the end of the task, participants were further asked how often they interacted with native and non-native English speakers (on a 9-point scale, 1: never, 9: always) and were allowed to report if they noticed anything odd in the auditory stimuli.
+
+Table \ref{tab:means_validation} shows the means (and standard deviations) of participants' ratings of fluency, naturalness, and accentedness.
+A linear mixed model for fluency ratings with fixed effects of fluency, speaker's linguistic background, and their interaction, with random intercepts by participant and by horse description showed that fluency ratings differed significantly for the fluent and disfluent conditions ($\beta$ = 1.19, SE = 0.34, t = 3.52).
+The non-native speaker was perceived as more disfluent than the native speaker ($\beta$ = -1.23, SE = 0.34, t = -3.64, in line with previous findings, (e.g.,{pingetetal2014, boskeretal2014b}), but the interaction between the two variables was not significant ($\beta$ = -0.15, SE = 0.48, t = -0.31).
+An identical model for naturalness ratings showed no significant differences by fluency ($\beta$ = -0.29, SE = 0.41, t = -0.71), speaker's linguistic background ($\beta$ = 0.10, SE = 0.41, t = 0.26) or their interaction ($\beta$ = 0.40, SE = 0.58, t = 0.69).
 
 ## Procedure
+
+Stimuli were presented using JsPsych [], hosted on MindProbe (via JATOS, []).
+The task began with a cover story introducing two horse racing tipsters.
+Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race at Musselburgh Racecourse (Edinburgh).
+The cover story explained that the two tipsters were well-known experts in the field, and added that one of the speakers was a non-native English speaker (without specifying the nationality of either speaker), introducing the element of the speakers' linguistic backgrounds as well as the factor of competence.
 
@@
 # Results
+
+## Pre-registered analyses
+
+### Betting behaviour
+
+### Language attitudes
+
+## Exploratory analysis
+
+### Learning preference
 

### 2024-09-12 analysis/data-analysis.R
analysis updates

@@ -1,0 +1,270 @@
+# Note: if running on its own, remove one period
+# Otherwise, it is set for running on the manuscript
+source('../analysis/data-wrangling.R')
+
+
+library(psych)
+library(optimx)
+library(gt)
+library(gtsummary)
+library(webshot2)
+
+
+###### PRE-REGISTERED ANALYSIS ######
+
+# 12/09/2024
+# Change in code: R bug whereby using formula in t.test forces you to drop paired
+# Formula is for unpaired t-test, S3 method is for paired
+# See here: https://github.com/insightsengineering/cardx/issues/56
+
+# 1st: Explore and report behavioural data that is not directly related to our question 
+# Dimensions to compare: naturalness, accentedness, trustworthy, fluency, comprehensibility, exposure to non-native speaker
+
+langatt_native <- dexp1lang_prereg %>% filter(speaker == "native")
+langatt_nonnative <-dexp1lang_prereg %>% filter(speaker == "nonnative")
+
+t.test(langatt_native$trustworthy, langatt_nonnative$trustworthy, paired = TRUE) # trustworthiness
+t.test(langatt_native$easy, langatt_nonnative$easy, paired = TRUE) # comprehensibility, 'how easy is to comprehend this speaker'
+t.test(langatt_native$naturalness, langatt_nonnative$naturalness, paired = TRUE) # naturalness of the audio
+t.test(langatt_native$strong, langatt_nonnative$strong, paired = TRUE) # accent, 'how strong was this speaker's accent'
+t.test(langatt_native$fluent, langatt_nonnative$fluent, paired = TRUE) # fluency
+t.test(langatt_native$exposure, langatt_nonnative$exposure, paired = TRUE) # exposure to native and non-native speakers in daily life
+
+# RQ: Does money bet differ depending on manner of delivery and speaker's linguistic background?
+## exp1_mdlbet runs fine, but NB it misses a random intercept by-participant, which should be included
+## log: 07/11/2023
+## not modelling random intercept-by participant (previous model run with variance 0) because everyone is betting the 100
+## so the average is 25
+## fix: do not include it
[…]

### 2024-09-12 analysis/data-analysis_exp1.R

@@ -1,216 +1,0 @@
-source('./analysis/data-wrangling.R')
-
-
-library(psych)
-library(optimx)
-library(gt)
-library(gtsummary)
-library(webshot2)
-
-
-###### PRE-REGISTERED ANALYSIS ######
-
-# 1st: Explore and report behavioural data that is not directly related to our question 
-# Dimensions to compare: naturalness, accentedness, trustworthy, fluency, comprehensibility, exposure to non-native speaker
-
-t.test(trustworthy ~ speaker, data = dexp1lang_prereg, paired = FALSE) # trustworthiness
-t.test(easy ~ speaker, data = dexp1lang_prereg, paired = FALSE) # comprehensibility, 'how easy is to comprehend this speaker'
-t.test(naturalness ~ speaker, data = dexp1lang_prereg, paired = FALSE) # naturalness of the audio
-t.test(strong ~ speaker, data = dexp1lang_prereg, paired = FALSE) # accent, 'how strong was this speaker's accent'
-t.test(fluent ~ speaker, data = dexp1lang_prereg, paired = FALSE) # fluency
-t.test(exposure ~ speaker, data = dexp1lang_prereg, paired = FALSE) # exposure to native and non-native speakers in daily life
-
-# RQ: Does money bet differ depending on manner of delivery and speaker's linguistic background?
-## exp1_mdlbet runs fine, but NB it misses a random intercept by-participant, which should be included
-## log: 07/11/2023
-## not modelling random intercept-by participant (previous model run with variance 0) because everyone is betting the 100
-## so the average is 25
-## fix: do not include it
-## additionally: we want to model nonetheless the variance by effect
-## lme4 does not work well with sum coding, RSO stats UGent offers the following alternative:
-
-
-dexp1bet_prereg$flue_nat <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
-                                      dexp1bet_prereg$speaker == "native")
-dexp1bet_prereg$flue_non <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
-                                      dexp1bet_prereg$speaker == "nonnative")
-dexp1bet_prereg$dis_nat <- 1 * (dexp1bet_prereg$delivery != "fluent" & 
[…]

### 2024-09-12 analysis/data-visualization.R

@@ -1,5 +1,7 @@
-source('./analysis/data-wrangling.R')
-source('./analysis/utils.R') # for violin plot graphs
+# Note: if running on its own, remove one period
+# Otherwise, it is set for running on the manuscript
+source('../analysis/data-wrangling.R')
+source('../analysis/utils.R') # for violin plot graphs
 
 library(psych)
 library(optimx)
@@ -15,57 +17,67 @@ library(wesanderson)
 
 # questionnaire data
 # avg and sd of language attitudes dimensions, naturalness, accentedness, fluency, trustworthiness, ease of understanding, exposure to native and non-native speakers
-
-tab_exp1descriptive <- dexp1lang_prereg %>%
+# papaja and gt are not friends
+# re doing this code to be able to use apa_table and also to refer to it in-text
+tab5 <- dexp1lang_prereg %>%
   select(c(18:24,38,39)) %>% mutate(speaker = ifelse(speaker=='native', 'Native Speaker', 'Non-native Speaker')) %>%
   rename_with(str_to_title) %>%
   select(c("Speaker", "Easy", "Strong", "Affect", "Status", "Solidarity", "Trustworthy")) %>%
   rename(Comprehensibility = Easy,
          Accentedness = Strong
          ) %>%
-  tbl_summary(
-    by = Speaker,
-    statistic = list(
-      all_continuous() ~ "{mean} ({sd})"
-    ),
-    digits = all_continuous() ~ 2,
-    type = c(Comprehensibility = "continuous", Accentedness = "continuous", 
-             Affect = "continuous", Status = "continuous", Solidarity = "continuous", Trustworthy = "continuous") # just for testing the table
-  )%>% modify_header(label = "**Dimension**") %>% as_gt() %>%
-  tab_options(
-    table.border.top.color = "white",
-    heading.title.font.size = px(16),
-    column_labels.border.top.width = 3,
-    column_labels.border.top.color = "black",
-    column_labels.border.bottom.width = 3,
-    column_labels.border.bottom.color = "black",
-    table_body.border.bottom.color = "black",
-    table.border.bottom.color = "white",
-    table.width = pct(100),
-    table.background.color = "white",
-    column_labels.text_transform = 'capitalize'
-  ) %>%
-  cols_align(align="center") %>%
-  tab_style(
-    style = list(
[…]

### 2024-09-12 analysis/data-wrangling.R

@@ -47,7 +47,7 @@ library(here)
 
 # load all anonymised data
 
-dexp1 <- read_csv("./data/exp1/horse_race_exp1_rawdata.csv") %>% select(-c(1))
+dexp1 <- read_csv("../data/exp1/horse_race_exp1_rawdata.csv") %>% select(-c(1))
 
 # wrangle separately bet data from questionnaire data
 
@@ -178,9 +178,9 @@ dexp1survey <- dexp1survey %>%
 # PUT ALL INFO IN ONE DF
 # for filtering & analyses
 
-dexp1lang <- left_join(dexp1lang, dexp1survey, by = 'ppt')
+dexp1lang <- left_join(dexp1lang, dexp1survey, by = 'ppt', relationship = "many-to-many")
 dexp1lang <- dexp1lang %>%  filter(speaker.x == speaker.y) %>% mutate(speaker = speaker.x) %>% select(!c(speaker.x, speaker.y))
-dexp1bet <- left_join(dexp1bet, dexp1lang, by = c('ppt'))
+dexp1bet <- left_join(dexp1bet, dexp1lang, by = c('ppt'), relationship = "many-to-many")
 dexp1bet <- dexp1bet %>% filter(speaker.x == speaker.y) %>% mutate(speaker = speaker.x) %>% select(!c(speaker.x, speaker.y))
 
 

### 2024-09-12 manuscript/manuscript_eb.Rmd
manuscript
up to discussion

@@
     affiliation   : "2"
+
 affiliation:
   - id            : "1"
-    institution   : "Department of Experimental Psychology, Ghent University, Ghent, Belgium."
+    institution   : "Ghent University"
   - id            : "2"
-    institution   : "Department of Psychology, University of Edinburgh, Edinburgh, United Kingdom."
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+    institution   : "University of Edinburgh"
 
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-  One or two sentences to put the results into a more **general context**.
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+  Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the situational (e.g, who is speaking) to the ephemeral (e.g., how they speak).
+Listeners are more likely to evaluate non-native speakers as less veracious, more deceiving, and evaluate the speaker as less competent.
+Similar judgements are elicited by how fluent speech is: Filled pauses, such as _uh_ or _um_ in English, elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge.
+Interestingly, the co-existence of these two cues has been shown to yield, sometimes, different processes.
+However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear.
+In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge.
+This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous.
+Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness.
+Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.
 
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
+keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
 wordcount         : "X"
 
-bibliography      : "r-references.bib"
+bibliography      : "references.bib"
 
-floatsintext      : no
+floatsintext      : yes
 linenumbers       : yes
@@
 library("papaja")
-r_refs("r-references.bib")
+library("tidyverse")
+library("lme4")
+library("gt")
+library("gtsummary")
+r_refs("references.bib")
 ```
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
+knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
 ```
@@
 Speakers can be evaluated not only by what they say but how they say it.
-For example, vocal features of speech can affect perceptions of confidence and persuasion [], status and solidarity [], and even attractiveness [].
-One repeately reported feature of speech said to bias listeners' evaluations is its fluency.
-Disfluencies, such as _uh_ or _um_ in English can lead to poorer evaluations of the speaker in terms of intelligence [], competence [], and certainty of their own knowledge [].
-Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (e.g., [], [], [], []).
-In this study, however, we explore a rather counterintuitive approach: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually.
+For example, vocal features of speech can affect perceptions of confidence and persuasion [@guyeretal2019speech], status and solidarity [@pittamgallois198], and even attractiveness [@feinbergetal2005].
+One repeatedly reported feature of speech said to bias listeners' evaluations is its fluency.
+Disfluencies, such as _uh_ or _um_ in English can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995].
+Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility [@gluszeketal2011; @gluszekdovidio2010; @rakicetal2011; @levarikeysar2010].
+In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually.
+It is important to note that it is not our interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
+
+There is a growing body of literature showing that listeners speech qualities are taken as reflective of a speaker's knowledgeability.
+Voices with a slow speech rate, low amplitude and a large F0 range are more likely to be rated as less confident, and produce distinct neural responses [@jiangpell2015; @jiangpell2016a; @jiangpell2016b].
+Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically [@goupiletal2021].
+These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies [@shribergetal1997; @shriberglickley1993; @grosjeandeschamps1975; @jiangpell2017].
+@brennanwilliams1995 demonstrated that filled pauses (e.g., uh, mm, or um) can be perceived as indices of speakers’ confidence in their knowledge.
+In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., _feeling of another's knowing_, FOAK.
+Amongst the cues that biased participants' assessments were filled pauses:  Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers’ reduced certainty about their knowledge.
+In contrast, non-answers (i.e., 'I don’t know') were more likely to receive a higher FOAK rating if preceded by a filled pause.
+@brennanwilliams1995 took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question [see also @smithclark1993].
+
+However, certain speech qualities can yield negative evaluations without being explicitly associated with those.
+One consistent finding is that speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., [@dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010].
+This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].
+Alternatively, but not exclusively, it is possible that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018].
+This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted.
+Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker.
+In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], why a statement is believed to be underinformative [@fairchildpapafragou2018; @fairchildetal2020; @lorenzonietal2022; @ippapafragou2022] and why non-native speech is processed shallower [@levarikeysar2012; @hanulikovetal2012].
+
+Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted.
+However, stereotypes on linguistic competence may also affect how speech is delivered.
+In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived [@jiangetal2019; @caballeropell2020].
+Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listenes [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
+This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014].
+
+Recently, @matzingeretal2023 explored whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers.
+In their study, participants listened to native and non-native speakers answer trivial questions and requests, and were explicitly asked to rate the speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
+Crucially, @matzingeretal2023 manipulated speakers' fluency by having answers prefaced with either short (200 ms) or long (1200 ms) pauses.
+For requests, long pauses were less likely to be associated with unwillingness for non-native compared to native speakers.
+However, FOAK ratings did not differ between speakers: Long pauses produced by either speaker were likely to be taken as reflecting low confidence and low knowledge.
+@matzingeretal2023 attribute this pattern to different conversational contexts: Requests tap into speakers' cooperativeness, and thus in this context, tuning to the interlocutor's mental state and stereotyping might be more relevant than evaluating the speaker's competence (i.e., knowledge).
+
+To date, most experimental evaluations of manner of speech have been explicit.
+Participants are asked to rate particular traits of speakers on a scale.
+Further, these ratings are elicited in non-social contexts, where participants do not have anything at stake.
+Although these experiments demonstrate that listeners show sensitivity to aspects of speech such as fluency and accent when asked to make explicit judgements about the speaker, they may not explain how listeners evaluate speech implicitly, when to do so is consequential.Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm.
+In this task, participants listen to a set of speakers provide descriptions of horses and are asked to distribute virtual tokens as 'bets' on each horse's likelihood of winning a putative race.
+This approach presents two advantages over previous experiments.
+First, in the horse-race paradigm, participants are not explicitly asked to evaluate a certain trait of the speaker (in this case, how knowledgeable they are).
+Instead, we take participants' allocations of `betting money' as an indirect measurement of their perceptions of speakers' knowledge.
+Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets [@butterworth2019].
+Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing).
+
+In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency and the speaker's identity as conveyed by their accent.
+We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently.
+If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners’ lower FOAK for the speaker.
+However, disfluent descriptions provided by a non-native speaker may not impact listeners’ betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker’s knowledge.
+To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker [see @dragojevicgiles2016], perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived reliability of each speaker.
+We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements [@boduchlevari2021].
 
@@
 
-All experimental stimuli can be found at OSF.
+All experimental stimuli can be found at https://osf.io/zsut7/.
 
@@
 
-We conducted a sensitivity power analysis via data simulation following [].
+We conducted a sensitivity power analysis via data simulation following @debruinebarr2021.
 We explored the required number of participants for a study with a power higher than .8 for the interaction between fluency and speaker identity.
@@
 This meant that we recruited 641 participants for a sample of 360.
-Participants were recruited via the online platform Prolific, and were reimbursed 1.50 pounds for a 10-minutes experiment.
+Participants were recruited via the online platform Prolific, and were reimbursed £1.50 for a 10-minutes experiment.
 
@@
 The selected images each featured only one racehorse in the foreground, in motion, ridden by a jockey, and the horses all took up approximately the same proportion of the image.
-To ensure that the pictures did not bias participants' bets, we recruited ten participants on Prolific, who did not take part in the main study, and asked them to rate on a 10-point scale how likely each horse was to win a hypothetical race and to rank the horses in the order they thought they would cross the finish line, in exchange for 0.45 pounds.
+To ensure that the pictures did not bias participants' bets, we recruited ten participants on Prolific, who did not take part in the main study, and asked them to rate on a 10-point scale how likely each horse was to win a hypothetical race and to rank the horses in the order they thought they would cross the finish line, in exchange for £0.45.
 
@@
 
-We used four descriptions of racing horses from _The Racing Post_, retrieved on October 2018, originally edited and used by [].
+We used four descriptions of racing horses from _The Racing Post_, retrieved on October 2018, originally edited and used by @butterworth2019.
 Each passage consisted of three to four sentences describing a horse and its performance in previous races.
 30 British English speakers, who did not participate in the final experiment, rated these passages to ensure that all descriptions were perceived as equally likely to describe a winning horse.
-Participants rated on a 10-point scale how likely they thought each horse was to win a race individually, and then ranked all the horses, in exchange for 0.50 pounds.
+Participants rated on a 10-point scale how likely they thought each horse was to win a race individually, and then ranked all the horses, in exchange for £0.50.
 
@@
 A new sample fo 30 British English speaker rated the edited passages.
-A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, \textit{p} = .52), nor in the order in which they were ranked (all $|t|$ $<$ 2).
-The final set of descriptions for the experiment can be found in Table \ref{tab:Horse descriptions}.
+A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, _p_ = .52), nor in the order in which they were ranked (all |t| <$ 2).
+The final set of descriptions for the experiment can be found in Table \@ref(tab:tab-horse-description-text).
 Each description was paired with one of the four visual stimuli.
+
+```{r tab-horse-description-text}
+
+tab1A <- data.frame(
+    Horse = c("Fire Walker", "Silver Sky", "Apocalypse", "Black Blade"),
+    Description = c("Fire Walker is looking strong thanks to his come-from-behind success in the Acomb Stakes.
+The impression given in both runs is that Fire Walker should handle the demands of the extra furlong and Charlie Hills is looking forward to the test.
+The trainer said ''He's done really well for a little break, his work's been good and I couldn't be more pleased with him''.",
+    "Silver Sky, a runner-up of a seven-furlong maiden at Naas on his debut last month, the son of Invincible Spirit ran crack French colt Persian King to a neck in the Group 3 Autumn Stakes over today's trip at Newmarket two weeks ago and his trainer believes he has done well since.
+O'Brien said ''Silver Sky is a fine big colt and a talented one''.",
+    "Apocalypse has put in a string of consistent performances, most recently finishing third to Norway in the Zetland.
+''He's had a very solid year'' said trainer Archie Watson.
+''He ran a good race in the Zetland, beaten only a length and a quarter, and I think the field here is of a similar level so I'm more than happy for him to take his chance''.",
+    "Black Blade proved the market all wrong as the complexion of the 6.5-furlong novice race changed dramatically in the final two furlongs, with the Rebel Racing premier-owned newcomer under Tom Queally collaring long-time leaded Monsieur Noir.
+Spencer said: ''He did it well.
+He's a nice horse.
+We always thought had a bright future''.")
+  )
+
+apa_table(
+  tab1A,
+  caption = "Original description of each horse that speakers were asked to memorise and reproduce.",
+  align = c("m{2cm}", "m{13cm}")
+)
+
+```
 
@@
 To avoid differences between the descriptions provided by the speakers, they were allowed to look at the descriptions as they spoke if they could not remember the continuation.
-We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (see \ref{tab:Horse disfluent descriptions}).
-To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the `Tempo' function.
+We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (see Table \@ref(tab:tab-horse-description-disfluent)).
+To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the 'Tempo' function.
 The final auditory experimental stimuli consisted, for each speaker, of two descriptions of each horse (one disfluent, one fluent), resulting in sixteen recordings.
@@
 
-To ensure that the resulting descriptions were perceived to be natural (i.e., our edited `fluent' audios were not clearly edited) and that they were perceived as differing in fluency (i.e., disfluent and `fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
+```{r tab-horse-description-disfluent}
+
+tab1A <- data.frame(
+    Horse = c("Fire Walker", "Silver Sky", "Apocalypse", "Black Blade"),
+    Description = c("FP-um Fire Walker is looking SP strong thanks to his (elongation) SP come-from-behind success SP FP-er in the Acomb Stakes.
+FP-um The (elongation) impression given SP in both runs FP-uh is that Fire Walker should SP handle the demands of SP the extra furlong and FP-uh Charlie Hills is looking forward to the test.
+The trainer said ''He's done (elongation) FP-um really well for a little break, FP-uh his work's been good and I couldn't be more pleased with him''.",
+    "Silver Sky, FP-uh a runner-up of -a seven-furlong maiden at Naas on his (elongation) debut last month.
+FP-uh The son of Invincible Spirit SP  ran (elongation) crack French colt Persian King   to a neck in the FP-uh  Group 3 Autumn Stakes.
+over today's trip at Newmarket two weeks ago FP-uh and his trainer believes he has done well since.
+O'Brien said FP-uh ''Silver Sky is a fine big colt and a talented one''.",
+    "FP Apocalypse has put in a (elongation-ish) string SP of consistent performances, FP most recently finishing third to SP Norway in the Zetland.
+FP ''He's had a very solid year'' said trainer SP FP Archie Watson.
+''He ran a SP good race in the Zetland, SP FP SP beaten only a length and a quarter, and I think the field here SP is of a similar level so I'm- I'm more than happy for him to (elongation-ish) take his chance''.",
+    "FP-um Black SP Blade proved SP FP-uh the market all wrong as the complexion SP of the 6.5 furlong SP novice SP race FP-um changed dramatically in SP the final two furlong.
+SP FP-uh with the  Rebel Racing SP premier-owned SP newcomer under Tom SP Queally FP-um SP collaring long-time leaded Monsieur Noir.
+FP-uh Spencer said: ''He did it well.
+FP-uh He's a nice horse.
+FP-uh We always thought he had a bright future''.")
+  )
+
+apa_table(
+  tab1A,
+  caption = "Transcription of the disfluent horse descriptions.",
+  align = c("m{2cm}", "m{13cm}")
+)
+
+```
+
+To ensure that the resulting descriptions were perceived to be natural (i.e., our edited 'fluent' audios were not clearly edited) and that they were perceived as differing in fluency (i.e., disfluent and 'fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
 Participants were allocated to one of the 24 experimental lists, to ensure that our validation procedure was similar to how participants encountered stimuli in the actual experiment.
-Following [] procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
+Following @boskeretal2014 procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
 We instructed participants to rate fluency by considering silent and filled pauses, speed of speech, and repairs, and to ignore speakers' accents and the content of their speech.
@@
 
-Table \ref{tab:means_validation} shows the means (and standard deviations) of participants' ratings of fluency, naturalness, and accentedness.
-A linear mixed model for fluency ratings with fixed effects of fluency, speaker's linguistic background, and their interaction, with random intercepts by participant and by horse description showed that fluency ratings differed significantly for the fluent and disfluent conditions ($\beta$ = 1.19, SE = 0.34, t = 3.52).
-The non-native speaker was perceived as more disfluent than the native speaker ($\beta$ = -1.23, SE = 0.34, t = -3.64, in line with previous findings, (e.g.,{pingetetal2014, boskeretal2014b}), but the interaction between the two variables was not significant ($\beta$ = -0.15, SE = 0.48, t = -0.31).
-An identical model for naturalness ratings showed no significant differences by fluency ($\beta$ = -0.29, SE = 0.41, t = -0.71), speaker's linguistic background ($\beta$ = 0.10, SE = 0.41, t = 0.26) or their interaction ($\beta$ = 0.40, SE = 0.58, t = 0.69).
+```{r tab-results-validation}
 
-## Procedure
+dval <- read_csv('../stimuli/auditory-stimuli/validation/dval_audio.csv')
+source('../analysis/utils.R')
 
-Stimuli were presented using JsPsych [], hosted on MindProbe (via JATOS, []).
+dval <- dval %>%
+  filter(trial_type %in% c("filler", "critical"))
+
+tab2 <- dval %>%
+  filter(trial_status %in% c("fluency", "naturalness", "accentedness")) %>%
+  mutate(speaker = ifelse(speaker=='native', 'Native Speaker', 'Non-native Speaker'), delivery = ifelse(delivery=='disfluent', 'Disfluent', 'Fluent')) %>%
+  pivot_wider(names_from = trial_status, values_from = response) %>%
+  group_by(participant_ID) %>% tidyr::fill(fluency) %>% tidyr::fill(accentedness, .direction = "up") %>% ungroup() %>%
+  filter(!is.na(naturalness)==TRUE) %>%
+  rename_with(str_to_title) %>%
+  mutate(Delivery = factor(Delivery, levels = c("Fluent", "Disfluent"))) %>%
+  group_by(Speaker, Delivery) %>%
+  dplyr::summarise(
+    avg_flu = mean(as.numeric(Fluency), na.rm = TRUE),
+    sd_flu = sd(as.numeric(Fluency), na.rm = TRUE),
+    avg_nat = mean(as.numeric(Naturalness), na.rm = TRUE),
+    sd_nat = sd(as.numeric(Naturalness), na.rm = TRUE),
+    avg_acc = mean(as.numeric(Accentedness), na.rm = TRUE),
+    sd_acc = sd(as.numeric(Accentedness), na.rm = TRUE),
+  ) %>% 
+  dplyr::mutate(
+    Fluency = paste(round(avg_flu, 2), paste("(", round(sd_flu,2), ")", sep = ""), sep = " "),
+    Naturalness = paste(round(avg_nat, 2), paste("(", round(sd_nat,2), ")", sep = ""), sep = " "),
+    Accentedness = paste(round(avg_acc, 2), paste("(", round(sd_acc,2), ")", sep = ""), sep = " ")) %>%
+  select(c(Speaker, Delivery, Fluency, Naturalness, Accentedness))
+
+tab2[c(2,4), 1] <- ""
+
+apa_table(
+  tab2,
+  caption = "Mean (standard deviation) ratings of native and non-native speakers’ fluent and disfluent
+recordings for fluency, naturalness, and accentedness, on a 9-point scale where lower values indicate
+less fluent, less natural, and less accent respectively."
+)
+
+```
+```{r dval-analysis}
+
+dval <- read_csv('../stimuli/auditory-stimuli/validation/dval_audio.csv')
+dval <- dval %>%
+  filter(trial_type %in% c("filler", "critical"))
+
+# FLUENCY ANALYSIS
+
+# descriptive stats
+# ignoring horse description for now (because we are including it as random effect in our model anyways)
+
+mdl_validation_flu <- apa_print(dval %>%
+  filter(trial_status == "fluency") %>%
+  mutate(delivery = factor(delivery, levels = c("fluent", "disfluent"))) %>%
+  lmer(
+    as.numeric(response) ~ delivery * speaker +
+      (1 + delivery + speaker| participant_ID) + (1  | description),
+    data = .
+  ))
+
+# disfluent utterances are judged lower than fluent ones
+# the non-native speaker is judged as more disfluent (which partially aligns with our experiment)
+# no interaction between the two
+
+# NATURALNESS ANALYSIS
+
+# descriptive stats
+# ignoring horse description for now (because we are including it as random effect in our model anyways)
+
+# is naturalness affected by manner of delivery and speaker?
+
+mdl_validation_nat <- apa_print(dval %>%
+  filter(trial_status == "naturalness") %>%
+  mutate(delivery = factor(delivery, levels = c("fluent", "disfluent"))) %>%
+  lmer(
+    as.numeric(response) ~ delivery * speaker +
+      (1 + delivery | participant_ID) + (1 | description),
+    data = .
+  ))
+
+# disfluent utterances are judged lower than fluent ones
+# the non-native speaker is judged as more disfluent (which partially aligns with our experiment)
+# no interaction between the two
+
+```
+
+Table \@ref(tab:tab-results-validation) shows the means (and standard deviations) of participants' ratings of fluency, naturalness, and accentedness.
+A linear mixed model for fluency ratings with fixed effects of fluency (treatment-coded, reference: fluent), speaker's linguistic background (treatment-coded, reference: native speaker), and their interaction, with random intercepts by participant and by horse description showed that fluency ratings differed significantly for the fluent and disfluent conditions (`r mdl_validation_flu$full_result$deliverydisfluent`).
+The non-native speaker was perceived as more disfluent than the native speaker (`r mdl_validation_flu$full_result$speakernonnative`), in line with previous findings [@pingetetal2014; @boskeretal2014b], but the interaction between the two variables was not significant (`r mdl_validation_flu$full_result$deliverydisfluent_speakernonnative`).
+An identical model for naturalness ratings showed no significant differences by fluency (`r mdl_validation_nat$full_result$deliverydisfluent`), speaker's linguistic background (`r mdl_validation_nat$full_result$speakernonnative`) or their interaction (`r mdl_validation_nat$full_result$deliverydisfluent_speakernonnative`).
+
+# Procedure
+
+Stimuli were presented using JsPsych [@jspsych], hosted on MindProbe [via JATOS, @jatos].
 The task began with a cover story introducing two horse racing tipsters.
@@
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+At the beginning of the experiment, participants were shown four pictures of the horses that they had been told would take part in the race, alongside their names.
+Participants were instructed to distribute one-hundred pounds in betting money across the four horses based on the likelihood they thought each horse had of winning: They could split the bets as they wished, and they did not have to spend all the money.
+Each participant was randomly assigned to one out of 24 groups, so that they would listen to each speaker twice, one in each fluency level.
+The order in which horses were presented was randomised.
+In each trial, participants listened to one speaker described a given horse's performance.
+Once the playback stopped, participants were asked to place a bet by typing a number on a web form.
+Participants could only move to the next horse's description once they had placed a bet.
+Participants were allowed to modify their previous bets every time they heard a new description.
+If the sum of bets made at any point was more than the allotted maximum, they were asked to re-distribute their bets until the total was below one-hundred pounds.
 
-# Results
+After the betting round was complete, participants completed a questionnaire similar to that of @foucartetal2020 to measure their language attitudes towards the native and the non-native speaker.
+For each speaker, participants answered six questions measuring affect (three questions for negative affect and three questions for positive affect), five questions measuring solidarity, five questions measuring status, and one question each for comprehensibility, accentedness, fluency, and trustworthiness.
+Each question used a 9-point scale.
+Participants first answered questions about, at random, the native or non-native speaker, with the order of presentation of dimensions being randomised.
+They then answered the same questions for the remaining speaker.
+We also asked participants to guess the countries of origin of our native and non-native speakers, and from which speaker they would like to learn about horse races in the future.
+Additional questions included ratings on a 9-point scale of how natural the audio sounded (1: unnatural, edited; 9: natural, unedited), and two questions measuring participants' exposure to native and non-native accented English (1: never; 9: always).
+Likewise, we measured participants’ previous experience with betting and their perceived knowledge of horse races (two questions: Whether they had bet on horse races in the past, and to rate on a 5-point scale, from 'Strongly disagree' to 'Strongly agree', how closely they identified with the statement 'I am an expert on horse races').
+Finally, we included an open-ended question for participants to report what guided their decision-making, as well as their perception of the experiment's aim.
+
+## Results
+
+All data pre-processing and analyses were carried out in R version 4.4.1 [@R-base], using the packages _tidyverse_ version 2.0.0 [@tidyverse], _ggplot_ version 3.5.1 [@ggplot2], and _wesanderson_ version for data wrangling and visualization.
+_lme4_ version 1.1-35.5 [@lme4] was used for data analysis, and _papaja_ version 0.1.2 [@R-papaja] for manuscript write-up.
+Scripts can be found at https://osf.io/zsut7/
 
@@
 
+```{r include=FALSE}
+source('../analysis/data-visualization.R')
+```
+```{r tab-dist-money}
+apa_table(
+  tab4,
+  caption = "Mean (standard deviation) of money bet by manner of delivery and speaker’s linguistic
+background."
+)
+```
+```{r fig1, out.width="90%",fig.align='center', fig.cap="Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native)."}
+fig1
+```
+
+Table \@ref(tab:tab-dist-money) and Figure \@ref(fig:fig1) show the mean amount of money bet per speaker and fluency condition.
+On average, participants bet £25 on each horse.
+This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
+However, disfluent instructions seem to lower the amount of money bet.
+
+We modelled participants' betting behaviour in a linear mixed model.
+We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded.
+The model included fixed effects of fluency (sum-coded; fluent coded as -0.5, disfluent as +0.5), speaker's linguistic background (sum-coded, native coded as -0.5; non-native coded as +0.5), and their interaction.
+The maximal model [@barretal2013], with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge.
+We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept.
+The final model included a random intercept by-item.
+Results were deemed significant at |t| > 2 [@baayen2008].
+
+```{r model-bets, include=FALSE}
+source('../analysis/data-analysis.R')
+```
+
+Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (`r mdlbet_m1$full_result$delivery_cont1`).
+There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and no other significances (for speaker, `r mdlbet_m1_all$full_result$speaker_cont1`; for the interaction `r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].
+
 ### Language attitudes
+
+Table \@ref(tab:tab5) depicts the mean (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
+Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score.
+For the _Affect_ dimension, we reverse-scored items measuring negative affect.
+Cronbach's alpha showed that the scores for these attitudes were reliable ($\alpha_{affect}$ = `r affect_alpha`, $\alpha_{status}$ = `r status_alpha`, $\alpha_{solidarity}$ = `r solidarity_alpha`).
+We explored differences between the native and the non-native speaker's evaluations in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.
+
+```{r tab5}
+apa_table(tab5,
+          caption = "Average score (and standard deviation) in each dimension by speaker.")
+```
+```{r tab6}
+apa_table(tab6,
+          caption = "Paired t test for each dimension between speakers.")
+```
+
+Analyses showed that speakers were rared differently across all six dimensions (see Table \@ref(tab:tab6)).
+The largest differences were, unsurprisingly, in comprehensibility and accentedness, where the non-native speaker received lower ratings.
+
+Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours.
+This second model improved model fit ($\chi^2$(6) = 19.46, _p_ < .01).
+Besides a main effect of manner of delivery (`r mdlbet_attitudes$full_result$delivery_cont1`), the model showed an effect of affect, whereby higher ratings of affect were more likely to yield higher bettings (`r mdlbet_attitudes$full_result$affect`)
 
@@
 
-### Learning preference
+We additionally explored participants' preferences to learn from either speaker in the future.
+206 participants reported they would prefer to learn from the native spaker, and 154 preferred the non-native speaker.
+A $\chi^2$ test of goodness of fit showed that there was a significant difference in participants' preferences ($\chi^2$(1) = 7.51, _p_ < .01).
 
 # Discussion
+
+The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced [@brennanwilliams1995].
+Descriptions that included hesitation phenomena, in the form of filled pauses, led to smaller bets compared to their fluent counterparts.
+This aligns with @brennanwilliams1995 findings wherein listeners were less likely to attribute confidence in their knowledge to a speaker when their answers included hesitation phenomena (i.e., Feeling of Another's Knowing).
+Brennan and Williams (1995) attributed participants' ratings to inferences made about the speaker's mental state - specifically, inferences about the degree of confidence a speaker has in their knowledge.
+In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because the utterance is semantically and acoustically identical apart from the excision of disfluencies, an inference about a speaker's confidence based on those disfluencies is an important potential determinant of participants' decisions.
 

### 2024-09-12 manuscript/manuscript_eb.tex
manuscript
up to discussion

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Same as always: I suck at titles},
  pdfauthor={Esperanza Badaya1, Robert J. Hartsuiker1, \& Martin Corley2},
  pdflang={en-EN},
  pdfkeywords={filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Same as always: I suck at titles}
\author{Esperanza Badaya\textsuperscript{1}, Robert J. Hartsuiker\textsuperscript{1}, \& Martin Corley\textsuperscript{2}}
\date{}

\shorttitle{Horse race experiment}

\authornote{

Correspondence concerning this article should be addressed to Esperanza Badaya. E-mail: \href{mailto:esperanza.badaya@ugent.be}{\nolinkurl{esperanza.badaya@ugent.be}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Ghent University\\\textsuperscript{2} University of Edinburgh}

\abstract{%
Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the situational (e.g, who is speaking) to the ephemeral (e.g., how they speak). Listeners are more likely to evaluate non-native speakers as less veracious, more deceiving, and evaluate the speaker as less competent. Similar judgements are elicited by how fluent speech is: Filled pauses, such as \emph{uh} or \emph{um} in English, elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge. Interestingly, the co-existence of these two cues has been shown to yield, sometimes, different processes. However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear. In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge. This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous. Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness. Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.
}

\begin{document}
\maketitle

Impressions of other people arise naturally and automatically (Uleman, Adil Saribay, \& Gonzalez, 2008). Speakers can be evaluated not only by what they say but how they say it. For example, vocal features of speech can affect perceptions of confidence and persuasion (Guyer, Fabrigar, \& Vaughan-Johnston, 2019), status and solidarity (Pittam \& Gallois, 1986), and even attractiveness (Feinberg, Jones, Little, Burt, \& Perrett, 2005). One repeatedly reported feature of speech said to bias listeners' evaluations is its fluency. Disfluencies, such as \emph{uh} or \emph{um} in English can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995). Interestingly, speech produced with an accent different from one's own - particularly a \emph{foreign} accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek \& Dovidio, 2010; Gluszek, Newheiser, \& Dovidio, 2011; Lev-Ari \& Keysar, 2010; Rakić, Steffens, \& Mummendey, 2011). In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually. It is important to note that it is not our interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.

There is a growing body of literature showing that listeners speech qualities are taken as reflective of a speaker's knowledgeability. Voices with a slow speech rate, low amplitude and a large F0 range are more likely to be rated as less confident, and produce distinct neural responses (Jiang \& Pell, 2015, 2016b, 2016a). Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil, Ponsot, Richardson, Reyes, \& Aucouturier, 2021). These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg, Bates, \& Stolcke, 1997; Shriberg \& Lickley, 1993). Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) can be perceived as indices of speakers' confidence in their knowledge. In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., \emph{feeling of another's knowing}, FOAK. Amongst the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge. In contrast, non-answers (i.e., `I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause. Brennan and Williams (1995) took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question (see also Smith \& Clark, 1993).

However, certain speech qualities can yield negative evaluations without being explicitly associated with those. One consistent finding is that speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., (Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Lev-Ari \& Keysar, 2010). This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013). Alternatively, but not exclusively, it is possible that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015). This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018), why a statement is believed to be underinformative (Fairchild, Mathis, \& Papafragou, 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022) and why non-native speech is processed shallower (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listenes (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014).

Recently, Matzinger, Pleyer, and Żywiczyński (2023) explored whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers. In their study, participants listened to native and non-native speakers answer trivial questions and requests, and were explicitly asked to rate the speaker's knowledge and confidence (for FOAK) and their willingness to grant the request. Crucially, Matzinger et al. (2023) manipulated speakers' fluency by having answers prefaced with either short (200 ms) or long (1200 ms) pauses. For requests, long pauses were less likely to be associated with unwillingness for non-native compared to native speakers. However, FOAK ratings did not differ between speakers: Long pauses produced by either speaker were likely to be taken as reflecting low confidence and low knowledge. Matzinger et al. (2023) attribute this pattern to different conversational contexts: Requests tap into speakers' cooperativeness, and thus in this context, tuning to the interlocutor's mental state and stereotyping might be more relevant than evaluating the speaker's competence (i.e., knowledge).

To date, most experimental evaluations of manner of speech have been explicit. Participants are asked to rate particular traits of speakers on a scale. Further, these ratings are elicited in non-social contexts, where participants do not have anything at stake. Although these experiments demonstrate that listeners show sensitivity to aspects of speech such as fluency and accent when asked to make explicit judgements about the speaker, they may not explain how listeners evaluate speech implicitly, when to do so is consequential.Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm. In this task, participants listen to a set of speakers provide descriptions of horses and are asked to distribute virtual tokens as `bets' on each horse's likelihood of winning a putative race. This approach presents two advantages over previous experiments. First, in the horse-race paradigm, participants are not explicitly asked to evaluate a certain trait of the speaker (in this case, how knowledgeable they are). Instead, we take participants' allocations of `betting money' as an indirect measurement of their perceptions of speakers' knowledge. Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets (Butterworth, 2019). Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing).

In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency and the speaker's identity as conveyed by their accent. We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently. If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners' lower FOAK for the speaker. However, disfluent descriptions provided by a non-native speaker may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge. To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived reliability of each speaker. We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements (Boduch-Grabka \& Lev-Ari, 2021).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

All experimental stimuli can be found at \url{https://osf.io/zsut7/}.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

We conducted a sensitivity power analysis via data simulation following DeBruine and Barr (2021). We explored the required number of participants for a study with a power higher than .8 for the interaction between fluency and speaker identity. We conducted a 1000 simulations per different combinations of the effect size (ranging from small to medium) and the standard deviation of the residuals. In this analysis, we assumed a medium effect size of fluency and no effect of speaker identity. This analysis showed that a sample size of 360 participants ensured enough power to detect a medium or greater effect size.

In our pre-registration, we set that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study. Further, we would exclude from analysis data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four, or considered themselves experts in horse races. This meant that we recruited 641 participants for a sample of 360. Participants were recruited via the online platform Prolific, and were reimbursed £1.50 for a 10-minutes experiment.

\hypertarget{visual-stimuli}{%
\subsection{Visual stimuli}\label{visual-stimuli}}

We selected a set of eight images of racehorses from the web. The selected images each featured only one racehorse in the foreground, in motion, ridden by a jockey, and the horses all took up approximately the same proportion of the image. To ensure that the pictures did not bias participants' bets, we recruited ten participants on Prolific, who did not take part in the main study, and asked them to rate on a 10-point scale how likely each horse was to win a hypothetical race and to rank the horses in the order they thought they would cross the finish line, in exchange for £0.45.

A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (F(7) = 0.5, \emph{p} = .83). An ordinal logistic regression showed that none of the horses were more likely to be ranked differently from the others (all \textbar t\textbar{} \textless{} 2). We therefore selected four out of the eight images as visual stimuli.

\hypertarget{auditory-stimuli}{%
\subsection{Auditory stimuli}\label{auditory-stimuli}}

We used four descriptions of racing horses from \emph{The Racing Post}, retrieved on October 2018, originally edited and used by Butterworth (2019). Each passage consisted of three to four sentences describing a horse and its performance in previous races. 30 British English speakers, who did not participate in the final experiment, rated these passages to ensure that all descriptions were perceived as equally likely to describe a winning horse. Participants rated on a 10-point scale how likely they thought each horse was to win a race individually, and then ranked all the horses, in exchange for £0.50.

Based on these results, we further edited the descriptions as some descriptions were more likely to be rated as winning horses. A new sample fo 30 British English speaker rated the edited passages. A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, \emph{p} = .52), nor in the order in which they were ranked (all \textbar t\textbar{} \textless\$ 2). The final set of descriptions for the experiment can be found in Table \ref{tab:tab-horse-description-text}. Each description was paired with one of the four visual stimuli.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tab-horse-description-text}Original description of each horse that speakers were asked to memorise and reproduce.}

\begin{tabular}{m{2cm}m{13cm}}
\toprule
Horse & \multicolumn{1}{c}{Description}\\
\midrule
Fire Walker & Fire Walker is looking strong thanks to his come-from-behind success in the Acomb Stakes. The impression given in both runs is that Fire Walker should handle the demands of the extra furlong and Charlie Hills is looking forward to the test. The trainer said ''He's done really well for a little break, his work's been good and I couldn't be more pleased with him''.\\
Silver Sky & Silver Sky, a runner-up of a seven-furlong maiden at Naas on his debut last month, the son of Invincible Spirit ran crack French colt Persian King to a neck in the Group 3 Autumn Stakes over today's trip at Newmarket two weeks ago and his trainer believes he has done well since. O'Brien said ''Silver Sky is a fine big colt and a talented one''.\\
Apocalypse & Apocalypse has put in a string of consistent performances, most recently finishing third to Norway in the Zetland. ''He's had a very solid year'' said trainer Archie Watson. ''He ran a good race in the Zetland, beaten only a length and a quarter, and I think the field here is of a similar level so I'm more than happy for him to take his chance''.\\
Black Blade & Black Blade proved the market all wrong as the complexion of the 6.5-furlong novice race changed dramatically in the final two furlongs, with the Rebel Racing premier-owned newcomer under Tom Queally collaring long-time leaded Monsieur Noir. Spencer said: ''He did it well. He's a nice horse. We always thought had a bright future''.\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

We then recorded a British English native speaker and a non-native (L1: Italian) English speaker to create the auditory stimuli. Both speakers were female. Passages were recorded one at a time. To elicit naturally disfluent recordings, both speakers were instructed to read the passages silently and then were recorded as they tried to recall the passage from memory. To avoid differences between the descriptions provided by the speakers, they were allowed to look at the descriptions as they spoke if they could not remember the continuation. We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (see Table \ref{tab:tab-horse-description-disfluent}). To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the `Tempo' function. The final auditory experimental stimuli consisted, for each speaker, of two descriptions of each horse (one disfluent, one fluent), resulting in sixteen recordings. Description, fluency, speaker, and order of presentation were counterbalanced in a Latin Square design, resulting in 24 lists.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tab-horse-description-disfluent}Transcription of the disfluent horse descriptions.}

\begin{tabular}{m{2cm}m{13cm}}
\toprule
Horse & \multicolumn{1}{c}{Description}\\
\midrule
Fire Walker & FP-um Fire Walker is looking SP strong thanks to his (elongation) SP come-from-behind success SP FP-er in the Acomb Stakes. FP-um The (elongation) impression given SP in both runs FP-uh is that Fire Walker should SP handle the demands of SP the extra furlong and FP-uh Charlie Hills is looking forward to the test. The trainer said ''He's done (elongation) FP-um really well for a little break, FP-uh his work's been good and I couldn't be more pleased with him''.\\
Silver Sky & Silver Sky, FP-uh a runner-up of -a seven-furlong maiden at Naas on his (elongation) debut last month. FP-uh The son of Invincible Spirit SP\ \ ran (elongation) crack French colt Persian King\ \  to a neck in the FP-uh\ \ Group 3 Autumn Stakes. over today's trip at Newmarket two weeks ago FP-uh and his trainer believes he has done well since. O'Brien said FP-uh ''Silver Sky is a fine big colt and a talented one''.\\
Apocalypse & FP Apocalypse has put in a (elongation-ish) string SP of consistent performances, FP most recently finishing third to SP Norway in the Zetland. FP ''He's had a very solid year'' said trainer SP FP Archie Watson. ''He ran a SP good race in the Zetland, SP FP SP beaten only a length and a quarter, and I think the field here SP is of a similar level so I'm- I'm more than happy for him to (elongation-ish) take his chance''.\\
Black Blade & FP-um Black SP Blade proved SP FP-uh the market all wrong as the complexion SP of the 6.5 furlong SP novice SP race FP-um changed dramatically in SP the final two furlong. SP FP-uh with the\ \ Rebel Racing SP premier-owned SP newcomer under Tom SP Queally FP-um SP collaring long-time leaded Monsieur Noir. FP-uh Spencer said: ''He did it well. FP-uh He's a nice horse. FP-uh We always thought he had a bright future''.\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

To ensure that the resulting descriptions were perceived to be natural (i.e., our edited `fluent' audios were not clearly edited) and that they were perceived as differing in fluency (i.e., disfluent and `fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study. Participants were allocated to one of the 24 experimental lists, to ensure that our validation procedure was similar to how participants encountered stimuli in the actual experiment. Following Bosker, Quené, Sanders, and De Jong (2014) procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent). We instructed participants to rate fluency by considering silent and filled pauses, speed of speech, and repairs, and to ignore speakers' accents and the content of their speech. Participants additionally rated on a 9-point scale each recording's naturalness (defined as how likely it was that the audio had been recorded in one go; 1: not unlikely at all; 9: very likely), and accentedness (while ignoring the perceived speaker's proficiency in the language; 1: not accented at all, 9: very accented). We additionally asked participants to guess the speakers' country of origin. At the end of the task, participants were further asked how often they interacted with native and non-native English speakers (on a 9-point scale, 1: never, 9: always) and were allowed to report if they noticed anything odd in the auditory stimuli.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tab-results-validation}Mean (standard deviation) ratings of native and non-native speakers’ fluent and disfluent
recordings for fluency, naturalness, and accentedness, on a 9-point scale where lower values indicate
less fluent, less natural, and less accent respectively.}

\begin{tabular}{lllll}
\toprule
Speaker & \multicolumn{1}{c}{Delivery} & \multicolumn{1}{c}{Fluency} & \multicolumn{1}{c}{Naturalness} & \multicolumn{1}{c}{Accentedness}\\
\midrule
Native Speaker & Fluent & 7.62 (1.59) & 5.44 (2.62) & 4.38 (2.22)\\
 & Disfluent & 6.44 (2.36) & 5.73 (2.57) & 4 (1.97)\\
Non-native Speaker & Fluent & 6.25 (1.73) & 5.94 (1.83) & 7.02 (1.59)\\
 & Disfluent & 5.21 (1.75) & 5.83 (1.99) & 7.17 (1.51)\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

Table \ref{tab:tab-results-validation} shows the means (and standard deviations) of participants' ratings of fluency, naturalness, and accentedness. A linear mixed model for fluency ratings with fixed effects of fluency (treatment-coded, reference: fluent), speaker's linguistic background (treatment-coded, reference: native speaker), and their interaction, with random intercepts by participant and by horse description showed that fluency ratings differed significantly for the fluent and disfluent conditions (\(\hat{\beta} = -1.19\), 95\% CI \([-1.79, -0.58]\), \(t = -3.84\)). The non-native speaker was perceived as more disfluent than the native speaker (\(\hat{\beta} = -1.37\), 95\% CI \([-1.97, -0.78]\), \(t = -4.51\)), in line with previous findings (Bosker, Quené, Sanders, \& Jong, 2014; Pinget et al., 2014), but the interaction between the two variables was not significant (\(\hat{\beta} = 0.15\), 95\% CI \([-0.49, 0.78]\), \(t = 0.45\)). An identical model for naturalness ratings showed no significant differences by fluency (\(\hat{\beta} = 0.29\), 95\% CI \([-0.52, 1.11]\), \(t = 0.70\)), speaker's linguistic background (\(\hat{\beta} = 0.50\), 95\% CI \([-0.27, 1.27]\), \(t = 1.27\)) or their interaction (\(\hat{\beta} = -0.40\), 95\% CI \([-1.49, 0.70]\), \(t = -0.71\)).

\hypertarget{procedure}{%
\section{Procedure}\label{procedure}}

Stimuli were presented using JsPsych (Leeuw, Gilbert, \& Luchterhandt, 2023), hosted on MindProbe (via JATOS, Lange, Kühn, \& Filevich, 2015). The task began with a cover story introducing two horse racing tipsters. Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race at Musselburgh Racecourse (Edinburgh). The cover story explained that the two tipsters were well-known experts in the field, and added that one of the speakers was a non-native English speaker (without specifying the nationality of either speaker), introducing the element of the speakers' linguistic backgrounds as well as the factor of competence.

At the beginning of the experiment, participants were shown four pictures of the horses that they had been told would take part in the race, alongside their names. Participants were instructed to distribute one-hundred pounds in betting money across the four horses based on the likelihood they thought each horse had of winning: They could split the bets as they wished, and they did not have to spend all the money. Each participant was randomly assigned to one out of 24 groups, so that they would listen to each speaker twice, one in each fluency level. The order in which horses were presented was randomised. In each trial, participants listened to one speaker described a given horse's performance. Once the playback stopped, participants were asked to place a bet by typing a number on a web form. Participants could only move to the next horse's description once they had placed a bet. Participants were allowed to modify their previous bets every time they heard a new description. If the sum of bets made at any point was more than the allotted maximum, they were asked to re-distribute their bets until the total was below one-hundred pounds.

After the betting round was complete, participants completed a questionnaire similar to that of Foucart, Costa, Morís-Fernández, and Hartsuiker (2020) to measure their language attitudes towards the native and the non-native speaker. For each speaker, participants answered six questions measuring affect (three questions for negative affect and three questions for positive affect), five questions measuring solidarity, five questions measuring status, and one question each for comprehensibility, accentedness, fluency, and trustworthiness. Each question used a 9-point scale. Participants first answered questions about, at random, the native or non-native speaker, with the order of presentation of dimensions being randomised. They then answered the same questions for the remaining speaker. We also asked participants to guess the countries of origin of our native and non-native speakers, and from which speaker they would like to learn about horse races in the future. Additional questions included ratings on a 9-point scale of how natural the audio sounded (1: unnatural, edited; 9: natural, unedited), and two questions measuring participants' exposure to native and non-native accented English (1: never; 9: always). Likewise, we measured participants' previous experience with betting and their perceived knowledge of horse races (two questions: Whether they had bet on horse races in the past, and to rate on a 5-point scale, from `Strongly disagree' to `Strongly agree', how closely they identified with the statement `I am an expert on horse races'). Finally, we included an open-ended question for participants to report what guided their decision-making, as well as their perception of the experiment's aim.

\hypertarget{results}{%
\subsection{Results}\label{results}}

All data pre-processing and analyses were carried out in R version 4.4.1 (R Core Team, 2024), using the packages \emph{tidyverse} version 2.0.0 (Wickham et al., 2019), \emph{ggplot} version 3.5.1 (Wickham, 2016), and \emph{wesanderson} version for data wrangling and visualization. \emph{lme4} version 1.1-35.5 (Bates, Mächler, Bolker, \& Walker, 2015) was used for data analysis, and \emph{papaja} version 0.1.2 (Aust \& Barth, 2023) for manuscript write-up. Scripts can be found at \url{https://osf.io/zsut7/}

\hypertarget{pre-registered-analyses}{%
\subsection{Pre-registered analyses}\label{pre-registered-analyses}}

\hypertarget{betting-behaviour}{%
\subsubsection{Betting behaviour}\label{betting-behaviour}}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tab-dist-money}Mean (standard deviation) of money bet by manner of delivery and speaker’s linguistic
background.}

\begin{tabular}{lll}
\toprule
Speaker & \multicolumn{1}{c}{Delivery} & \multicolumn{1}{c}{Money bet}\\
\midrule
Native & Fluent & 24.24 (13.92)\\
 & Disfluent & 20.66 (12.23)\\
Non-native & Fluent & 24.15 (13.61)\\
 & Disfluent & 22.31 (13.81)\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}
\begin{figure}[H]

{\centering \includegraphics[width=0.9\linewidth,]{manuscript_eb_files/figure-latex/fig1-1}

}

\caption{Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native).}\label{fig:fig1}
\end{figure}

Table \ref{tab:tab-dist-money} and Figure \ref{fig:fig1} show the mean amount of money bet per speaker and fluency condition. On average, participants bet £25 on each horse. This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally. However, disfluent instructions seem to lower the amount of money bet.

We modelled participants' betting behaviour in a linear mixed model. We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded. The model included fixed effects of fluency (sum-coded; fluent coded as -0.5, disfluent as +0.5), speaker's linguistic background (sum-coded, native coded as -0.5; non-native coded as +0.5), and their interaction. The maximal model (Barr, Levy, Scheepers, \& Tily, 2013), with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge. We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept. The final model included a random intercept by-item. Results were deemed significant at \textbar t\textbar{} \textgreater{} 2 (Baayen, 2008).

Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)). There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\)) and importantly, no interaction between delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)), and no other significances (for speaker, \(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\); for the interaction \(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))}.

\hypertarget{language-attitudes}{%
\subsubsection{Language attitudes}\label{language-attitudes}}

Table \ref{tab:tab5} depicts the mean (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background. Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score. For the \emph{Affect} dimension, we reverse-scored items measuring negative affect. Cronbach's alpha showed that the scores for these attitudes were reliable (\(\alpha_{affect}\) = 0.80, \(\alpha_{status}\) = 0.93, \(\alpha_{solidarity}\) = 0.87). We explored differences between the native and the non-native speaker's evaluations in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for \emph{p} values.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tab5}Average score (and standard deviation) in each dimension by speaker.}

\begin{tabular}{lll}
\toprule
Dimension & \multicolumn{1}{c}{Native Speaker} & \multicolumn{1}{c}{Non-native Speaker}\\
\midrule
Comprehensibility & 7.62 (1.57) & 5.51 (2.14)\\
Accentedness & 5.46 (2.1) & 6.84 (1.37)\\
Affect & 5.77 (1.49) & 6.05 (1.32)\\
Status & 5.95 (1.52) & 6.43 (1.31)\\
Solidarity & 5.67 (1.48) & 6.41 (1.24)\\
Trustworthy & 6 (1.61) & 6.36 (1.41)\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tab6}Paired t test for each dimension between speakers.}

\begin{tabular}{llll}
\toprule
Dimension & \multicolumn{1}{c}{t(359)} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{d}\\
\midrule
Comprehensibility & 15.99 & {}[1.85, 2.36] & 2.11\\
Accent & -11.51 & {}[-1.62, -1.15] & -1.39\\
Affect & -3.54 & {}[-0.44, -0.13] & -0.29\\
Status & -6.55 & {}[-0.62, -0.33] & -0.48\\
Solidarity & -9.63 & {}[-0.89, -0.59] & -0.74\\
Trustworthy & -4.12 & {}[-0.53, -0.19] & -0.36\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

Analyses showed that speakers were rared differently across all six dimensions (see Table \ref{tab:tab6}). The largest differences were, unsurprisingly, in comprehensibility and accentedness, where the non-native speaker received lower ratings.

Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours. This second model improved model fit (\(\chi^2\)(6) = 19.46, \emph{p} \textless{} .01). Besides a main effect of manner of delivery (\(\hat{\beta} = -2.71\), 95\% CI \([-4.03, -1.39]\), \(t = -4.02\)), the model showed an effect of affect, whereby higher ratings of affect were more likely to yield higher bettings (\(\hat{\beta} = 0.81\), 95\% CI \([0.14, 1.49]\), \(t = 2.35\))

\hypertarget{exploratory-analysis}{%
\subsection{Exploratory analysis}\label{exploratory-analysis}}

We additionally explored participants' preferences to learn from either speaker in the future. 206 participants reported they would prefer to learn from the native spaker, and 154 preferred the non-native speaker. A \(\chi^2\) test of goodness of fit showed that there was a significant difference in participants' preferences (\(\chi^2\)(1) = 7.51, \emph{p} \textless{} .01).

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced (Brennan \& Williams, 1995). Descriptions that included hesitation phenomena, in the form of filled pauses, led to smaller bets compared to their fluent counterparts. This aligns with Brennan and Williams (1995) findings wherein listeners were less likely to attribute confidence in their knowledge to a speaker when their answers included hesitation phenomena (i.e., Feeling of Another's Knowing). Brennan and Williams (1995) attributed participants' ratings to inferences made about the speaker's mental state - specifically, inferences about the degree of confidence a speaker has in their knowledge. In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because the utterance is semantically and acoustically identical apart from the excision of disfluencies, an inference about a speaker's confidence based on those disfluencies is an important potential determinant of participants' decisions.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-arnoldetal2007}{}}%
Arnold, J. E., Kam, C. L. H., \& Tanenhaus, M. K. (2007). If you say thee uh you are describing something hard: The on-line attribution of disfluency during reference comprehension. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{33}(5), 914--930. \url{https://doi.org/10.1037/0278-7393.33.5.914}

\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2023). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-baayen2008}{}}%
Baayen, R. H. (2008). \emph{Analyzing linguistic data: A practical introduction to statistics using r}. Cambridge University Press. \url{https://doi.org/10.1017/CBO9780511801686}

\leavevmode\vadjust pre{\hypertarget{ref-barretal2013}{}}%
Barr, D. J., Levy, R., Scheepers, C., \& Tily, H. J. (2013). Random effects structure for confirmatory hypothesis testing: Keep it maximal. \emph{Journal of Memory and Language}, \emph{68}(3), 255--278. \url{https://doi.org/10.1016/j.jml.2012.11.001}

\leavevmode\vadjust pre{\hypertarget{ref-barrseyfeddinipur2010}{}}%
Barr, D. J., \& Seyfeddinipur, M. (2010). The role of fillers in listener attributions for speaker disfluency. \emph{Language and Cognitive Processes}, \emph{25}(4), 441--455.

\leavevmode\vadjust pre{\hypertarget{ref-lme4}{}}%
Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear mixed-effects models using {lme4}. \emph{Journal of Statistical Software}, \emph{67}(1), 1--48. \url{https://doi.org/10.18637/jss.v067.i01}

\leavevmode\vadjust pre{\hypertarget{ref-bazzietal2022}{}}%
Bazzi, L., Brouwer, S., \& Foucart, A. (2022). The impact of foreign accent on irony and its consequences on social interaction. \emph{Journal of Multilingual and Multicultural Development}, 1--13.

\leavevmode\vadjust pre{\hypertarget{ref-bergmannetal2015}{}}%
Bergmann, C., Sprenger, S. A., \& Schmid, M. S. (2015). The impact of language co-activation on {L1} and {L2} speech fluency. \emph{Acta {Psychologica}}, \emph{161}, 25--35.

\leavevmode\vadjust pre{\hypertarget{ref-boduchlevari2021}{}}%
Boduch-Grabka, K., \& Lev-Ari, S. (2021). Exposing individuals to foreign accent increases their trust in what nonnative speakers say. \emph{Cognitive Science}, \emph{45}(11), e13064. \url{https://doi.org/10.1111/cogs.13064}

\leavevmode\vadjust pre{\hypertarget{ref-boskeretal2014}{}}%
Bosker, H. R., Quené, H., Sanders, T., \& De Jong, N. H. (2014). Native `um's elicit prediction of low-frequency referents, but non-native `um's do not. \emph{Journal of Memory and Language}, \emph{75}, 104--116. \url{https://doi.org/10.1016/j.jml.2014.05.004}

\leavevmode\vadjust pre{\hypertarget{ref-boskeretal2014b}{}}%
Bosker, H. R., Quené, H., Sanders, T., \& Jong, N. H. de. (2014). The perception of fluency in native and nonnative speech. \emph{Lang. Learn.}, \emph{64}(3), 579--614. \url{https://doi.org/10.1111/lang.12067}

\leavevmode\vadjust pre{\hypertarget{ref-brennanwilliams1995}{}}%
Brennan, S. E., \& Williams, M. (1995). The feeling of another's knowing: Prosody and filled pauses as cues to listeners about the metacognitive states of speakers. \emph{Journal of Memory and Language}, \emph{34}(3), 383--398.

\leavevmode\vadjust pre{\hypertarget{ref-butterworth2019}{}}%
Butterworth, H. (2019). \emph{How much do they, um, know?: Disfluencies in speech as cues to speakers' knowledge.} University of Edinburgh.

\leavevmode\vadjust pre{\hypertarget{ref-caballeropell2020}{}}%
Caballero, J. A., \& Pell, M. D. (2020). Implicit effects of speaker accents and vocally-expressed confidence on decisions to trust. \emph{Decision}, \emph{7}(4), 314. \url{https://doi.org/10.1037/dec0000140}

\leavevmode\vadjust pre{\hypertarget{ref-caffarraetal2018}{}}%
Caffarra, S., Michell, E., \& Martin, C. D. (2018). The impact of foreign accent on irony interpretation. \emph{{PLoS} One}, \emph{13}(8), e0200939.

\leavevmode\vadjust pre{\hypertarget{ref-christenfeld1995}{}}%
Christenfeld, N. (1995). Does it hurt to say um? \emph{Journal of Nonverbal Behavior}, \emph{19}, 171--186.

\leavevmode\vadjust pre{\hypertarget{ref-davies2003}{}}%
Davies, A. (2003). \emph{The native speaker: Myth and reality} (Vol. 38). Multilingual matters. \url{https://doi.org/10.21832/9781853596247}

\leavevmode\vadjust pre{\hypertarget{ref-debruinebarr2021}{}}%
DeBruine, L. M., \& Barr, D. J. (2021). Understanding mixed-effects models through data simulation. \emph{Advances in Methods and Practices in Psychological Science}, \emph{4}(1), 2515245920965119. \url{https://doi.org/10.1177/251524592096511}

\leavevmode\vadjust pre{\hypertarget{ref-dragojevicgiles2016}{}}%
Dragojevic, M., \& Giles, H. (2016). I don't like you because you're hard to understand: The role of processing fluency in the language attitudes process. \emph{Human Communication Research}, \emph{42}(3), 396--420. \url{https://doi.org/10.1111/hcre.12079}

\leavevmode\vadjust pre{\hypertarget{ref-fairchildetal2020}{}}%
Fairchild, S., Mathis, A., \& Papafragou, A. (2020). Pragmatics and social meaning: Understanding under-informativeness in native and non-native speakers. \emph{Cognition}, \emph{200}, 104171.

\leavevmode\vadjust pre{\hypertarget{ref-fairchildpapafragou2018}{}}%
Fairchild, S., \& Papafragou, A. (2018). Sins of omission are more likely to be forgiven in non-native speakers. \emph{Cognition}, \emph{181}, 80--92.

\leavevmode\vadjust pre{\hypertarget{ref-feinbergetal2005}{}}%
Feinberg, D. R., Jones, B. C., Little, A. C., Burt, D. M., \& Perrett, D. I. (2005). Manipulations of fundamental and formant frequencies influence the attractiveness of human male voices. \emph{Animal Behaviour}, \emph{69}(3), 561--568.

\leavevmode\vadjust pre{\hypertarget{ref-foucartetal2020}{}}%
Foucart, A., Costa, A., Morís-Fernández, L., \& Hartsuiker, R. J. (2020). Foreignness or processing {fluency? On} understanding the negative bias toward foreign-accented speakers. \emph{Language Learning}, \emph{70}(4), 974--1016. \url{https://doi.org/10.1111/lang.12413}

\leavevmode\vadjust pre{\hypertarget{ref-gkalitsiouwerle2023}{}}%
Gkalitsiou, Z., \& Werle, D. (2023). Speech disfluencies in bilingual greek-english young adults. \emph{Journal of Fluency Disorders}, \emph{78}, 106001.

\leavevmode\vadjust pre{\hypertarget{ref-gluszekdovidio2010}{}}%
Gluszek, A., \& Dovidio, J. F. (2010). The way they speak: A social psychological perspective on the stigma of nonnative accents in communication. \emph{Personality and Social Psychology Review}, \emph{14}(2), 214--237.

\leavevmode\vadjust pre{\hypertarget{ref-gluszeketal2011}{}}%
Gluszek, A., Newheiser, A.-K., \& Dovidio, J. F. (2011). Social psychological orientations and accent strength. \emph{Journal of Language and Social Psychology}, \emph{30}(1), 28--45.

\leavevmode\vadjust pre{\hypertarget{ref-goupiletal2021}{}}%
Goupil, L., Ponsot, E., Richardson, D., Reyes, G., \& Aucouturier, J.-J. (2021). Listeners' perceptions of the certainty and honesty of a speaker are associated with a common prosodic signature. \emph{Nature Communications}, \emph{12}(1), 861.

\leavevmode\vadjust pre{\hypertarget{ref-grosjeandeschamps1975}{}}%
Grosjean, F., \& Deschamps, A. (1975). Analyse contrastive des variables temporelles de l'anglais et du fran{ç}ais: Vitesse de parole et variables composantes, ph{é}nom{é}nes d'h{é}sitation. \emph{Phonetica}, \emph{31}(3-4), 144--184.

\leavevmode\vadjust pre{\hypertarget{ref-guyeretal2019speech}{}}%
Guyer, J. J., Fabrigar, L. R., \& Vaughan-Johnston, T. I. (2019). Speech rate, intonation, and pitch: Investigating the bias and cue effects of vocal confidence on persuasion. \emph{Personality and Social Psychology Bulletin}, \emph{45}(3), 389--405.

\leavevmode\vadjust pre{\hypertarget{ref-hanulikovetal2012}{}}%
Hanuíková, A., Alphen, P. M. van, Goch, M. M. van, \& Weber, A. (2012). When one person{\textquotesingle}s mistake is another{\textquotesingle}s standard usage: The effect of foreign accent on syntactic processing. \emph{Journal of Cognitive Neuroscience}, \emph{24}(4), 878--887. \url{https://doi.org/10.1162/jocn_a_00103}

\leavevmode\vadjust pre{\hypertarget{ref-helleretal2015}{}}%
Heller, D., Arnold, J. E., Klein, N., \& Tanenhaus, M. K. (2015). Inferring difficulty: Flexibility in the real-time processing of disfluency. \emph{Language and Speech}, \emph{58}(2), 190--203.

\leavevmode\vadjust pre{\hypertarget{ref-ippapafragou2022}{}}%
Ip, M. H. K., \& Papafragou, A. (2022). Integrating non-native speaker identity in semantic and pragmatic processing. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{44}.

\leavevmode\vadjust pre{\hypertarget{ref-jiangetal2019}{}}%
Jiang, X., Gossack-Keenan, K., \& Pell, M. D. (2019). To believe or not to believe? {How voice and accent information in speech alter listener impressions of trust}. \emph{Quarterly Journal of Experimental Psychology}, \emph{73}(1), 55--79. \url{https://doi.org/10.1177/1747021819865833}

\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2015}{}}%
Jiang, X., \& Pell, M. D. (2015). On how the brain decodes vocal cues about speaker confidence. \emph{Cortex}, \emph{66}, 9--34.

\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2016b}{}}%
Jiang, X., \& Pell, M. D. (2016a). Neural responses towards a speaker's feeling of (un) knowing. \emph{Neuropsychologia}, \emph{81}, 79--93.

\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2016a}{}}%
Jiang, X., \& Pell, M. D. (2016b). The feeling of another's knowing: How {``mixed messages''} in speech are reconciled. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{42}(9), 1412.

\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2017}{}}%
Jiang, X., \& Pell, M. D. (2017). The sound of confidence and doubt. \emph{Speech Communication}, \emph{88}, 106--126.

\leavevmode\vadjust pre{\hypertarget{ref-jatos}{}}%
Lange, K., Kühn, S., \& Filevich, E. (2015). " just another tool for online studies''(JATOS): An easy solution for setup and management of web servers supporting online studies. \emph{PloS One}, \emph{10}(6), e0130834. \url{https://doi.org/10.1371/journal.pone.0130834}

\leavevmode\vadjust pre{\hypertarget{ref-jspsych}{}}%
Leeuw, J. R. de, Gilbert, R. A., \& Luchterhandt, B. (2023). jsPsych: Enabling an open-source collaborative ecosystem of behavioral experiments. \emph{Journal of Open Source Software}, \emph{8}(85), 5351. \url{https://doi.org/10.21105/joss.05351.}

\leavevmode\vadjust pre{\hypertarget{ref-levari2015}{}}%
Lev-Ari, S. (2015). Comprehending non-native speakers: Theory and evidence for adjustment in manner of processing. \emph{Frontiers in Psychology}, \emph{5}, 1546.

\leavevmode\vadjust pre{\hypertarget{ref-levarikeysar2010}{}}%
Lev-Ari, S., \& Keysar, B. (2010). Why don{\textquotesingle}t we believe non-native speakers? {The influence of accent on credibility}. \emph{Journal of Experimental Social Psychology}, \emph{46}(6), 1093--1096. \url{https://doi.org/10.1016/j.jesp.2010.05.025}

\leavevmode\vadjust pre{\hypertarget{ref-levarikeysar2012}{}}%
Lev-Ari, S., \& Keysar, B. (2012). Less-detailed representation of non-native language: Why non-native speakers' stories seem more vague. \emph{Discourse Processes}, \emph{49}(7), 523--538.

\leavevmode\vadjust pre{\hypertarget{ref-lorenzonietal2022}{}}%
Lorenzoni, A., Pagliarini, E., Vespignani, F., \& Navarrete, E. (2022). Pragmatic and knowledge range lenience towards foreigners. \emph{Acta Psychologica}, \emph{226}, 103572.

\leavevmode\vadjust pre{\hypertarget{ref-maihoffmann2014}{}}%
Mai, R., \& Hoffmann, S. (2013). Accents in business communication: An integrative model and propositions for future research. \emph{Journal of Consumer Psychology}, \emph{24}(1), 137--158. \url{https://doi.org/10.1016/j.jcps.2013.09.004}

\leavevmode\vadjust pre{\hypertarget{ref-matzingeretal2023}{}}%
Matzinger, T., Pleyer, M., \& Żywiczyński, P. (2023). Pause length and differences in cognitive state attribution in native and non-native speakers. \emph{Languages}, \emph{8}(1), 26. \url{https://doi.org/10.3390/languages8010026}

\leavevmode\vadjust pre{\hypertarget{ref-nortonhogan1980}{}}%
Norton-Ford, J. D., \& Hogan, D. R. (1980). Role of nonverbal behaviors in social judgments of peers' assertiveness. \emph{Psychological Reports}, \emph{46}(3\_suppl), 1085--1086.

\leavevmode\vadjust pre{\hypertarget{ref-pingetetal2014}{}}%
Pinget, A. F., Bosker, H. R., Quené, H., \& De Jong, N. H. (2014). Native speakers' perceptions of fluency and accent in {L2} speech. \emph{Language Testing}, \emph{31}(3), 349--365. \url{https://doi.org/10.1177/026553221452}

\leavevmode\vadjust pre{\hypertarget{ref-pittamgallois198}{}}%
Pittam, J., \& Gallois, C. (1986). Predicting impressions of speakers from voice quality: Acoustic and perceptual measures. \emph{Journal of Language and Social Psychology}, \emph{5}(4), 233--247.

\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
R Core Team. (2024). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\vadjust pre{\hypertarget{ref-rakicetal2011}{}}%
Rakić, T., Steffens, M. C., \& Mummendey, A. (2011). When it matters how you pronounce it: The influence of regional accents on job interview outcome. \emph{British Journal of Psychology}, \emph{102}(4), 868--883.

\leavevmode\vadjust pre{\hypertarget{ref-shribergetal1997}{}}%
Shriberg, E. E., Bates, R., \& Stolcke, A. (1997). A prosody only decision-tree model for disfluency detection. \emph{Fifth European Conference on Speech Communication and Technology}.

\leavevmode\vadjust pre{\hypertarget{ref-shriberglickley1993}{}}%
Shriberg, E. E., \& Lickley, R. J. (1993). Intonation of clause-internal filled pauses. \emph{Phonetica}, \emph{50}(3), 172--179.

\leavevmode\vadjust pre{\hypertarget{ref-smithclark1993}{}}%
Smith, V. L., \& Clark, H. H. (1993). On the course of answering questions. \emph{Journal of Memory and Language}, \emph{32}(1), 25--38.

\leavevmode\vadjust pre{\hypertarget{ref-ulemanetal2008}{}}%
Uleman, J. S., Adil Saribay, S., \& Gonzalez, C. M. (2008). Spontaneous inferences, implicit impressions, and implicit theories. \emph{Annu. Rev. Psychol.}, \emph{59}, 329--360.

\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\end{CSLReferences}

\end{document}

### 2024-09-13 manuscript/manuscript_eb.Rmd
edits manuscripts

@@
 abstract: |
-  Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the situational (e.g, who is speaking) to the ephemeral (e.g., how they speak).
-Listeners are more likely to evaluate non-native speakers as less veracious, more deceiving, and evaluate the speaker as less competent.
-Similar judgements are elicited by how fluent speech is: Filled pauses, such as _uh_ or _um_ in English, elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge.
-Interestingly, the co-existence of these two cues has been shown to yield, sometimes, different processes.
+  Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking).
+The presence of disfluencies, such as filled pauses (e.g., _uh_ or _um_ in English), elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge.
+On the other hand, listeners consider alternative explanations for the speaker to be underinformative: Specifically, non-native speakers are more likely to be forgiven when they fail to be informative.
 However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear.
@@
 
-figurelist        : no
-tablelist         : no
+figurelist        : yes
+tablelist         : yes
 footnotelist      : no
@@
 classoption       : "man"
+documentclass     : "apa7"
 output            : papaja::apa6_pdf
@@
 Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listenes [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
-This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014].
+This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.
 
@@
 
-## Results
+# Results
 
@@
 ```
+
+Table \@ref(tab:tab-dist-money) and Figure \@ref(fig:fig1) show the mean amount of money bet per speaker and fluency condition.
+On average, participants bet £25 on each horse.
+This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
+However, disfluent instructions seem to lower the amount of money bet.
+
 ```{r tab-dist-money}
@@
 ```
+
 ```{r fig1, out.width="90%",fig.align='center', fig.cap="Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native)."}
@@
 ```
-
-Table \@ref(tab:tab-dist-money) and Figure \@ref(fig:fig1) show the mean amount of money bet per speaker and fluency condition.
-On average, participants bet £25 on each horse.
-This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
-However, disfluent instructions seem to lower the amount of money bet.
 
@@
 
+Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude.
+A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995].
+However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009].
+In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance [@levari2015], which consequently leads native listeners to "forgive" what otherwise would be lead to a negative evaluation [@lorenzonietal2022; @fairchildetal2020].
+In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
+Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.
+
 The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced [@brennanwilliams1995].
@@
 In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because the utterance is semantically and acoustically identical apart from the excision of disfluencies, an inference about a speaker's confidence based on those disfluencies is an important potential determinant of participants' decisions.
+
+This inference explanation would predict that listeners would forgive foreign disfluencies, in line with the expectations-based account.
+While previous research has reported that whether a filled pause affects processes involved in speech comprehension depending on speaker identity [e.g., @boskeretal2014], recent studies have failed to find this effect when it comes to speaker's attributions [@matzingeretal2023].
+In our experiment, participants distributed money similarly when either speaker provided disfluent descriptions, suggesting that listeners did not weigh in our (non-native) speaker's identity to interpret the disfluency.
+This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.
+One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster.
+This introduction of the speaker as an authoritative figure may have overridden any other features of their identity, including their non-native speaker identity.
+Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty [@moletal2013].
+Considering the language attitudes triggered by both accents, the difference in speaker preference may more likely reflect the ease of comprehending the native speaker, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
+
+The experiment here also introduced a novel approach to measuring how certain the speaker is perceived.
+While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new venue to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
+However, a potential shortcoming of our design has to do with how people approached the betting system.
+Because of the nature of the task, in that we tested participants with no prior knowledge of horse races, our participants behaved rationally: The vast majority employed the hundred pounds allocated and distributed them fairly rationally in a way that maximizes their chances of winning (i.e., around £25 per horse).
+It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where individuals have more knowledge) or where they are rewarded for allocating money to the winning horse, how the speaker is perceived may yield a larger effect on participants' behaviours.
 

### 2024-09-13 manuscript/manuscript_eb.tex
edits manuscripts

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{csquotes}
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
+\cftpagenumbersoff{table}
+\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
+\renewcommand{\cfttabaftersnum}{.\space}
+\setlength{\cfttabindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \ifLuaTeX
@@
 \abstract{%
-Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the situational (e.g, who is speaking) to the ephemeral (e.g., how they speak).
-Listeners are more likely to evaluate non-native speakers as less veracious, more deceiving, and evaluate the speaker as less competent.
-Similar judgements are elicited by how fluent speech is: Filled pauses, such as \emph{uh} or \emph{um} in English, elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge.
-Interestingly, the co-existence of these two cues has been shown to yield, sometimes, different processes.
+Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking).
+The presence of disfluencies, such as filled pauses (e.g., \emph{uh} or \emph{um} in English), elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge.
+On the other hand, listeners consider alternative explanations for the speaker to be underinformative: Specifically, non-native speakers are more likely to be forgiven when they fail to be informative.
 However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear.
@@
 Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listenes (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
-This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014).
+This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.
 
@@
 \hypertarget{results}{%
-\subsection{Results}\label{results}}
+\section{Results}\label{results}}
 
@@
 \subsubsection{Betting behaviour}\label{betting-behaviour}}
+
+Table \ref{tab:tab-dist-money} and Figure \ref{fig:fig1} show the mean amount of money bet per speaker and fluency condition.
+On average, participants bet £25 on each horse.
+This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
+However, disfluent instructions seem to lower the amount of money bet.
 
@@
 \end{table}
+
 \begin{figure}[H]
@@
 \end{figure}
-
-Table \ref{tab:tab-dist-money} and Figure \ref{fig:fig1} show the mean amount of money bet per speaker and fluency condition.
-On average, participants bet £25 on each horse.
-This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
-However, disfluent instructions seem to lower the amount of money bet.
 
@@
 
+Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude.
+A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995).
+However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009).
+In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance (Lev-Ari, 2015), which consequently leads native listeners to ``forgive'' what otherwise would be lead to a negative evaluation (Fairchild et al., 2020; Lorenzoni et al., 2022).
+In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
+Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.
+
 The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced (Brennan \& Williams, 1995).
@@
 In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because the utterance is semantically and acoustically identical apart from the excision of disfluencies, an inference about a speaker's confidence based on those disfluencies is an important potential determinant of participants' decisions.
+
+This inference explanation would predict that listeners would forgive foreign disfluencies, in line with the expectations-based account.
+While previous research has reported that whether a filled pause affects processes involved in speech comprehension depending on speaker identity (e.g., Bosker, Quené, Sanders, \& De Jong, 2014), recent studies have failed to find this effect when it comes to speaker's attributions (Matzinger et al., 2023).
+In our experiment, participants distributed money similarly when either speaker provided disfluent descriptions, suggesting that listeners did not weigh in our (non-native) speaker's identity to interpret the disfluency.
+This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.
+One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster.
+This introduction of the speaker as an authoritative figure may have overridden any other features of their identity, including their non-native speaker identity.
+Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty (Mol, Kuhlen, Van der Steen, \& Obbens, 2013).
+Considering the language attitudes triggered by both accents, the difference in speaker preference may more likely reflect the ease of comprehending the native speaker, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
+
+The experiment here also introduced a novel approach to measuring how certain the speaker is perceived.
+While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new venue to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
+However, a potential shortcoming of our design has to do with how people approached the betting system.
+Because of the nature of the task, in that we tested participants with no prior knowledge of horse races, our participants behaved rationally: The vast majority employed the hundred pounds allocated and distributed them fairly rationally in a way that maximizes their chances of winning (i.e., around £25 per horse).
+It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where individuals have more knowledge) or where they are rewarded for allocating money to the winning horse, how the speaker is perceived may yield a larger effect on participants' behaviours.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-dejongetal2015}{}}%
+De Jong, N.
+H., Groenhout, R., Schoonen, R., \& Hulstijn, J.
+H.
+(2015).
+Second language fluency: Speaking style or proficiency?
+Correcting measures of second language fluency for first language behavior.
+\emph{Applied Psycholinguistics}, \emph{36}(2), 223--243.
+
 \leavevmode\vadjust pre{\hypertarget{ref-debruinebarr2021}{}}%
@@
 \url{https://doi.org/10.1177/251524592096511}
+
+\leavevmode\vadjust pre{\hypertarget{ref-derwingetal2009}{}}%
+Derwing, T.
+M., Munro, M.
+J., Thomson, R.
+I., \& Rossiter, M.
+J.
+(2009).
+The relationship between L1 fluency and L2 fluency development.
+\emph{Studies in Second Language Acquisition}, \emph{31}(4), 533--557.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-moletal2013}{}}%
+Mol, L., Kuhlen, A., Van der Steen, R., \& Obbens, M.
+(2013).
+Beliefs about a speaker affect feeling of another's knowing.
+\emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{35}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-nortonhogan1980}{}}%
@@
 
+\clearpage
+\renewcommand{\listfigurename}{Figure captions}
+
+\clearpage
+\renewcommand{\listtablename}{Table captions}
+
 \end{document}

### 2024-09-13 manuscript/manuscript_eb.Rmd
first draft
sent to rob and martin

@@
 keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
-wordcount         : "X"
+wordcount         : "4774"
 
@@
 
-However, certain speech qualities can yield negative evaluations without being explicitly associated with those.
-One consistent finding is that speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., [@dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010].
+Interestingly, who produces the information can also affect how it is evaluated.
+On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., [@dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021].
 This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].
-Alternatively, but not exclusively, it is possible that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018].
+
+Alternatively, but not exclusively, speaker identity in itself can bias interpretation.
+Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret.
+@fairchildetal2020 asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story.
+Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information.
+The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp.
+1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp.
+2).
+Further, this 'forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp.
+3 and 4).
+One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018].
 This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted.
 Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker.
-In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], why a statement is believed to be underinformative [@fairchildpapafragou2018; @fairchildetal2020; @lorenzonietal2022; @ippapafragou2022] and why non-native speech is processed shallower [@levarikeysar2012; @hanulikovetal2012].
+In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], why a statement is believed to be underinformative [@fairchildpapafragou2018; @lorenzonietal2022; @ippapafragou2022] and why non-native speech is processed shallower [@levarikeysar2012; @hanulikovetal2012].
 
 Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted.
-However, stereotypes on linguistic competence may also affect how speech is delivered.
-In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived [@jiangetal2019; @caballeropell2020].
-Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listenes [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
+However, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
+In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived [@jiangetal2019; @caballeropell2020].
+Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listeners [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
 This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

### 2024-09-13 manuscript/manuscript_eb.tex
first draft
sent to rob and martin

@@
 {}{\PatchFailed}
-\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: X}
+\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 4774}
 \usepackage{lineno}
@@
 
-However, certain speech qualities can yield negative evaluations without being explicitly associated with those.
-One consistent finding is that speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., (Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Lev-Ari \& Keysar, 2010).
+Interestingly, who produces the information can also affect how it is evaluated.
+On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., (Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021).
 This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013).
-Alternatively, but not exclusively, it is possible that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015).
+
+Alternatively, but not exclusively, speaker identity in itself can bias interpretation.
+Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret.
+Fairchild, Mathis, and Papafragou (2020) asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story.
+Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information.
+The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp.
+1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp.
+2).
+Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp.
+3 and 4).
+One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015).
 This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted.
 Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker.
-In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018), why a statement is believed to be underinformative (Fairchild, Mathis, \& Papafragou, 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022) and why non-native speech is processed shallower (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).
+In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018), why a statement is believed to be underinformative (Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022) and why non-native speech is processed shallower (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).
 
 Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted.
-However, stereotypes on linguistic competence may also affect how speech is delivered.
-In the case of confidence and knowledgeability, nativeness has been shown to affect how confident a speaker is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019).
-Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listenes (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
+However, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
+In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019).
+Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
 This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.
@@
 
-After the betting round was complete, participants completed a questionnaire similar to that of Foucart, Costa, Morís-Fernández, and Hartsuiker (2020) to measure their language attitudes towards the native and the non-native speaker.
+After the betting round was complete, participants completed a questionnaire similar to that of Foucart et al.
+(2020) to measure their language attitudes towards the native and the non-native speaker.
 For each speaker, participants answered six questions measuring affect (three questions for negative affect and three questions for positive affect), five questions measuring solidarity, five questions measuring status, and one question each for comprehensibility, accentedness, fluency, and trustworthiness.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-barlowetal2024}{}}%
+Barlow, S., Beardsley, G., Bsharah, Z., Crofts, R., De La Rosa, C., Gutierrez, A., et al.others.
+(2024).
+The effects of exposure and explicit stereotypes on veracity judgments of polish-accented english speech: A preregistered close replication and extension of boduch-grabka \& lev-ari (2021).
+\emph{Studies in Second Language Acquisition}, 1--17.
+
 \leavevmode\vadjust pre{\hypertarget{ref-barretal2013}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-foucarthartsuiker2021}{}}%
+Foucart, A., \& Hartsuiker, R.
+J.
+(2021).
+Are foreign-accented speakers that {``incredible''}?
+The impact of the speaker's indexical properties on sentence processing.
+\emph{Neuropsychologia}, \emph{158}, 107902.
+
 \leavevmode\vadjust pre{\hypertarget{ref-gkalitsiouwerle2023}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-souzamarkman2013}{}}%
+Souza, A. L., \& Markman, A. B. (2013). Foreign accent does not influence cognitive judgments. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{35}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stocker2017}{}}%
+Stocker, L. (2017). The impact of foreign accent on credibility: An analysis of cognitive statement ratings in a swiss context. \emph{Journal of Psycholinguistic Research}, \emph{46}, 617--628.
+
 \leavevmode\vadjust pre{\hypertarget{ref-ulemanetal2008}{}}%
 Uleman, J. S., Adil Saribay, S., \& Gonzalez, C. M. (2008). Spontaneous inferences, implicit impressions, and implicit theories. \emph{Annu. Rev. Psychol.}, \emph{59}, 329--360.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wetzeletal2021}{}}%
+Wetzel, M., Zufferey, S., \& Gygax, P.
+(2021).
+Do non-native and unfamiliar accents sound less credible?
+An examination of the processing fluency hypothesis.
+\emph{Journal of Articles in Support of the Null Hypothesis}, \emph{17}(2).
 

### 2024-09-16 manuscript/manuscript_eb.Rmd
change typos
there will still be typos :)

@@
 Impressions of other people arise naturally and automatically [@ulemanetal2008].
-Speakers can be evaluated not only by what they say but how they say it.
-For example, vocal features of speech can affect perceptions of confidence and persuasion [@guyeretal2019speech], status and solidarity [@pittamgallois198], and even attractiveness [@feinbergetal2005].
-One repeatedly reported feature of speech said to bias listeners' evaluations is its fluency.
-Disfluencies, such as _uh_ or _um_ in English can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995].
+Speakers can be evaluated not only by what they say but also by how they say it.
+For example, vocal features of speech can affect perceptions of confidence and persuasion [@guyeretal2019speech], status and solidarity [@pittamgallois198], or even attractiveness [@feinbergetal2005].
+One speech feature consistently found to bias evaluations of the speaker is speech fluency.
+Disfluencies, such as _uh_ or _um_ in English, can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995].
 Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility [@gluszeketal2011; @gluszekdovidio2010; @rakicetal2011; @levarikeysar2010].
 In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually.
-It is important to note that it is not our interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
+It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
 
-There is a growing body of literature showing that listeners speech qualities are taken as reflective of a speaker's knowledgeability.
-Voices with a slow speech rate, low amplitude and a large F0 range are more likely to be rated as less confident, and produce distinct neural responses [@jiangpell2015; @jiangpell2016a; @jiangpell2016b].
+There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability.
+Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and produce distinct neural responses [@jiangpell2015; @jiangpell2016a; @jiangpell2016b].
 Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically [@goupiletal2021].
 These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies [@shribergetal1997; @shriberglickley1993; @grosjeandeschamps1975; @jiangpell2017].
-@brennanwilliams1995 demonstrated that filled pauses (e.g., uh, mm, or um) can be perceived as indices of speakers’ confidence in their knowledge.
+@brennanwilliams1995 demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers’ confidence in their knowledge.
 In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., _feeling of another's knowing_, FOAK.
-Amongst the cues that biased participants' assessments were filled pauses:  Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers’ reduced certainty about their knowledge.
-In contrast, non-answers (i.e., 'I don’t know') were more likely to receive a higher FOAK rating if preceded by a filled pause.
+Among the cues that biased participants' assessments were filled pauses:  Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers’ reduced certainty about their knowledge.
+In contrast, non-answers (i.e., 'I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause.
 @brennanwilliams1995 took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question [see also @smithclark1993].
 
-Interestingly, who produces the information can also affect how it is evaluated.
-On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., [@dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021].
-This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].
+Interestingly, speaker identity can itself affect evaluations of both the speaker and the content of speech.
+In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations.
+On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated [e.g., @dragojevicgiles2016; @gluszekdovidio2010].
+Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021].
+These negative effects of triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].
 
-Alternatively, but not exclusively, speaker identity in itself can bias interpretation.
-Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret.
-@fairchildetal2020 asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story.
-Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information.
+On the other hand, there seem to be instances where being a non-native speaker is more advantageous.
+@fairchildetal2020 examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness.
+@fairchildetal2020 isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identity.
+In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention.
+Native speakers who were underinformative were more likely to be rated as unwilling to share the information.
 The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp.
@@
 Further, this 'forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp.
-3 and 4).
-One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018].
+3 and 4) [for similar results, see @@fairchildpapafragou2018; @lorenzonietal2022].
+Interestingly, this pattern of results holds even for auditory stimuli [@ippapafragou2022], suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.
+
+One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations about their competence.
+Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018].
 This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted.
 Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker.
-In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], why a statement is believed to be underinformative [@fairchildpapafragou2018; @lorenzonietal2022; @ippapafragou2022] and why non-native speech is processed shallower [@levarikeysar2012; @hanulikovetal2012].
+In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022] or why non-native speech is processed more shallowly [@levarikeysar2012; @hanulikovetal2012].
 
-Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted.
-However, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
-In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived [@jiangetal2019; @caballeropell2020].
-Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listeners [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
-This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.
+Interestingly, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
+For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be [@jiangetal2019; @caballeropell2020].
+Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and are perceived as such by native listeners [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
+This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
 
@@
 
-Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude.
-A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995].
-However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009].
+Listeners can attribute a speaker knowledgeability based on a range of cues, such as voice pitch or amplitude.
+Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995].
+However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in one's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009].
 In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance [@levari2015], which consequently leads native listeners to "forgive" what otherwise would be lead to a negative evaluation [@lorenzonietal2022; @fairchildetal2020].

### 2024-09-16 manuscript/manuscript_eb.tex
change typos
there will still be typos :)

@@
 Impressions of other people arise naturally and automatically (Uleman, Adil Saribay, \& Gonzalez, 2008).
-Speakers can be evaluated not only by what they say but how they say it.
-For example, vocal features of speech can affect perceptions of confidence and persuasion (Guyer, Fabrigar, \& Vaughan-Johnston, 2019), status and solidarity (Pittam \& Gallois, 1986), and even attractiveness (Feinberg, Jones, Little, Burt, \& Perrett, 2005).
-One repeatedly reported feature of speech said to bias listeners' evaluations is its fluency.
-Disfluencies, such as \emph{uh} or \emph{um} in English can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995).
+Speakers can be evaluated not only by what they say but also by how they say it.
+For example, vocal features of speech can affect perceptions of confidence and persuasion (Guyer, Fabrigar, \& Vaughan-Johnston, 2019), status and solidarity (Pittam \& Gallois, 1986), or even attractiveness (Feinberg, Jones, Little, Burt, \& Perrett, 2005).
+One speech feature consistently found to bias evaluations of the speaker is speech fluency.
+Disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995).
 Interestingly, speech produced with an accent different from one's own - particularly a \emph{foreign} accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek \& Dovidio, 2010; Gluszek, Newheiser, \& Dovidio, 2011; Lev-Ari \& Keysar, 2010; Rakić, Steffens, \& Mummendey, 2011).
 In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually.
-It is important to note that it is not our interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
-
-There is a growing body of literature showing that listeners speech qualities are taken as reflective of a speaker's knowledgeability.
-Voices with a slow speech rate, low amplitude and a large F0 range are more likely to be rated as less confident, and produce distinct neural responses (Jiang \& Pell, 2015, 2016b, 2016a).
+It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
+
+There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability.
+Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and produce distinct neural responses (Jiang \& Pell, 2015, 2016b, 2016a).
 Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil, Ponsot, Richardson, Reyes, \& Aucouturier, 2021).
 These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg, Bates, \& Stolcke, 1997; Shriberg \& Lickley, 1993).
-Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) can be perceived as indices of speakers' confidence in their knowledge.
+Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers' confidence in their knowledge.
 In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., \emph{feeling of another's knowing}, FOAK.
-Amongst the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge.
+Among the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge.
 In contrast, non-answers (i.e., `I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause.
@@
 
-Interestingly, who produces the information can also affect how it is evaluated.
-On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., (Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021).
-This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013).
-
-Alternatively, but not exclusively, speaker identity in itself can bias interpretation.
-Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret.
-Fairchild, Mathis, and Papafragou (2020) asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story.
-Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information.
+Interestingly, speaker identity can itself affect evaluations of both the speaker and the content of speech.
+In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations.
+On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010).
+Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021).
+These negative effects of triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013).
+
+On the other hand, there seem to be instances where being a non-native speaker is more advantageous.
+Fairchild, Mathis, and Papafragou (2020) examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness.
+Fairchild et al.
+(2020) isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identity.
+In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention.
+Native speakers who were underinformative were more likely to be rated as unwilling to share the information.
 The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp.
@@
 Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp.
-3 and 4).
-One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015).
+3 and 4) (for similar results, see @ Fairchild \& Papafragou, 2018; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022).
+Interestingly, this pattern of results holds even for auditory stimuli (Ip \& Papafragou, 2022), suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.
+
+One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations about their competence.
+Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015).
 This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted.
 Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker.
-In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018), why a statement is believed to be underinformative (Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022) and why non-native speech is processed shallower (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).
-
-Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted.
-However, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
-In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019).
-Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
-This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.
+In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018) or why non-native speech is processed more shallowly (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).
+
+Interestingly, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
+For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019).
+Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
+This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
 
@@
 
-Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude.
-A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995).
-However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009).
+Listeners can attribute a speaker knowledgeability based on a range of cues, such as voice pitch or amplitude.
+Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995).
+However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in one's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009).
 In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance (Lev-Ari, 2015), which consequently leads native listeners to ``forgive'' what otherwise would be lead to a negative evaluation (Fairchild et al., 2020; Lorenzoni et al., 2022).

### 2024-09-27 manuscript/manuscript_eb.Rmd
edits manuscript
following MC feedback (mostly: discussion)

@@
 One speech feature consistently found to bias evaluations of the speaker is speech fluency.
-Disfluencies, such as _uh_ or _um_ in English, can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995].
+Speech which includes disfluencies, such as _uh_ or _um_ in English, can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995].
 Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility [@gluszeketal2011; @gluszekdovidio2010; @rakicetal2011; @levarikeysar2010].
-In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually.
+In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually.
 It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
@@
 There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability.
-Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and produce distinct neural responses [@jiangpell2015; @jiangpell2016a; @jiangpell2016b].
+Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener[@jiangpell2015; @jiangpell2016a; @jiangpell2016b].
 Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically [@goupiletal2021].
@@
 
-Interestingly, speaker identity can itself affect evaluations of both the speaker and the content of speech.
+In a similar vein, speaker identity can itself affect evaluations of both the speaker and the content of speech.
 In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations.
-On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated [e.g., @dragojevicgiles2016; @gluszekdovidio2010].
+On the one hand, speakers with a foregin accent are more likely to be negatively evaluated [e.g., @dragojevicgiles2016; @gluszekdovidio2010].
 Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021].
-These negative effects of triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].
+These negative effects triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency [@levarikeysar2010], group membership, or a combination of both [@maihoffmann2014].
 
@@
 @fairchildetal2020 examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness.
-@fairchildetal2020 isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identity.
+@fairchildetal2020 isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identities.
 In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention.
@@
 Further, this 'forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp.
-3 and 4) [for similar results, see @@fairchildpapafragou2018; @lorenzonietal2022].
+3 and 4) [for similar findings, see @fairchildpapafragou2018; @lorenzonietal2022].
 Interestingly, this pattern of results holds even for auditory stimuli [@ippapafragou2022], suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.
 
-One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations about their competence.
+One potential explanation is that non-native speakers are evaluated differently from native speakers due to expectations about their competence.
 Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018].
@@
 For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be [@jiangetal2019; @caballeropell2020].
-Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and are perceived as such by native listeners [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
-This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
+Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and are perceived as such by native listeners [@pingetetal2014], it is possible that a speaker's nativeness leads to different interpretations of disfluencies.
+This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including non-native versus native speakers [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
 
 Recently, @matzingeretal2023 explored whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers.
-In their study, participants listened to native and non-native speakers answer trivial questions and requests, and were explicitly asked to rate the speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
-Crucially, @matzingeretal2023 manipulated speakers' fluency by having answers prefaced with either short (200 ms) or long (1200 ms) pauses.
+In their study, participants listened staged conversations where native and non-native speakers answered trivial questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
+Crucially, @matzingeretal2023 manipulated speakers' fluency by manipulating inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses.
 For requests, long pauses were less likely to be associated with unwillingness for non-native compared to native speakers.
@@
 
-To date, most experimental evaluations of manner of speech have been explicit.
-Participants are asked to rate particular traits of speakers on a scale.
+As is the case for @matzingeretal2023, most studies evaluating the effects of manner of speech on pereptions of the speaker have used explicit ratings.
+Participants are asked to rate particular traits of speakers or what they say on a scale.
 Further, these ratings are elicited in non-social contexts, where participants do not have anything at stake.
 Although these experiments demonstrate that listeners show sensitivity to aspects of speech such as fluency and accent when asked to make explicit judgements about the speaker, they may not explain how listeners evaluate speech implicitly, when to do so is consequential.Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm.
-In this task, participants listen to a set of speakers provide descriptions of horses and are asked to distribute virtual tokens as 'bets' on each horse's likelihood of winning a putative race.
+In this task, participants listen to a set of speakers provide descriptions of horses, and are asked to distribute virtual tokens as 'bets' on each horse's likelihood of winning a putative race.
 This approach presents two advantages over previous experiments.
@@
 Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets [@butterworth2019].
-Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing).
+Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing or its technical vocabulary).
 
-In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency and the speaker's identity as conveyed by their accent.
+In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent.
 We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently.
@@
 We explored the required number of participants for a study with a power higher than .8 for the interaction between fluency and speaker identity.
-We conducted a 1000 simulations per different combinations of the effect size (ranging from small to medium) and the standard deviation of the residuals.
+We conducted a 1000 simulations per different combinations of the effect size of the interaction (ranging from small to medium) and the standard deviation of the residuals.
 In this analysis, we assumed a medium effect size of fluency and no effect of speaker identity.
@@
 
-In our pre-registration, we set that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study.
+In our pre-registration, we stipulated that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study.
 Further, we would exclude from analysis data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four, or considered themselves experts in horse races.
 This meant that we recruited 641 participants for a sample of 360.
-Participants were recruited via the online platform Prolific, and were reimbursed £1.50 for a 10-minutes experiment.
+Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the PPLS Ethics Committee (ref no 133-2223/3).
+Participants were reimbursed £1.50 for a 10-minutes experiment.
 
@@
 
-We selected a set of eight images of racehorses from the web.
+We selected a candidate set of eight images of racehorses from the web.
 The selected images each featured only one racehorse in the foreground, in motion, ridden by a jockey, and the horses all took up approximately the same proportion of the image.
@@
 A new sample fo 30 British English speaker rated the edited passages.
-A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, _p_ = .52), nor in the order in which they were ranked (all |t| <$ 2).
+A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, _p_ = .52), nor in the order in which they were ranked (all |t| < 2).
 The final set of descriptions for the experiment can be found in Table \@ref(tab:tab-horse-description-text).
@@
 
-We then recorded a British English native speaker and a non-native (L1: Italian) English speaker to create the auditory stimuli.
+We recorded a British English native speaker and a non-native (L1: Italian) English speaker to create the auditory stimuli.
 Both speakers were female.
@@
   tab1A,
-  caption = "Transcription of the disfluent horse descriptions.",
+  caption = "Transcriptions of the disfluent horse descriptions.",
   align = c("m{2cm}", "m{13cm}")
@@
 
-To ensure that the resulting descriptions were perceived to be natural (i.e., our edited 'fluent' audios were not clearly edited) and that they were perceived as differing in fluency (i.e., disfluent and 'fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
+To ensure that the resulting descriptions were perceived to be natural (i.e., edits to the 'fluent' audios were not obvious) and that they were perceived as differing in fluency (i.e., disfluent and 'fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
 Participants were allocated to one of the 24 experimental lists, to ensure that our validation procedure was similar to how participants encountered stimuli in the actual experiment.
-Following @boskeretal2014 procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
+Following @boskeretal2014's procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
 We instructed participants to rate fluency by considering silent and filled pauses, speed of speech, and repairs, and to ignore speakers' accents and the content of their speech.
@@
 Table \@ref(tab:tab-results-validation) shows the means (and standard deviations) of participants' ratings of fluency, naturalness, and accentedness.
-A linear mixed model for fluency ratings with fixed effects of fluency (treatment-coded, reference: fluent), speaker's linguistic background (treatment-coded, reference: native speaker), and their interaction, with random intercepts by participant and by horse description showed that fluency ratings differed significantly for the fluent and disfluent conditions (`r mdl_validation_flu$full_result$deliverydisfluent`).
+A linear mixed model for fluency ratings with fixed effects of fluency (treatment-coded, reference: fluent), speaker's linguistic background (treatment-coded, reference: native speaker), and their interaction, with random intercepts by participant and by horse description, showed that fluency ratings differed significantly for the fluent and disfluent conditions (`r mdl_validation_flu$full_result$deliverydisfluent`).
 The non-native speaker was perceived as more disfluent than the native speaker (`r mdl_validation_flu$full_result$speakernonnative`), in line with previous findings [@pingetetal2014; @boskeretal2014b], but the interaction between the two variables was not significant (`r mdl_validation_flu$full_result$deliverydisfluent_speakernonnative`).
@@
 The order in which horses were presented was randomised.
-In each trial, participants listened to one speaker described a given horse's performance.
+In each trial, participants listened as one speaker described a given horse's performance.
 Once the playback stopped, participants were asked to place a bet by typing a number on a web form.
@@
 Table \@ref(tab:tab-dist-money) and Figure \@ref(fig:fig1) show the mean amount of money bet per speaker and fluency condition.
-On average, participants bet £25 on each horse.
+On average, participants bet £25 on when information was provided fluently.
 This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
@@
 Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (`r mdlbet_m1$full_result$delivery_cont1`).
-There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and no other significances (for speaker, `r mdlbet_m1_all$full_result$speaker_cont1`; for the interaction `r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].
+There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between manner of delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and no other significances (for speaker, `r mdlbet_m1_all$full_result$speaker_cont1`; for the interaction `r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].
 
@@
 
-Table \@ref(tab:tab5) depicts the mean (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
+Table \@ref(tab:tab5) depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
 Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score.
@@
 Cronbach's alpha showed that the scores for these attitudes were reliable ($\alpha_{affect}$ = `r affect_alpha`, $\alpha_{status}$ = `r status_alpha`, $\alpha_{solidarity}$ = `r solidarity_alpha`).
-We explored differences between the native and the non-native speaker's evaluations in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.
+We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.
 
@@
 
-Analyses showed that speakers were rared differently across all six dimensions (see Table \@ref(tab:tab6)).
+Analyses showed that speakers were rated differently across all six dimensions (see Table \@ref(tab:tab6)).
 The largest differences were, unsurprisingly, in comprehensibility and accentedness, where the non-native speaker received lower ratings.
@@
 206 participants reported they would prefer to learn from the native spaker, and 154 preferred the non-native speaker.
-A $\chi^2$ test of goodness of fit showed that there was a significant difference in participants' preferences ($\chi^2$(1) = 7.51, _p_ < .01).
+A $\chi^2$ test of goodness of fit showed that this difference in preferences was reliable ($\chi^2$(1) = 7.51, _p_ < .01).
 
@@
 
-Listeners can attribute a speaker knowledgeability based on a range of cues, such as voice pitch or amplitude.
+Listeners can attribute knowledgeability to a speaker based on a range of cues, such as voice pitch or amplitude.
 Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995].
-However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in one's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009].
+However, speakers can be disfluent for reasons other than lack of confidence: For example, speaking in one's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009].
 In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance [@levari2015], which consequently leads native listeners to "forgive" what otherwise would be lead to a negative evaluation [@lorenzonietal2022; @fairchildetal2020].
-In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
+In the present experiment, we explored whether attributions of lack of knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
 Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.
 
-The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced [@brennanwilliams1995].
+The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced.
 Descriptions that included hesitation phenomena, in the form of filled pauses, led to smaller bets compared to their fluent counterparts.
@@
 Brennan and Williams (1995) attributed participants' ratings to inferences made about the speaker's mental state - specifically, inferences about the degree of confidence a speaker has in their knowledge.
-In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because the utterance is semantically and acoustically identical apart from the excision of disfluencies, an inference about a speaker's confidence based on those disfluencies is an important potential determinant of participants' decisions.
+In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because utterances were semantically identical and acoustically identical apart from the excision of disfluencies and accent, an inference about a speaker's confidence based on those disfluencies is the most likely potential determinant of participants' decisions.
 
-This inference explanation would predict that listeners would forgive foreign disfluencies, in line with the expectations-based account.
-While previous research has reported that whether a filled pause affects processes involved in speech comprehension depending on speaker identity [e.g., @boskeretal2014], recent studies have failed to find this effect when it comes to speaker's attributions [@matzingeretal2023].
-In our experiment, participants distributed money similarly when either speaker provided disfluent descriptions, suggesting that listeners did not weigh in our (non-native) speaker's identity to interpret the disfluency.
+The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions.
+This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension [e.g., @boskeretal2014; @arnoldetal2007; @helleretal2015], and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations [e.g., @fairchildetal2020; @lorenzonietal2020; @ippapafragou2022; @fairchildpapafragou2018] possibly because native listeners expect them to produce those [@levari2015].
 This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.
+
+Nonetheless, our results align with recent studies that have failed to find this an interaction between disfluencies and nativeness when it comes to speaker's attributions [@matzingeretal2023].
+@matzingeretal2023 accounted for their findings as a the results of the degree with which a listener needs to model the speaker: Assessing a speaker's knowledge is not as socially engaging as other communicative contexts (e.g., granting a request) and consequently, inferring an interlocutor's cognitive state is not relevant.
+Interestingly, there are several differences between their paradigm and ours that shed doubts on whether this explanation applies to our results.
+Specifically, in @matzingeretal2023 participants were overhearing a conversation, and given their task (i.e., explicitly rate their perception on speaker's knowledge or confidence), accurately ascribing the cause of disfluency did not have any consequences.
+In contrast, our participants listened to speakers talking in isolation and, most importantly, assessing speakers' knowledgeability was crucial for performing their task.
+
 One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster.
@@
 Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty [@moletal2013].
-Considering the language attitudes triggered by both accents, the difference in speaker preference may more likely reflect the ease of comprehending the native speaker, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
+The preference to learn in future occasions for the native speaker may be more likely to reflect the ease of comprehending them, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
 
-The experiment here also introduced a novel approach to measuring how certain the speaker is perceived.
-While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new venue to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
+This experiment introduced a novel approach to measuring how certain the speaker is perceived to be.
+While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new set-up to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
 However, a potential shortcoming of our design has to do with how people approached the betting system.
@@
 It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where individuals have more knowledge) or where they are rewarded for allocating money to the winning horse, how the speaker is perceived may yield a larger effect on participants' behaviours.
+
+Overall,
 

### 2024-09-27 manuscript/manuscript_eb.tex
edits manuscript
following MC feedback (mostly: discussion)

@@
 One speech feature consistently found to bias evaluations of the speaker is speech fluency.
-Disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995).
+Speech which includes disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995).
 Interestingly, speech produced with an accent different from one's own - particularly a \emph{foreign} accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek \& Dovidio, 2010; Gluszek, Newheiser, \& Dovidio, 2011; Lev-Ari \& Keysar, 2010; Rakić, Steffens, \& Mummendey, 2011).
-In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually.
+In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually.
 It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
@@
 There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability.
-Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and produce distinct neural responses (Jiang \& Pell, 2015, 2016b, 2016a).
+Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener(Jiang \& Pell, 2015, 2016b, 2016a).
 Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil, Ponsot, Richardson, Reyes, \& Aucouturier, 2021).
@@
 
-Interestingly, speaker identity can itself affect evaluations of both the speaker and the content of speech.
+In a similar vein, speaker identity can itself affect evaluations of both the speaker and the content of speech.
 In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations.
-On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010).
+On the one hand, speakers with a foregin accent are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010).
 Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021).
-These negative effects of triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013).
+These negative effects triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, or a combination of both (Mai \& Hoffmann, 2013).
 
@@
 Fairchild et al.
-(2020) isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identity.
+(2020) isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identities.
 In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention.
@@
 Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp.
-3 and 4) (for similar results, see @ Fairchild \& Papafragou, 2018; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022).
+3 and 4) (for similar findings, see Fairchild \& Papafragou, 2018; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022).
 Interestingly, this pattern of results holds even for auditory stimuli (Ip \& Papafragou, 2022), suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.
 
-One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations about their competence.
+One potential explanation is that non-native speakers are evaluated differently from native speakers due to expectations about their competence.
 Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015).
@@
 For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019).
-Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies.
-This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
+Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it is possible that a speaker's nativeness leads to different interpretations of disfluencies.
+This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including non-native versus native speakers (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
 
 Recently, Matzinger, Pleyer, and Żywiczyński (2023) explored whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers.
-In their study, participants listened to native and non-native speakers answer trivial questions and requests, and were explicitly asked to rate the speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
+In their study, participants listened staged conversations where native and non-native speakers answered trivial questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
 Crucially, Matzinger et al.
-(2023) manipulated speakers' fluency by having answers prefaced with either short (200 ms) or long (1200 ms) pauses.
+(2023) manipulated speakers' fluency by manipulating inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses.
 For requests, long pauses were less likely to be associated with unwillingness for non-native compared to native speakers.
@@
 
-To date, most experimental evaluations of manner of speech have been explicit.
-Participants are asked to rate particular traits of speakers on a scale.
+As is the case for Matzinger et al.
+(2023), most studies evaluating the effects of manner of speech on pereptions of the speaker have used explicit ratings.
+Participants are asked to rate particular traits of speakers or what they say on a scale.
 Further, these ratings are elicited in non-social contexts, where participants do not have anything at stake.
 Although these experiments demonstrate that listeners show sensitivity to aspects of speech such as fluency and accent when asked to make explicit judgements about the speaker, they may not explain how listeners evaluate speech implicitly, when to do so is consequential.Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm.
-In this task, participants listen to a set of speakers provide descriptions of horses and are asked to distribute virtual tokens as `bets' on each horse's likelihood of winning a putative race.
+In this task, participants listen to a set of speakers provide descriptions of horses, and are asked to distribute virtual tokens as `bets' on each horse's likelihood of winning a putative race.
 This approach presents two advantages over previous experiments.
@@
 Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets (Butterworth, 2019).
-Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing).
-
-In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency and the speaker's identity as conveyed by their accent.
+Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing or its technical vocabulary).
+
+In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent.
 We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently.
@@
 A new sample fo 30 British English speaker rated the edited passages.
-A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, \emph{p} = .52), nor in the order in which they were ranked (all \textbar t\textbar{} \textless\$ 2).
+A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, \emph{p} = .52), nor in the order in which they were ranked (all \textbar t\textbar{} \textless{} 2).
 The final set of descriptions for the experiment can be found in Table \ref{tab:tab-horse-description-text}.
@@
 
-\caption{\label{tab:tab-horse-description-disfluent}Transcription of the disfluent horse descriptions.}
+\caption{\label{tab:tab-horse-description-disfluent}Transcriptions of the disfluent horse descriptions.}
 
@@
 
-To ensure that the resulting descriptions were perceived to be natural (i.e., our edited `fluent' audios were not clearly edited) and that they were perceived as differing in fluency (i.e., disfluent and `fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
+To ensure that the resulting descriptions were perceived to be natural (i.e., edits to the `fluent' audios were not obvious) and that they were perceived as differing in fluency (i.e., disfluent and `fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
 Participants were allocated to one of the 24 experimental lists, to ensure that our validation procedure was similar to how participants encountered stimuli in the actual experiment.
-Following Bosker, Quené, Sanders, and De Jong (2014) procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
+Following Bosker, Quené, Sanders, and De Jong (2014)`s procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
 We instructed participants to rate fluency by considering silent and filled pauses, speed of speech, and repairs, and to ignore speakers' accents and the content of their speech.
@@
 Table \ref{tab:tab-results-validation} shows the means (and standard deviations) of participants' ratings of fluency, naturalness, and accentedness.
-A linear mixed model for fluency ratings with fixed effects of fluency (treatment-coded, reference: fluent), speaker's linguistic background (treatment-coded, reference: native speaker), and their interaction, with random intercepts by participant and by horse description showed that fluency ratings differed significantly for the fluent and disfluent conditions (\(\hat{\beta} = -1.19\), 95\% CI \([-1.79, -0.58]\), \(t = -3.84\)).
+A linear mixed model for fluency ratings with fixed effects of fluency (treatment-coded, reference: fluent), speaker's linguistic background (treatment-coded, reference: native speaker), and their interaction, with random intercepts by participant and by horse description, showed that fluency ratings differed significantly for the fluent and disfluent conditions (\(\hat{\beta} = -1.19\), 95\% CI \([-1.79, -0.58]\), \(t = -3.84\)).
 The non-native speaker was perceived as more disfluent than the native speaker (\(\hat{\beta} = -1.37\), 95\% CI \([-1.97, -0.78]\), \(t = -4.51\)), in line with previous findings (Bosker, Quené, Sanders, \& Jong, 2014; Pinget et al., 2014), but the interaction between the two variables was not significant (\(\hat{\beta} = 0.15\), 95\% CI \([-0.49, 0.78]\), \(t = 0.45\)).
@@
 Table \ref{tab:tab-dist-money} and Figure \ref{fig:fig1} show the mean amount of money bet per speaker and fluency condition.
-On average, participants bet £25 on each horse.
+On average, participants bet £25 on when information was provided fluently.
 This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
@@
 Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)).
-There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\)) and importantly, no interaction between delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)), and no other significances (for speaker, \(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\); for the interaction \(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))}.
+There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\)) and importantly, no interaction between manner of delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)), and no other significances (for speaker, \(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\); for the interaction \(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))}.
 
@@
 
-Table \ref{tab:tab5} depicts the mean (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
+Table \ref{tab:tab5} depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
 Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score.
@@
 Cronbach's alpha showed that the scores for these attitudes were reliable (\(\alpha_{affect}\) = 0.80, \(\alpha_{status}\) = 0.93, \(\alpha_{solidarity}\) = 0.87).
-We explored differences between the native and the non-native speaker's evaluations in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for \emph{p} values.
+We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for \emph{p} values.
 
@@
 
-Analyses showed that speakers were rared differently across all six dimensions (see Table \ref{tab:tab6}).
+Analyses showed that speakers were rated differently across all six dimensions (see Table \ref{tab:tab6}).
 The largest differences were, unsurprisingly, in comprehensibility and accentedness, where the non-native speaker received lower ratings.
@@
 206 participants reported they would prefer to learn from the native spaker, and 154 preferred the non-native speaker.
-A \(\chi^2\) test of goodness of fit showed that there was a significant difference in participants' preferences (\(\chi^2\)(1) = 7.51, \emph{p} \textless{} .01).
+A \(\chi^2\) test of goodness of fit showed that this difference in preferences was reliable (\(\chi^2\)(1) = 7.51, \emph{p} \textless{} .01).
 
@@
 
-Listeners can attribute a speaker knowledgeability based on a range of cues, such as voice pitch or amplitude.
+Listeners can attribute knowledgeability to a speaker based on a range of cues, such as voice pitch or amplitude.
 Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995).
-However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in one's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009).
+However, speakers can be disfluent for reasons other than lack of confidence: For example, speaking in one's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009).
 In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance (Lev-Ari, 2015), which consequently leads native listeners to ``forgive'' what otherwise would be lead to a negative evaluation (Fairchild et al., 2020; Lorenzoni et al., 2022).
-In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
+In the present experiment, we explored whether attributions of lack of knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
 Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.
 
-The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced (Brennan \& Williams, 1995).
+The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced.
 Descriptions that included hesitation phenomena, in the form of filled pauses, led to smaller bets compared to their fluent counterparts.
@@
 Brennan and Williams (1995) attributed participants' ratings to inferences made about the speaker's mental state - specifically, inferences about the degree of confidence a speaker has in their knowledge.
-In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because the utterance is semantically and acoustically identical apart from the excision of disfluencies, an inference about a speaker's confidence based on those disfluencies is an important potential determinant of participants' decisions.
-
-This inference explanation would predict that listeners would forgive foreign disfluencies, in line with the expectations-based account.
-While previous research has reported that whether a filled pause affects processes involved in speech comprehension depending on speaker identity (e.g., Bosker, Quené, Sanders, \& De Jong, 2014), recent studies have failed to find this effect when it comes to speaker's attributions (Matzinger et al., 2023).
-In our experiment, participants distributed money similarly when either speaker provided disfluent descriptions, suggesting that listeners did not weigh in our (non-native) speaker's identity to interpret the disfluency.
+In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because utterances were semantically identical and acoustically identical apart from the excision of disfluencies and accent, an inference about a speaker's confidence based on those disfluencies is the most likely potential determinant of participants' decisions.
+
+The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions.
+This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension (Arnold et al., 2007; e.g., Bosker, Quené, Sanders, \& De Jong, 2014; Heller et al., 2015), and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations (e.g., Fairchild et al., 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; \textbf{lorenzonietal2020?}) possibly because native listeners expect them to produce those (Lev-Ari, 2015).
 This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.
+
+Nonetheless, our results align with recent studies that have failed to find this an interaction between disfluencies and nativeness when it comes to speaker's attributions (Matzinger et al., 2023).
+Matzinger et al.
+(2023) accounted for their findings as a the results of the degree with which a listener needs to model the speaker: Assessing a speaker's knowledge is not as socially engaging as other communicative contexts (e.g., granting a request) and consequently, inferring an interlocutor's cognitive state is not relevant.
+Interestingly, there are several differences between their paradigm and ours that shed doubts on whether this explanation applies to our results.
+Specifically, in Matzinger et al.
+(2023) participants were overhearing a conversation, and given their task (i.e., explicitly rate their perception on speaker's knowledge or confidence), accurately ascribing the cause of disfluency did not have any consequences.
+In contrast, our participants listened to speakers talking in isolation and, most importantly, assessing speakers' knowledgeability was crucial for performing their task.
+
 One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster.
@@
 Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty (Mol, Kuhlen, Van der Steen, \& Obbens, 2013).
-Considering the language attitudes triggered by both accents, the difference in speaker preference may more likely reflect the ease of comprehending the native speaker, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
-
-The experiment here also introduced a novel approach to measuring how certain the speaker is perceived.
-While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new venue to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
+The preference to learn in future occasions for the native speaker may be more likely to reflect the ease of comprehending them, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
+
+This experiment introduced a novel approach to measuring how certain the speaker is perceived to be.
+While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new set-up to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
 However, a potential shortcoming of our design has to do with how people approached the betting system.
@@
 (2014).
-Native `um's elicit prediction of low-frequency referents, but non-native `um's do not.
+Native 'um's elicit prediction of low-frequency referents, but non-native 'um's do not.
 \emph{Journal of Memory and Language}, \emph{75}, 104--116.
@@
 (2021).
-Are foreign-accented speakers that {``incredible''}?
+Are foreign-accented speakers that 'incredible'?
 The impact of the speaker's indexical properties on sentence processing.

### 2024-09-27 manuscript/manuscript_eb.Rmd
changes & version sent for feedback

@@
 keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
-wordcount         : "4774"
+wordcount         : "5173"
 
@@
 The final model included a random intercept by-item.
-Results were deemed significant at |t| > 2 [@baayen2008].
 
@@
 Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (`r mdlbet_m1$full_result$delivery_cont1`).
-There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between manner of delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and no other significances (for speaker, `r mdlbet_m1_all$full_result$speaker_cont1`; for the interaction `r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].
+There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between manner of delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and a main effect for speaker (`r mdlbet_m1_all$full_result$speaker_cont1`), but no significant interaction (`r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].
 
@@
 Cronbach's alpha showed that the scores for these attitudes were reliable ($\alpha_{affect}$ = `r affect_alpha`, $\alpha_{status}$ = `r status_alpha`, $\alpha_{solidarity}$ = `r solidarity_alpha`).
-We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.
+We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, Fluency, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.
 
@@
 Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours.
-This second model improved model fit ($\chi^2$(6) = 19.46, _p_ < .01).
-Besides a main effect of manner of delivery (`r mdlbet_attitudes$full_result$delivery_cont1`), the model showed an effect of affect, whereby higher ratings of affect were more likely to yield higher bettings (`r mdlbet_attitudes$full_result$affect`)
+This second model improved model fit ($\chi^2$(7) = 24.77, _p_ < .01).
+The model showed a main effect of manner of delivery (`r mdlbet_attitudes$full_result$delivery_cont1`).
+Although affect (`r mdlbet_attitudes$full_result$affect`) and fluency (`r mdlbet_attitudes$full_result$fluent`) were significant, they did not survive Bonferroni correction.
 
@@
 A $\chi^2$ test of goodness of fit showed that this difference in preferences was reliable ($\chi^2$(1) = 7.51, _p_ < .01).
+
+Following previous research suggesting the role of exposure to foreign-accented speech in its role to trust and comprehensibility, we explored whether exposure to native and non-native speakers played a role in participants' betting behaviour beyond that of speaker identity and manner of delivery.
+A similar linear mixed model to that employed in our main analysis, but with the addition of exposure, showed that it did not affect participants' betting behaviour (`r mdlbet_m1_exposure$full_results$exposure`)
 
@@
 The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions.
-This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension [e.g., @boskeretal2014; @arnoldetal2007; @helleretal2015], and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations [e.g., @fairchildetal2020; @lorenzonietal2020; @ippapafragou2022; @fairchildpapafragou2018] possibly because native listeners expect them to produce those [@levari2015].
+This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension [e.g., @boskeretal2014; @arnoldetal2007; @helleretal2015], and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations [e.g., @fairchildetal2020; @lorenzonietal2022; @ippapafragou2022; @fairchildpapafragou2018] possibly because native listeners expect them to produce those [@levari2015].
 This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.
@@
 
-Overall,
+Overall, our study shows that disfluency is a cue that listeners take as an index of speaker's knowledgeability.
+Importantly, in situations of uncertainty where individuals lack information to optimise their behaviour, the presence of disfluency biases their otherwise rational behaviour.
+This highlights individuals' tuning to the different ways in which a speaker's mental state is signalled in speech and how in turn it can affect their subsequent behaviours.
 

### 2024-09-27 manuscript/manuscript_eb.tex
changes & version sent for feedback

@@
 {}{\PatchFailed}
-\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 4774}
+\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 5173}
 \usepackage{lineno}
@@
 The final model included a random intercept by-item.
-Results were deemed significant at \textbar t\textbar{} \textgreater{} 2 (Baayen, 2008).
-
-Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)).
-There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\)) and importantly, no interaction between manner of delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)), and no other significances (for speaker, \(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\); for the interaction \(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))}.
+
+Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t(1433) = -3.99\), \(p < .001\)).
+There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t(1433) = 1.15\), \(p = .251\)) and importantly, no interaction between manner of delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t(1433) = 1.28\), \(p = .200\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.92\), 95\% CI \([-3.91, -1.92]\), \(t(2557.08) = -5.75\), \(p < .001\)), and a main effect for speaker (\(\hat{\beta} = 1.21\), 95\% CI \([0.21, 2.20]\), \(t(2557.09) = 2.38\), \(p = .017\)), but no significant interaction (\(\hat{\beta} = 0.93\), 95\% CI \([-1.06, 2.92]\), \(t(2557.12) = 0.92\), \(p = .358\))}.
 
@@
 Cronbach's alpha showed that the scores for these attitudes were reliable (\(\alpha_{affect}\) = 0.80, \(\alpha_{status}\) = 0.93, \(\alpha_{solidarity}\) = 0.87).
-We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for \emph{p} values.
+We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, Fluency, and Trustworthiness via paired t-test using Bonferroni correction for \emph{p} values.
 
@@
 Accentedness & 5.46 (2.1) & 6.84 (1.37)\\
+Fluency & 7.97 (1.43) & 6.11 (1.83)\\
 Affect & 5.77 (1.49) & 6.05 (1.32)\\
@@
 Accent & -11.51 & {}[-1.62, -1.15] & -1.39\\
+Fluency & 17.15 & {}[1.65, 2.08] & 1.87\\
 Affect & -3.54 & {}[-0.44, -0.13] & -0.29\\
@@
 Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours.
-This second model improved model fit (\(\chi^2\)(6) = 19.46, \emph{p} \textless{} .01).
-Besides a main effect of manner of delivery (\(\hat{\beta} = -2.71\), 95\% CI \([-4.03, -1.39]\), \(t = -4.02\)), the model showed an effect of affect, whereby higher ratings of affect were more likely to yield higher bettings (\(\hat{\beta} = 0.81\), 95\% CI \([0.14, 1.49]\), \(t = 2.35\))
+This second model improved model fit (\(\chi^2\)(7) = 24.77, \emph{p} \textless{} .01).
+The model showed a main effect of manner of delivery (\(\hat{\beta} = -2.71\), 95\% CI \([-4.03, -1.39]\), \(t(1436.00) = -4.03\), \(p < .001\)).
+Although affect (\(\hat{\beta} = 0.83\), 95\% CI \([0.15, 1.50]\), \(t(1436.09) = 2.41\), \(p = .016\)) and fluency (\(\hat{\beta} = -0.67\), 95\% CI \([-1.24, -0.10]\), \(t(1436.10) = -2.31\), \(p = .021\)) were significant, they did not survive Bonferroni correction.
 
@@
 A \(\chi^2\) test of goodness of fit showed that this difference in preferences was reliable (\(\chi^2\)(1) = 7.51, \emph{p} \textless{} .01).
+
+Following previous research suggesting the role of exposure to foreign-accented speech in its role to trust and comprehensibility, we explored whether exposure to native and non-native speakers played a role in participants' betting behaviour beyond that of speaker identity and manner of delivery.
+A similar linear mixed model to that employed in our main analysis, but with the addition of exposure, showed that it did not affect participants' betting behaviour ()
 
@@
 The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions.
-This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension (Arnold et al., 2007; e.g., Bosker, Quené, Sanders, \& De Jong, 2014; Heller et al., 2015), and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations (e.g., Fairchild et al., 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; \textbf{lorenzonietal2020?}) possibly because native listeners expect them to produce those (Lev-Ari, 2015).
+This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension (Arnold et al., 2007; e.g., Bosker, Quené, Sanders, \& De Jong, 2014; Heller et al., 2015), and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations (e.g., Fairchild et al., 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni et al., 2022) possibly because native listeners expect them to produce those (Lev-Ari, 2015).
 This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-baayen2008}{}}%
-Baayen, R. H. (2008). \emph{Analyzing linguistic data: A practical introduction to statistics using r}. Cambridge University Press. \url{https://doi.org/10.1017/CBO9780511801686}
-
 \leavevmode\vadjust pre{\hypertarget{ref-barlowetal2024}{}}%

### 2024-09-27 analysis/data-analysis.R

@@ -40,27 +40,27 @@ t.test(langatt_native$exposure, langatt_nonnative$exposure, paired = TRUE) # exp
 ## lme4 does not work well with sum coding, RSO stats UGent offers the following alternative:
 
 
-dexp1bet_prereg$flue_nat <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
-                                      dexp1bet_prereg$speaker == "native")
-dexp1bet_prereg$flue_non <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
-                                      dexp1bet_prereg$speaker == "nonnative")
-dexp1bet_prereg$dis_nat <- 1 * (dexp1bet_prereg$delivery != "fluent" & 
-                                      dexp1bet_prereg$speaker == "native")
-
-exp1_mdlbet_max <- lmer(
-  raw_money ~ delivery_cont * speaker_cont +
-    (-1 + flue_nat + flue_non + dis_nat | ppt) +
-    (1 | horse),
-  data = dexp1bet_prereg, 
-  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=2e5))
-)
-
-summary(exp1_mdlbet_max)
-hist(resid(exp1_mdlbet_max))
+# dexp1bet_prereg$flue_nat <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
+#                                       dexp1bet_prereg$speaker == "native")
+# dexp1bet_prereg$flue_non <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
+#                                       dexp1bet_prereg$speaker == "nonnative")
+# dexp1bet_prereg$dis_nat <- 1 * (dexp1bet_prereg$delivery != "fluent" & 
+#                                       dexp1bet_prereg$speaker == "native")
+# 
+# exp1_mdlbet_max <- lmer(
+#   raw_money ~ delivery_cont * speaker_cont +
+#     (-1 + flue_nat + flue_non + dis_nat | ppt) +
+#     (1 | horse),
+#   data = dexp1bet_prereg, 
+#   control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=2e5))
+# )
+# 
+# summary(exp1_mdlbet_max)
+# hist(resid(exp1_mdlbet_max))
 
 # singular fit
 
-mdlbet_m1 <- lmer(
+mdlbet_m1 <- lmerTest::lmer(
[…]

### 2024-09-27 analysis/data-visualization.R

@@ -19,12 +19,14 @@ library(wesanderson)
 # avg and sd of language attitudes dimensions, naturalness, accentedness, fluency, trustworthiness, ease of understanding, exposure to native and non-native speakers
 # papaja and gt are not friends
 # re doing this code to be able to use apa_table and also to refer to it in-text
+
 tab5 <- dexp1lang_prereg %>%
   select(c(18:24,38,39)) %>% mutate(speaker = ifelse(speaker=='native', 'Native Speaker', 'Non-native Speaker')) %>%
   rename_with(str_to_title) %>%
-  select(c("Speaker", "Easy", "Strong", "Affect", "Status", "Solidarity", "Trustworthy")) %>%
+  select(c("Speaker", "Easy", "Strong", "Affect", "Status", "Solidarity", "Trustworthy", "Fluent")) %>%
   rename(Comprehensibility = Easy,
-         Accentedness = Strong
+         Accentedness = Strong,
+         Fluency = Fluent
          ) %>%
   group_by(Speaker) %>%
   summarise(
@@ -32,6 +34,8 @@ tab5 <- dexp1lang_prereg %>%
     sd_easy = sd(as.numeric(Comprehensibility)),
     avg_strong = mean(as.numeric(Accentedness)),
     sd_strong = sd(as.numeric(Accentedness)),
+    avg_flu = mean(as.numeric(Fluency)),
+    sd_flu = sd(as.numeric(Fluency)),
     avg_aff = mean(as.numeric(Affect)),
     sd_aff = sd(as.numeric(Affect)),
     avg_stat = mean(as.numeric(Status)),
@@ -39,17 +43,18 @@ tab5 <- dexp1lang_prereg %>%
     avg_sol = mean(as.numeric(Solidarity)),
     sd_sol = sd(as.numeric(Solidarity)),
     avg_trust = mean(as.numeric(Trustworthy)),
-    sd_trust = sd(as.numeric(Trustworthy)),
+    sd_trust = sd(as.numeric(Trustworthy))
   ) %>% 
   dplyr::mutate(
     Comprehensibility = paste(round(avg_easy, 2), paste("(", round(sd_easy,2), ")", sep = ""), sep = " "),
     Accentedness = paste(round(avg_strong, 2), paste("(", round(sd_strong,2), ")", sep = ""), sep = " "),
+    Fluency = paste(round(avg_flu, 2), paste("(", round(sd_flu,2), ")", sep = ""), sep = " "),
[…]

### 2024-09-27 manuscript/manuscript_eb.Rmd
minor changes

@@
 We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently.
-If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners’ lower FOAK for the speaker.
+If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners’ lower trust in, or lower FOAK, for the speaker.
 However, disfluent descriptions provided by a non-native speaker may not impact listeners’ betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker’s knowledge.
-To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker [see @dragojevicgiles2016], perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived reliability of each speaker.
+To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker [see @dragojevicgiles2016], perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker.
 We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements [@boduchlevari2021].
@@
 This meant that we recruited 641 participants for a sample of 360.
+Participants were aged between 18 and 30, born and raised in the United Kingdom, and reported that they did not consider themselves as experts in horse races.
 Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the PPLS Ethics Committee (ref no 133-2223/3).
@@
 The task began with a cover story introducing two horse racing tipsters.
-Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race at Musselburgh Racecourse (Edinburgh).
+Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race.
 The cover story explained that the two tipsters were well-known experts in the field, and added that one of the speakers was a non-native English speaker (without specifying the nationality of either speaker), introducing the element of the speakers' linguistic backgrounds as well as the factor of competence.
@@
 
-All data pre-processing and analyses were carried out in R version 4.4.1 [@R-base], using the packages _tidyverse_ version 2.0.0 [@tidyverse], _ggplot_ version 3.5.1 [@ggplot2], and _wesanderson_ version for data wrangling and visualization.
+All data pre-processing and analyses were carried out in R version 4.4.1 [@R-base], using the packages _tidyverse_ version 2.0.0 [@tidyverse], _ggplot_ version 3.5.1 [@ggplot2], and _wesanderson_ version 0.3.7 for data wrangling and visualization.
 _lme4_ version 1.1-35.5 [@lme4] was used for data analysis, and _papaja_ version 0.1.2 [@R-papaja] for manuscript write-up.
@@
 
-Table \@ref(tab:tab-dist-money) and Figure \@ref(fig:fig1) show the mean amount of money bet per speaker and fluency condition.
+Table \@ref(tab:tab-dist-money) shows the mean amount of money bet per speaker and fluency condition.
 On average, participants bet £25 on when information was provided fluently.
@@
 )
-```
-
-```{r fig1, out.width="90%",fig.align='center', fig.cap="Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native)."}
-fig1
 ```
@@
 
-### Language attitudes
+### Language attitudes and post-experimental questionnaire
 

### 2024-09-27 manuscript/manuscript_eb.tex
minor changes

@@
 We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently.
-If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners' lower FOAK for the speaker.
+If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners' lower trust in, or lower FOAK, for the speaker.
 However, disfluent descriptions provided by a non-native speaker may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge.
-To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived reliability of each speaker.
+To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker.
 We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements (Boduch-Grabka \& Lev-Ari, 2021).
@@
 
-All data pre-processing and analyses were carried out in R version 4.4.1 (R Core Team, 2024), using the packages \emph{tidyverse} version 2.0.0 (Wickham et al., 2019), \emph{ggplot} version 3.5.1 (Wickham, 2016), and \emph{wesanderson} version for data wrangling and visualization.
+All data pre-processing and analyses were carried out in R version 4.4.1 (R Core Team, 2024), using the packages \emph{tidyverse} version 2.0.0 (Wickham et al., 2019), \emph{ggplot} version 3.5.1 (Wickham, 2016), and \emph{wesanderson} version 0.3.7 for data wrangling and visualization.
 \emph{lme4} version 1.1-35.5 (Bates, Mächler, Bolker, \& Walker, 2015) was used for data analysis, and \emph{papaja} version 0.1.2 (Aust \& Barth, 2023) for manuscript write-up.
@@
 
-Table \ref{tab:tab-dist-money} and Figure \ref{fig:fig1} show the mean amount of money bet per speaker and fluency condition.
+Table \ref{tab:tab-dist-money} shows the mean amount of money bet per speaker and fluency condition.
 On average, participants bet £25 on when information was provided fluently.
@@
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=0.9\linewidth,]{manuscript_eb_files/figure-latex/fig1-1}
-
-}
-
-\caption{Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native).}\label{fig:fig1}
-\end{figure}
-
 We modelled participants' betting behaviour in a linear mixed model.
@@
 
-\hypertarget{language-attitudes}{%
-\subsubsection{Language attitudes}\label{language-attitudes}}
+\hypertarget{language-attitudes-and-post-experimental-questionnaire}{%
+\subsubsection{Language attitudes and post-experimental questionnaire}\label{language-attitudes-and-post-experimental-questionnaire}}
 

### 2024-12-12 manuscript/manuscript_eb.Rmd
tidy-stuff

@@
 abstract: |
-  Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking).
-The presence of disfluencies, such as filled pauses (e.g., _uh_ or _um_ in English), elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge.
-On the other hand, listeners consider alternative explanations for the speaker to be underinformative: Specifically, non-native speakers are more likely to be forgiven when they fail to be informative.
-However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear.
-In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge.
-This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous.
-Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness.
-Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.
+  Whether an individual is perceived as knowledgeable by others can be biased by several potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking).
+Existing evidence for these effects tends to come from metalinguistic evaluations; here we examine the behavioral consequences of variations in the ways in which spoken messages are produced.
+Specifically,we investigate how attributions of knowledgeability are influenced by speech fluency, and by whether or not the speaker has a native accent, cues which have been previously shown to bias listeners’ evaluations of speakers and what they are saying.
+We use a novel horse-race betting paradigm, in which participants have to place bets on horses which have been described in short spoken passages.
+By manipulating the fluency (fluent or disfluent) and accent (native or non-native) with which the descriptions are produced, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge (e.g., nativeness).
+Overall, our results align with a broader body of literature suggesting that the effects of hesitation phenomena are context-independent.
+Importantly, we demonstrate that individuals’ meta-linguistic judgements can be measured through behavior, suggesting that these judgements have ecological importance beyond the laboratory.
 
 keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
-wordcount         : "5173"
+wordcount         : "5367"
 
 bibliography      : "references.bib"
+annotate_references: yes
+nocite            : |
+  @barlowetal2024
+  @levarikeysar2010
+  @boduchlevari2021
+  @stocker2017
+  @wetzeletal2021
+  @souzamarkman2013
+  @foucartetal2020
+  @foucarthartsuiker2021
 
@@
 footnotelist      : no
+acknowledgements  : "This work was funded by the Scottish Graduate School of Social Sciences via a Saltire Emerging Research awarded to EB.
+We thank Drs.
+Abby Pooley and Greta Gandolfi for lending us their voices for the experiment, and Dr.
+Umberto Noe for his insight on how to analyse our data."
 
+header-includes:
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
 classoption       : "man"
@@
 Speakers can be evaluated not only by what they say but also by how they say it.
-For example, vocal features of speech can affect perceptions of confidence and persuasion [@guyeretal2019speech], status and solidarity [@pittamgallois198], or even attractiveness [@feinbergetal2005].
-One speech feature consistently found to bias evaluations of the speaker is speech fluency.
-Speech which includes disfluencies, such as _uh_ or _um_ in English, can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995].
-Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility [@gluszeketal2011; @gluszekdovidio2010; @rakicetal2011; @levarikeysar2010].
-In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually.
-It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
+For example, features of speech can affect perceptions of confidence and persuasion [@guyeretal2019speech], status and solidarity [@pittamgallois198], or even attractiveness [@feinbergetal2005].
+Similarly, speech which includes disfluencies, such as *uh* or *um* in English, can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995].
+Interestingly, speech produced with an accent different from one's own---particularly a *foreign* accent---can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility [@gluszeketal2011; @gluszekdovidio2010; @rakicetal2011; @levarikeysar2010].
+Most of these studies, however, have relied on listeners' explicit judgements, which may not reflect everyday language comprehension [@armstrongetal1983]: Do these judgements arise even when individuals are not asked to make them?.
+In this study we tested whether listeners' evaluations of a speaker affect their decision-making, and if the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually.
+In what follows, we briefly describe how speech fluency and accent have been shown to bias listeners' evaluations.
 
 There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability.
-Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener[@jiangpell2015; @jiangpell2016a; @jiangpell2016b].
+Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener [@jiangpell2015; @jiangpell2016a; @jiangpell2016b].
 Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically [@goupiletal2021].
 These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies [@shribergetal1997; @shriberglickley1993; @grosjeandeschamps1975; @jiangpell2017].
-@brennanwilliams1995 demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers’ confidence in their knowledge.
-In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., _feeling of another's knowing_, FOAK.
-Among the cues that biased participants' assessments were filled pauses:  Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers’ reduced certainty about their knowledge.
+@brennanwilliams1995 demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers' confidence in their knowledge.
+In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., to rate their *feeling of another's knowing*, FOAK.
+Among the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge.
 In contrast, non-answers (i.e., 'I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause.
-@brennanwilliams1995 took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question [see also @smithclark1993].
+Brennan and Williams took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question [see also @smithclark1993].
 
@@
 In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations.
-On the one hand, speakers with a foregin accent are more likely to be negatively evaluated [e.g., @dragojevicgiles2016; @gluszekdovidio2010].
-Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021].
-These negative effects triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency [@levarikeysar2010], group membership, or a combination of both [@maihoffmann2014].
+On the one hand, speakers with a foreign accent are more likely to be negatively evaluated [e.g., @dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Lev-Ari & Keysar, 2010; Boduch-Graba & Lev-Ari, 2021; but cf.
+Souza & Markan, 2013; Stocker, 2017; Foucart, Costa, Morís-Fernández, & Hartsuiker, 2020; Foucart & Hartsuiker, 2021; Wetzel, Zufferey, & Gygax, 2021; Barlow et al., 2024).
+These negative effects triggered by a speaker's non-nativeness have been primarily accounted for in terms of processing fluency [@levarikeysar2010], whereby difficulties in understanding accented speech decreases processing fluency and consequently elicits negative evaluations about the source.
 
-On the other hand, there seem to be instances where being a non-native speaker is more advantageous.
-@fairchildetal2020 examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness.
-@fairchildetal2020 isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identities.
-In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention.
-Native speakers who were underinformative were more likely to be rated as unwilling to share the information.
+On the other hand, there seem to be instances where being a non-native speaker is advantageous.
+@fairchildetal2020 examined whether and how failures to provide all relevant information (i.e., being under-informative) are interpreted differently as a function of speakers' nativeness.
+In four experiments, participants read stories where a speaker (native/non-native) provided a description.
+Crucially, these descriptions failed to provide all relevant information (e.g., not naming all elements on a display, failing to list all uses of an invention).
+Participants were then asked to provide an explanation for the speaker's under-informativeness.
+As descriptions were presented in the written modality, any differences in attributions of under-informativeness would be solely guided by the putative speakers' identities, rather than, for example, by processing fluency.
+Native speakers who were under-informative were more likely to be rated as unwilling to share the information than under-informative non-native speakers.
 The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp.
@@
 
-One potential explanation is that non-native speakers are evaluated differently from native speakers due to expectations about their competence.
-Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018].
-This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted.
-Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker.
-In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022] or why non-native speech is processed more shallowly [@levarikeysar2012; @hanulikovetal2012].
+One potential explanation for Fairchild et al.'s (2020) results is that non-native speakers are evaluated differently from native speakers due to expectations about their competence.
+Non-native speakers' accents may invoke stereotypes that suggests that these speakers are less competent linguistically than native speakers [@levari2015; @fairchildpapafragou2018].
+This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect the ways in which their speech is comprehended and interpreted.
+For example, in the case of under-informativeness, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors, such as ill will, when produced by a native speaker.
+In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], or how syntactic errors are processed [@hanulikovetal2012].
 
-Interestingly, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
-For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be [@jiangetal2019; @caballeropell2020].
-Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and are perceived as such by native listeners [@pingetetal2014], it is possible that a speaker's nativeness leads to different interpretations of disfluencies.
+Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @gkalitsiouwerle2023] and are perceived as such by native listeners [@pingetetal2014], it is possible that a speaker's non-nativeness leads to different interpretations of disfluencies.
 This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including non-native versus native speakers [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
 
-Recently, @matzingeretal2023 explored whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers.
-In their study, participants listened staged conversations where native and non-native speakers answered trivial questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
-Crucially, @matzingeretal2023 manipulated speakers' fluency by manipulating inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses.
-For requests, long pauses were less likely to be associated with unwillingness for non-native compared to native speakers.
+Recently, @matzingeretal2023 investigated whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers.
+In their study, participants listened to staged conversations in which native and non-native speakers answered trivia questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
+Crucially, speakers' fluency was manipulated by having different inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses.
+For requests, long pauses were more likely to be associated with unwillingness for native compared to non-native speakers.
 However, FOAK ratings did not differ between speakers: Long pauses produced by either speaker were likely to be taken as reflecting low confidence and low knowledge.
-@matzingeretal2023 attribute this pattern to different conversational contexts: Requests tap into speakers' cooperativeness, and thus in this context, tuning to the interlocutor's mental state and stereotyping might be more relevant than evaluating the speaker's competence (i.e., knowledge).
+Matzinger et al.
+attributed this pattern to the degree with which a speaker's mental state is relevant across conversational contexts.
 
-As is the case for @matzingeretal2023, most studies evaluating the effects of manner of speech on pereptions of the speaker have used explicit ratings.
+As is the case for @matzingeretal2023, most studies evaluating the effects of manner of speech on perceptions of the speaker have used explicit ratings.
 Participants are asked to rate particular traits of speakers or what they say on a scale.
-Further, these ratings are elicited in non-social contexts, where participants do not have anything at stake.
-Although these experiments demonstrate that listeners show sensitivity to aspects of speech such as fluency and accent when asked to make explicit judgements about the speaker, they may not explain how listeners evaluate speech implicitly, when to do so is consequential.Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm.
+Explicit measures as those are more likely to be affected by factors such as self-presentation and less likely to reflect how individuals would behave [@greenwaldetal2002].
+In contrast, implicit measures overcome these obstacles while still being able to predict behaviours: For example the Implicit Association Test can predict racist behaviours [@mcconellleibold2001; although see @paynehannay2021 for whether IAT scores are better conceptualised as an aggregation rather than at the individual level].
+In the case of evaluations about the speaker, they tend to be elicited in non-social contexts: Participants are either overhearers [e.g., @matzingeretal2023] or simply attend to a previously recorded speaker [e.g., @levarikeysar2010; @ippapafragou2022; @brennanwilliams1995].
+Further, in these experiments, participants have nothing at stake i.e., they are evaluating the speaker, but they do not have to perform any behaviour following the utterance they just heard.
+While experiments eliciting metalinguistic judgements shed light on what factors may affect how a speaker is perceived, the lack of interaction on participant's behalf entails that these findings may not explain how listeners evaluate speech implicitly, when to do so is consequential.
+
+Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm.
 In this task, participants listen to a set of speakers provide descriptions of horses, and are asked to distribute virtual tokens as 'bets' on each horse's likelihood of winning a putative race.
 This approach presents two advantages over previous experiments.
-First, in the horse-race paradigm, participants are not explicitly asked to evaluate a certain trait of the speaker (in this case, how knowledgeable they are).
-Instead, we take participants' allocations of `betting money' as an indirect measurement of their perceptions of speakers' knowledge.
+First, in the horse-race paradigm, participants are not explicitly asked to evaluate a specific trait of the speaker (in this case, how knowledgeable they are).
+Instead, we take participants' allocations of \`betting money' as an indirect measurement of their perceptions of speakers' knowledge.
 Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets [@butterworth2019].
-Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing or its technical vocabulary).
+Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are not familiar with the world of horse racing or its technical vocabulary).
 
-In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent.
+In a pre-registered study, we set up to test whether and how perceptions of knowledgeability are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent.
 We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently.
-If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners’ lower trust in, or lower FOAK, for the speaker.
-However, disfluent descriptions provided by a non-native speaker may not impact listeners’ betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker’s knowledge.
+If listeners are sensitive to speaker identity when making judgements about knowledge and confidence following disfluent speech, then descriptions peppered with disfluencies provided by a native speaker should result in less money bet, reflecting listeners' lower trust in, or lower FOAK, for this speaker compared to disfluent descriptions provided by a non-native speaker.
+The non-native disfluent descriptions may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge.
 To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker [see @dragojevicgiles2016], perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker.
@@
 
-All experimental stimuli can be found at https://osf.io/zsut7/.
+Our pre-registration, all experimental stimuli and scripts can be found at <https://osf.io/zsut7/>. Deviations from the original pre-registration (e.g., additional analysis) are marked as such.
 
@@
 We explored the required number of participants for a study with a power higher than .8 for the interaction between fluency and speaker identity.
-We conducted a 1000 simulations per different combinations of the effect size of the interaction (ranging from small to medium) and the standard deviation of the residuals.
+We conducted 1000 simulations per different combinations of the effect size of the interaction (ranging from small to medium) and the standard deviation of the residuals.
 In this analysis, we assumed a medium effect size of fluency and no effect of speaker identity.
@@
 
-In our pre-registration, we stipulated that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study.
-Further, we would exclude from analysis data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four, or considered themselves experts in horse races.
-This meant that we recruited 641 participants for a sample of 360.
-Participants were aged between 18 and 30, born and raised in the United Kingdom, and reported that they did not consider themselves as experts in horse races.
-Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the PPLS Ethics Committee (ref no 133-2223/3).
+In our pre-registration, we stipulated that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could take part in the study.
+Further, we would exclude from analyse data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four of a 9-point scale (see Procedure section), or considered themselves experts in horse races.
+This meant that we recruited 641 participants for a sample of 360 (N = 268 rated the audio lower than four, 9 reported the manipulation, 11 rated themselves as experts in horse races).
+Participants were aged between 18 and 30, and born and raised in the United Kingdom.
+Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the University of Edinburgh PPLS Ethics Committee (ref no 133-2223/3).
 Participants were reimbursed £1.50 for a 10-minutes experiment.
@@
 ## Visual stimuli
+
+```{r validation-images}
+
+visual <- read_csv('../stimuli/visual-stimuli/validation/validation-images.csv')
+
+library(dplyr)
+library(MASS)
+library(car)
+library(lme4)
+
+# move ranking so it's one column the position the other is the horse
+
+visual_pos <- visual %>%
+  pivot_longer(c(2:9), names_to = "Horse", values_to = "Position")
+
+visual_rank <- visual %>%
+  pivot_longer(c(10:17), names_to = "Horse", values_to = "Rank")
+
+# Individual likelihood to win a race
+
+# summary(aov(Position ~ Horse, data = visual_pos))
+
+# for manuscript
+
+mdl_visualval <-
+  apa_print(aov(Position ~ Horse, data = visual_pos))
+
+# Ranking data
+
+visual_rank <- visual_rank %>%
+  mutate(
+    Horse = as.factor(Horse),
+    Rank = as.factor(Rank)
+  )
+
+# NB polr is not available for newer versions of R, which is why here we are typing the results by hand (I updated R and now I can't use polr)
+
+# model_rank <- polr(Rank ~ Horse, data = visual_rank)
+# summary(model_rank)
+# newdata <- data.frame(Horse =levels(visual_rank$Horse))
+# 
+# (phat <- predict(object = model_rank, newdata, type="p"))
+
+```
 
@@
 
-A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (F(7) = 0.5, _p_ = .83).
-An ordinal logistic regression showed that none of the horses were more likely to be ranked differently from the others (all |t| < 2).
+A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (`r mdl_visualval$full_result$Horse`).
+An ordinal logistic regression showed that none of the horses were more likely to be ranked differently from the others (all \|t\| \< 2).
 We therefore selected four out of the eight images as visual stimuli.
@@
 
-We used four descriptions of racing horses from _The Racing Post_, retrieved on October 2018, originally edited and used by @butterworth2019.
+```{r validation-descriptions}
+
+dval_descriptions <- read_csv('../stimuli/horse-descriptions/validation/data-validation-butterworth1.csv')
+
+# Information about variables
+# ID: Prolific ID
+# H1_independent rate_4 and so on: likelihood for each horse of winning the race, on a 10-point scale
+# Horse1_Position and so on: position of each horse (relative to the others) of winning a race (i.e., assuming the four of them are competing against one another)
+# Bet: Whether participants had bet on horse races before (1 = No, 2 = Yes)
+# Expertise: How much participants agree with the statement 'I am an expert on horse races'  on a 5-point scale (1: Strongly disagree, 5: Strongly agree)
+
+# Questions to answer
+# H1: Is there a difference in the likelihood of each horse to win individually depending on the description?
+# H2: Is there a difference in rankings attributable to horses' description?
+
+# H1 to answer = score_winning ~ horse 
+# H2 to answer = position ~ horse (ordinal regression)
+
+# Data wrangling
+
+# we to change columns to rows for horses and their position
+
+dval_descriptionsrank <- dval_descriptions %>% pivot_longer(c(Horse1_Position, Horse2_Position, Horse3_Position, Horse4_Position),
+                                                    names_to = "Horse", values_to = "Position") %>%
+  mutate(
+    Horse = case_when(Horse == "Horse1_Position" ~ "Horse1",
+                      Horse == "Horse2_Position" ~ "Horse2",
+                      Horse == "Horse3_Position" ~ "Horse3",
+                      Horse == "Horse4_Position" ~ "Horse4")
+  ) %>%
+  dplyr::select(ID, Horse, Position, Bet, Expertise)
+
+# we also want a column for score and another one for horse
+
+dval_descriptionsscore <- dval_descriptions %>% pivot_longer(c(H1_independent, H2_independent, H3_independent, H4_independent),
+                                                    names_to = "Horse", values_to = "Score_winning") %>%
+  mutate(
+    Horse = case_when(Horse == "H1_independent" ~ "Horse1",
+                      Horse == "H2_independent" ~ "Horse2",
+                      Horse == "H3_independent" ~ "Horse3",
+                      Horse == "H4_independent" ~ "Horse4")
+  ) %>%
+  dplyr::select(ID, Horse, Score_winning, Bet, Expertise)
+
+# merge
+
+dval_descriptions <- left_join(dval_descriptionsrank, dval_descriptionsscore)
+
+# wrang data
+
+dval_descriptions <- dval_descriptions %>%
+  mutate(
+    Position = as.factor(Position),
+    Horse = as.factor(Horse),
+    ID = as.factor(ID),
+    #Bet = ifelse(pilot_materials_ug$Bet == 1, 'No', 'Yes'),
+    Expertise = case_when(
+      dval_descriptions$Expertise == 1 ~ 'Strongly disagree',
+      dval_descriptions$Expertise == 2 ~ 'Somewhat disagree',
+      dval_descriptions$Expertise == 3 ~ 'Neither',
+      dval_descriptions$Expertise == 4 ~ 'Somewhat agree',
+      dval_descriptions$Expertise == 5 ~ 'Strongly agree'
+    )
+  )
+
+# summary statistics
+
+# table(dval_descriptions$Score_winning, dval_descriptions$Horse)
+
+# let's see how many people are into betting
+# 
+# dval_descriptions  %>%
+#   filter(!duplicated(ID)) %>%
+#   count(Bet)
+# 
+# dval_descriptions  %>%
+#   filter(!duplicated(ID)) %>%
+#   count(Expertise)
+
+# psych::describeBy(dval_descriptions$Score_winning, dval_descriptions$Horse)
+
+# Individual likelihood of winning
+
+# summary(aov(Score_winning ~ Horse, data = dval_descriptionsscore))
+
+# for manuscript
+
+mdl_valbut1 <- apa_print(
+  aov(Score_winning ~ Horse, data = dval_descriptionsscore)
+)
+
+# import data
+# all saved in the same csv file
+
+dval_descriptions <- read_csv('../stimuli/horse-descriptions/validation/data-validation-butterworth2.csv')
+
+# Information about variables
+# ID: Prolific ID
+# H1_independent rate_4 and so on: likelihood for each horse of winning the race, on a 10-point scale
+# Horse1_Position and so on: position of each horse (relative to the others) of winning a race (i.e., assuming the four of them are competing against one another)
+# Bet: Whether participants had bet on horse races before (1 = No, 2 = Yes)
+# Expertise: How much participants agree with the statement 'I am an expert on horse races'  on a 5-point scale (1: Strongly disagree, 5: Strongly agree)
+
+# Questions to answer
+# H1: Is there a difference in the likelihood of each horse to win individually depending on the description?
+# H2: Is there a difference in rankings attributable to horses' description?
+
+# H1 to answer = score_winning ~ horse (lm), 
+# H2 to answer = position ~ horse (ordinal regression)
+
+# Data wrangling
+
+# we to change columns to rows for horses and their position
+
+dval_descriptions_rank <- dval_descriptions %>% pivot_longer(c(SS_Position, FW_Position, BB_Position, A_Position),
+                                                    names_to = "Horse", values_to = "Position") %>%
+  mutate(
+    Horse = case_when(Horse == "SS_Position" ~ "Silver Sky",
+                      Horse == "FW_Position" ~ "Fire Walker",
+                      Horse == "BB_Position" ~ "Black Blade",
+                      Horse == "A_Position" ~ "Apocalypse")
+  ) %>%
+  dplyr::select(ID, Horse, Position, Bet, Expertise)
+
+# we also want a column for score and another one for horse
+
+dval_descriptions_score <- dval_descriptions %>% pivot_longer(c(SS_independent, FW_independent, BB_independent, A_independent),
+                                                    names_to = "Horse", values_to = "Score_winning") %>%
+  mutate(
+    Horse = case_when(Horse == "SS_independent" ~ "Silver Sky",
+                      Horse == "FW_independent" ~ "Fire Walker",
+                      Horse == "BB_independent" ~ "Black Blade",
+                      Horse == "A_independent" ~ "Apocalypse")
+  ) %>%
+  dplyr::select(ID, Horse, Score_winning, Bet, Expertise)
+
+# merge
+
+dval_descriptions <- left_join(dval_descriptions_rank, dval_descriptions_score)
+
+# wrang data
+
+dval_descriptions <- dval_descriptions %>%
+  mutate(
+    Position = as.factor(Position),
+    Horse = as.factor(Horse),
+    ID = as.factor(ID),
+    #Bet = ifelse(pilot_materials_ug$Bet == 1, 'No', 'Yes'),
+    # Expertise = case_when(
+    #   pilot_materials_ug$Expertise == 1 ~ 'Strongly disagree',
+    #   pilot_materials_ug$Expertise == 2 ~ 'Somewhat disagree',
+    #   pilot_materials_ug$Expertise == 3 ~ 'Neither',
+    #   pilot_materials_ug$Expertise == 4 ~ 'Somewhat agree',
+    #   pilot_materials_ug$Expertise == 5 ~ 'Strongly agree',
+    #   TRUE ~ 'Boh'
+    # )
+  )
+
+# summary statistics
+
+# table(dval_descriptions$Score_winning, dval_descriptions$Horse)
+
+# let's see how many people are into betting
+
+# dval_descriptions  %>%
+#   filter(!duplicated(ID)) %>%
+#   count(Bet)
+# 
+# dval_descriptions  %>%
+#   filter(!duplicated(ID)) %>%
+#   count(Expertise)
+
+# psych::describeBy(dval_descriptions$Score_winning, dval_descriptions$Horse)
+
+# Individual likelihood of winning
+
+# ummary(aov(Score_winning ~ Horse, data = dval_descriptions_score))
+
+# model for manuscript
+
+mdl_valbut2 <- apa_print(
+  aov(Score_winning ~ Horse, data = dval_descriptions_score)
+)
+
+# Ranking data
+
+# model_rank <- polr(as.factor(Position) ~ Horse, data = dval_descriptions_rank)
+# summary(model_rank)
+# 
+# newdata <- data.frame(Horse = rep(c("Silver Sky", "Fire Walker", "Black Blade", "Apocalypse"), 1)
+#                      # Bet = rep(c("Yes", "No"), 6),
+#                       #Expertise = rep(c("Strongly disagree", "Somewhat disagree", "Somewhat agree"),4)
+#                      )
+# 
+# (phat <- predict(object = model_rank, newdata, type="p"))
+
+```
+
+We used four descriptions of racing horses from *The Racing Post*, retrieved on October 2018, originally edited and used by @butterworth2019.
 Each passage consisted of three to four sentences describing a horse and its performance in previous races.
@@
 
-Based on these results, we further edited the descriptions as some descriptions were more likely to be rated as winning horses.
-A new sample fo 30 British English speaker rated the edited passages.
-A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, _p_ = .52), nor in the order in which they were ranked (all |t| < 2).
+A one-way repeated measures ANOVA showed that some descriptions were more likely to be rated as winning horses (`r mdl_valbut1$full_result$Horse`).
+Therefore, we edited those passages and had a new sample of 30 British English speaker rate them.
+A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (`r mdl_valbut2$full_result$Horse`), nor in the order in which they were ranked (all \|t\| \< 2).
 The final set of descriptions for the experiment can be found in Table \@ref(tab:tab-horse-description-text).
@@
 The impression given in both runs is that Fire Walker should handle the demands of the extra furlong and Charlie Hills is looking forward to the test.
-The trainer said ''He's done really well for a little break, his work's been good and I couldn't be more pleased with him''.",
+The trainer said ``He\'s done really well for a little break, his work\'s been good and I couldn\'t be more pleased with him''.",
     "Silver Sky, a runner-up of a seven-furlong maiden at Naas on his debut last month, the son of Invincible Spirit ran crack French colt Persian King to a neck in the Group 3 Autumn Stakes over today's trip at Newmarket two weeks ago and his trainer believes he has done well since.
-O'Brien said ''Silver Sky is a fine big colt and a talented one''.",
+O'Brien said ``Silver Sky is a fine big colt and a talented one''.",
     "Apocalypse has put in a string of consistent performances, most recently finishing third to Norway in the Zetland.
-''He's had a very solid year'' said trainer Archie Watson.
-''He ran a good race in the Zetland, beaten only a length and a quarter, and I think the field here is of a similar level so I'm more than happy for him to take his chance''.",
+``He's had a very solid year'' said trainer Archie Watson.
+``He ran a good race in the Zetland, beaten only a length and a quarter, and I think the field here is of a similar level so I'm more than happy for him to take his chance''.",
     "Black Blade proved the market all wrong as the complexion of the 6.5-furlong novice race changed dramatically in the final two furlongs, with the Rebel Racing premier-owned newcomer under Tom Queally collaring long-time leaded Monsieur Noir.
-Spencer said: ''He did it well.
+Spencer said: ``He did it well.
 He's a nice horse.
-We always thought had a bright future''.")
+We always thought he had a bright future''.")
   )
@@
 
-We recorded a British English native speaker and a non-native (L1: Italian) English speaker to create the auditory stimuli.
-Both speakers were female.
+We recorded a British English native speaker (Darrington area) and a non-native (L1: Italian) English speaker to create the auditory stimuli.
+Both speakers were female and of similar age.
 Passages were recorded one at a time.
@@
 To avoid differences between the descriptions provided by the speakers, they were allowed to look at the descriptions as they spoke if they could not remember the continuation.
-We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (see Table \@ref(tab:tab-horse-description-disfluent)).
+We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (recordings can be found on OSF).
 To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the 'Tempo' function.
@@
 
-tab1A <- data.frame(
-    Horse = c("Fire Walker", "Silver Sky", "Apocalypse", "Black Blade"),
-    Description = c("FP-um Fire Walker is looking SP strong thanks to his (elongation) SP come-from-behind success SP FP-er in the Acomb Stakes.
+# Log: 22/10/2024 Rob recommended moving this to an Appendix
+# or all together just refer to the stimuli on OSF so they can hear to it
+
+# tab1B <- data.frame(
+#     Horse = c("Fire Walker", "Silver Sky", "Apocalypse", "Black Blade"),
+#     Description = c("FP-um Fire Walker is looking SP strong thanks to his (elongation) SP come-from-behind success SP FP-er in the Acomb Stakes.
 FP-um The (elongation) impression given SP in both runs FP-uh is that Fire Walker should SP handle the demands of SP the extra furlong and FP-uh Charlie Hills is looking forward to the test.
 The trainer said ''He's done (elongation) FP-um really well for a little break, FP-uh his work's been good and I couldn't be more pleased with him''.",
-    "Silver Sky, FP-uh a runner-up of -a seven-furlong maiden at Naas on his (elongation) debut last month.
+#     "Silver Sky, FP-uh a runner-up of -a seven-furlong maiden at Naas on his (elongation) debut last month.
 FP-uh The son of Invincible Spirit SP  ran (elongation) crack French colt Persian King   to a neck in the FP-uh  Group 3 Autumn Stakes.
@@
 O'Brien said FP-uh ''Silver Sky is a fine big colt and a talented one''.",
-    "FP Apocalypse has put in a (elongation-ish) string SP of consistent performances, FP most recently finishing third to SP Norway in the Zetland.
+#     "FP Apocalypse has put in a (elongation-ish) string SP of consistent performances, FP most recently finishing third to SP Norway in the Zetland.
 FP ''He's had a very solid year'' said trainer SP FP Archie Watson.
 ''He ran a SP good race in the Zetland, SP FP SP beaten only a length and a quarter, and I think the field here SP is of a similar level so I'm- I'm more than happy for him to (elongation-ish) take his chance''.",
-    "FP-um Black SP Blade proved SP FP-uh the market all wrong as the complexion SP of the 6.5 furlong SP novice SP race FP-um changed dramatically in SP the final two furlong.
+#     "FP-um Black SP Blade proved SP FP-uh the market all wrong as the complexion SP of the 6.5 furlong SP novice SP race FP-um changed dramatically in SP the final two furlong.
 SP FP-uh with the  Rebel Racing SP premier-owned SP newcomer under Tom SP Queally FP-um SP collaring long-time leaded Monsieur Noir.
@@
 FP-uh We always thought he had a bright future''.")
-  )
-
-apa_table(
-  tab1A,
-  caption = "Transcriptions of the disfluent horse descriptions.",
-  align = c("m{2cm}", "m{13cm}")
-)
+#   )
+# 
+# apa_table(
+#   tab1B,
+#   caption = "Transcriptions of the disfluent horse descriptions of the native speaker.",
+#   note = "Annotation scheme:
+#   FP: Filled pause, distinguished between um and uh; SP: Silent pause.",
+#   align = c("m{2cm}", "m{13cm}"),
+#   landscape = TRUE
+# )
 
@@
 Participants were allocated to one of the 24 experimental lists, to ensure that our validation procedure was similar to how participants encountered stimuli in the actual experiment.
-Following @boskeretal2014's procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
-We instructed participants to rate fluency by considering silent and filled pauses, speed of speech, and repairs, and to ignore speakers' accents and the content of their speech.
+Following Bosker et al.'s procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
+We instructed participants to rate fluency by considering silent and filled pauses, speech rate, and repairs, and to ignore speakers' accents and the content of their speech.
 Participants additionally rated on a 9-point scale each recording's naturalness (defined as how likely it was that the audio had been recorded in one go; 1: not unlikely at all; 9: very likely), and accentedness (while ignoring the perceived speaker's proficiency in the language; 1: not accented at all, 9: very accented).
@@
     Naturalness = paste(round(avg_nat, 2), paste("(", round(sd_nat,2), ")", sep = ""), sep = " "),
-    Accentedness = paste(round(avg_acc, 2), paste("(", round(sd_acc,2), ")", sep = ""), sep = " ")) %>%
-  select(c(Speaker, Delivery, Fluency, Naturalness, Accentedness))
+    Accentedness = paste(format(round(avg_acc, 2), nsmall = 2), paste("(", round(sd_acc,2), ")", sep = ""), sep = " ")) %>% # otherwise table isn't displayed in apa style
+  dplyr::select(.,c(Speaker, Delivery, Fluency, Naturalness, Accentedness))
 
@@
 ```
+
 ```{r dval-analysis}
@@
 
+# ACCENTEDNESS ANALYSIS AS PER ROB'S REQUEST
+
+mdl_validation_acc <- apa_print(dval %>%
+  filter(trial_status == "accentedness") %>%
+  mutate(delivery = factor(delivery, levels = c("fluent", "disfluent"))) %>%
+  lmer(
+    as.numeric(response) ~ delivery * speaker +
+      (1 + delivery | participant_ID) + (1 | description),
+    data = .
+  ))
+
 ```
@@
 An identical model for naturalness ratings showed no significant differences by fluency (`r mdl_validation_nat$full_result$deliverydisfluent`), speaker's linguistic background (`r mdl_validation_nat$full_result$speakernonnative`) or their interaction (`r mdl_validation_nat$full_result$deliverydisfluent_speakernonnative`).
+Finally, an identical model for accentedness only showed a significant difference for speaker's linguistic background (`r mdl_validation_acc$full_result$speakernonnative`).
 
@@
 At the beginning of the experiment, participants were shown four pictures of the horses that they had been told would take part in the race, alongside their names.
-Participants were instructed to distribute one-hundred pounds in betting money across the four horses based on the likelihood they thought each horse had of winning: They could split the bets as they wished, and they did not have to spend all the money.
-Each participant was randomly assigned to one out of 24 groups, so that they would listen to each speaker twice, one in each fluency level.
+Participants were instructed to distribute one hundred pounds in betting money across the four horses based on the likelihood they thought each horse had of winning: They could split the bets as they wished, and they did not have to spend all the money.
+Each participant was randomly assigned to one out of 24 lists, so that they would listen to each speaker twice, one in each fluency level.
 The order in which horses were presented was randomised.
@@
 Participants were allowed to modify their previous bets every time they heard a new description.
-If the sum of bets made at any point was more than the allotted maximum, they were asked to re-distribute their bets until the total was below one-hundred pounds.
+If the sum of bets made at any point was more than the allotted maximum, they were asked to re-distribute their bets until the total was below or equal to one hundred pounds.
 
@@
 Additional questions included ratings on a 9-point scale of how natural the audio sounded (1: unnatural, edited; 9: natural, unedited), and two questions measuring participants' exposure to native and non-native accented English (1: never; 9: always).
-Likewise, we measured participants’ previous experience with betting and their perceived knowledge of horse races (two questions: Whether they had bet on horse races in the past, and to rate on a 5-point scale, from 'Strongly disagree' to 'Strongly agree', how closely they identified with the statement 'I am an expert on horse races').
+Likewise, we measured participants' previous experience with betting and their perceived knowledge of horse races (two questions: Whether they had bet on horse races in the past, and to rate on a 5-point scale, from 'Strongly disagree' to 'Strongly agree', how closely they identified with the statement 'I am an expert on horse races').
 Finally, we included an open-ended question for participants to report what guided their decision-making, as well as their perception of the experiment's aim.
@@
 
-All data pre-processing and analyses were carried out in R version 4.4.1 [@R-base], using the packages _tidyverse_ version 2.0.0 [@tidyverse], _ggplot_ version 3.5.1 [@ggplot2], and _wesanderson_ version 0.3.7 for data wrangling and visualization.
-_lme4_ version 1.1-35.5 [@lme4] was used for data analysis, and _papaja_ version 0.1.2 [@R-papaja] for manuscript write-up.
-Scripts can be found at https://osf.io/zsut7/
+All data pre-processing and analyses were carried out in R version 4.4.1 [@R-base], using the packages *tidyverse* version 2.0.0 [@tidyverse], *ggplot* version 3.5.1 [@ggplot2], and *wesanderson* version 0.3.7 for data wrangling and visualization.
+*lme4* version 1.1-35.5 [@lme4] was used for data analysis, and *papaja* version 0.1.2 [@R-papaja] for manuscript write-up.
+Scripts can be found at <https://osf.io/zsut7/>.
 
@@
 Table \@ref(tab:tab-dist-money) shows the mean amount of money bet per speaker and fluency condition.
-On average, participants bet £25 on when information was provided fluently.
-This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
-However, disfluent instructions seem to lower the amount of money bet.
+On average, participants bet £24 on when information was provided fluently while disfluent instructions seem to lower the amount of money bet.
 
@@
 
-We modelled participants' betting behaviour in a linear mixed model.
+We modelled participants' betting behaviour using a linear mixed model.
 We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded.
@@
 We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept.
-The final model included a random intercept by-item.
+The final model only included a random intercept by-item.
 
@@
 Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (`r mdlbet_m1$full_result$delivery_cont1`).
-There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between manner of delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and a main effect for speaker (`r mdlbet_m1_all$full_result$speaker_cont1`), but no significant interaction (`r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].
+There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and no interaction between manner of delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)[^1].
+
+[^1]: An identical model including the 281 excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and a main effect for speaker (`r mdlbet_m1_all$full_result$speaker_cont1`), but no significant interaction (`r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)
 
@@
 
-Table \@ref(tab:tab5) depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
+Table \@ref(tab:tab7) depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
 Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score.
-For the _Affect_ dimension, we reverse-scored items measuring negative affect.
+For the *Affect* dimension, we reverse-scored items measuring negative affect.
 Cronbach's alpha showed that the scores for these attitudes were reliable ($\alpha_{affect}$ = `r affect_alpha`, $\alpha_{status}$ = `r status_alpha`, $\alpha_{solidarity}$ = `r solidarity_alpha`).
-We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, Fluency, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.
+We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, Fluency, and Trustworthiness via paired t-test using Bonferroni correction for *p* values.
 
-```{r tab5}
-apa_table(tab5,
-          caption = "Average score (and standard deviation) in each dimension by speaker.")
-```
-```{r tab6}
-apa_table(tab6,
-          caption = "Paired t test for each dimension between speakers.")
+```{r tab7}
+# 22/10/2024: Rob recommended merging tab5 and tab6
+
+tab7 <- left_join(tab5, tab6)
+
+apa_table(tab7,
+          caption = "Average score (and standard deviation) in each dimension by speaker, and paired t-test for each dimension between speakers. ")
 ```
 
-Analyses showed that speakers were rated differently across all six dimensions (see Table \@ref(tab:tab6)).
-The largest differences were, unsurprisingly, in comprehensibility and accentedness, where the non-native speaker received lower ratings.
-
-Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours.
-This second model improved model fit ($\chi^2$(7) = 24.77, _p_ < .01).
+Analyses showed that speakers were rated differently across all seven dimensions (see Table \@ref(tab:tab7)).
+The largest differences were, unsurprisingly, in the linguistic variables for comprehensibility, fluency and accentedness.
+The native speaker was rated as more comprehensible, more fluent and less accented.
+Following our pre-registered analysis, we included these seven variables and their interaction with speaker identity to our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours.
+This second model improved model fit ($\chi^2$(14) = 33.67, *p* \< .01).
 The model showed a main effect of manner of delivery (`r mdlbet_attitudes$full_result$delivery_cont1`).
-Although affect (`r mdlbet_attitudes$full_result$affect`) and fluency (`r mdlbet_attitudes$full_result$fluent`) were significant, they did not survive Bonferroni correction.
+Regarding the linguistic variables, the higher the ratings on comprehensibility, the more money bet (`r mdlbet_attitudes$full_result$easy`) and paralleling the effect of manner of delivery, higher ratings of fluency yielded higher bets (`r mdlbet_attitudes$full_result$fluent`).
+As to the non-linguistic variables, affect was marginally significant (`r mdlbet_attitudes$full_result$affect`).
+The model also showed an interaction between status and speaker identity (`r mdlbet_attitudes$full_result$speaker_cont1_status`): For the native speaker, higher ratings in status yielded higher money bet, while the opposite pattern was found for the non-native speaker.
 
@@
 We additionally explored participants' preferences to learn from either speaker in the future.
-206 participants reported they would prefer to learn from the native spaker, and 154 preferred the non-native speaker.
-A $\chi^2$ test of goodness of fit showed that this difference in preferences was reliable ($\chi^2$(1) = 7.51, _p_ < .01).
+There was a slight preference to learn from the native speaker, with 206 participants choosing this speaker compared to 154 who preferred the non-native speaker.
+A $\chi^2$ test of goodness of fit showed that this difference in preferences was reliable ($\chi^2$(1) = 7.51, *p* \< .01).
 
 Following previous research suggesting the role of exposure to foreign-accented speech in its role to trust and comprehensibility, we explored whether exposure to native and non-native speakers played a role in participants' betting behaviour beyond that of speaker identity and manner of delivery.
-A similar linear mixed model to that employed in our main analysis, but with the addition of exposure, showed that it did not affect participants' betting behaviour (`r mdlbet_m1_exposure$full_results$exposure`)
+A similar linear mixed model to that employed in our main analysis, but with the addition of the interaction between exposure and speaker, showed that it did not affect participants' betting behaviour (`r mdlbet_m1_exposure$full_result$speaker_cont1_exposure`) nor was it a main effect (`r mdlbet_m1_exposure$full_result$exposure`).
 
@@
 
-Listeners can attribute knowledgeability to a speaker based on a range of cues, such as voice pitch or amplitude.
 Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995].
-However, speakers can be disfluent for reasons other than lack of confidence: For example, speaking in one's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009].
-In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance [@levari2015], which consequently leads native listeners to "forgive" what otherwise would be lead to a negative evaluation [@lorenzonietal2022; @fairchildetal2020].
-In the present experiment, we explored whether attributions of lack of knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
-Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.
+However, speakers can be disfluent for reasons other than lack of confidence: For example, speaking in one's second language is also associated with an increase in disfluencies [@dejongetal2015; @derwingetal2009].
+In the present experiment, we investigated whether speaker disfluency would have behavioral consequences where measurement of their knowledgeability was implicit, and whether speaker nativeness would be taken into account when listeners made their choices.
+Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Participants placed lower bets on horses that were described disfluently, regardless of the accent of the speaker.
 
-The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced.
-Descriptions that included hesitation phenomena, in the form of filled pauses, led to smaller bets compared to their fluent counterparts.
-This aligns with @brennanwilliams1995 findings wherein listeners were less likely to attribute confidence in their knowledge to a speaker when their answers included hesitation phenomena (i.e., Feeling of Another's Knowing).
-Brennan and Williams (1995) attributed participants' ratings to inferences made about the speaker's mental state - specifically, inferences about the degree of confidence a speaker has in their knowledge.
-In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because utterances were semantically identical and acoustically identical apart from the excision of disfluencies and accent, an inference about a speaker's confidence based on those disfluencies is the most likely potential determinant of participants' decisions.
+These findings reinforce the idea that listeners are sensitive to how an utterance is produced.
+In Brennan and Williams' [-@brennanwilliams1995] study, participants explicity rated factual responses which included hesitation phenomena as less likely to be correct, or in other words, made inferences about the degree of confidence the speaker had in their knowledge.
+In the present experiment, participants were selected to have little a priori knowledge that could have guided their betting behaviour.
+Moreover, the utterances they heard were semantically identical and, within speakers, acoustically matched apart from the excision of disfluencies.
+In the absence of other factors, a reasonable conclusion is that participants' betting decisions were predicated on inferences about the confidence with which each horse was described; and these inferences were affected by the speaker's disfluencies.
 
-The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions.
+There was no evidence that participants' decisions were swayed by the fact that a non-native speaker might be expected to be disfluent for other reasons.
 This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension [e.g., @boskeretal2014; @arnoldetal2007; @helleretal2015], and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations [e.g., @fairchildetal2020; @lorenzonietal2022; @ippapafragou2022; @fairchildpapafragou2018] possibly because native listeners expect them to produce those [@levari2015].
@@
 
-Nonetheless, our results align with recent studies that have failed to find this an interaction between disfluencies and nativeness when it comes to speaker's attributions [@matzingeretal2023].
-@matzingeretal2023 accounted for their findings as a the results of the degree with which a listener needs to model the speaker: Assessing a speaker's knowledge is not as socially engaging as other communicative contexts (e.g., granting a request) and consequently, inferring an interlocutor's cognitive state is not relevant.
-Interestingly, there are several differences between their paradigm and ours that shed doubts on whether this explanation applies to our results.
-Specifically, in @matzingeretal2023 participants were overhearing a conversation, and given their task (i.e., explicitly rate their perception on speaker's knowledge or confidence), accurately ascribing the cause of disfluency did not have any consequences.
-In contrast, our participants listened to speakers talking in isolation and, most importantly, assessing speakers' knowledgeability was crucial for performing their task.
+Another recent study failed to find an interaction between disfluencies and nativeness when judging speaker knowledge, although an interaction was evident in ratings of willingness to grant a request [@matzingeretal2023].
+Matzinger et al.
+attributed their findings to the degree with which a listener needs to model the speaker: Assessing a speaker's knowledge is not as socially engaging as other communicative contexts (e.g., granting a request) and consequently, inferring an interlocutor's cognitive state is not relevant.
+However, there are several differences between their paradigm and ours that cast doubt on whether this explanation applies to our results.
+Specifically, in Matzinger et al.
+participants overheard a conversation, and were asked explicitly to rate their perceptions of each speaker's knowledge or confidence.
+In the present experiment, participants listened to speakers talking in isolation; most importantly, assessing speakers' knowledgeability was critical to task performance.
 
-One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster.
-This introduction of the speaker as an authoritative figure may have overridden any other features of their identity, including their non-native speaker identity.
+An aspect of the current experiment that might have affected the outcome is that both speakers were introduced to participants as knowledgeable tipsters.
+The fact that the speakers were purported to be authoritative figures may have been more salient than other features of their identities, including that of being a native or non-native speaker of English.
 Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty [@moletal2013].
-The preference to learn in future occasions for the native speaker may be more likely to reflect the ease of comprehending them, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
+The preference to learn in future occasions from the native speaker might reflect ease of comprehension, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of any inference concerning the non-native speaker's competence.
 
-This experiment introduced a novel approach to measuring how certain the speaker is perceived to be.
-While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new set-up to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
-However, a potential shortcoming of our design has to do with how people approached the betting system.
-Because of the nature of the task, in that we tested participants with no prior knowledge of horse races, our participants behaved rationally: The vast majority employed the hundred pounds allocated and distributed them fairly rationally in a way that maximizes their chances of winning (i.e., around £25 per horse).
-It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where individuals have more knowledge) or where they are rewarded for allocating money to the winning horse, how the speaker is perceived may yield a larger effect on participants' behaviours.
+This experiment introduced a novel approach to measuring how knowledgeable the speaker is perceived to be.
+While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study avoids explicit judgement and, instead, relies on behaviors which are highly likely to index an implicit judgement.
+However, a potential shortcoming of our design has to do with how people approached the betting system: Most participants followed a conservative approach and distributed their bets fairly evenly.
+It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where speakers are deemed to have more knowledge) or where participants are rewarded only for allocating money to the winning horse, speaker perception could yield a larger effect on participants' behaviours.
 
-Overall, our study shows that disfluency is a cue that listeners take as an index of speaker's knowledgeability.
-Importantly, in situations of uncertainty where individuals lack information to optimise their behaviour, the presence of disfluency biases their otherwise rational behaviour.
-This highlights individuals' tuning to the different ways in which a speaker's mental state is signalled in speech and how in turn it can affect their subsequent behaviours.
+Overall, our study shows that disfluency is a cue that listeners take as an index of a speaker's (lack of) knowledgeability.
+Importantly, in situations of uncertainty where individuals may lack information to optimise their behavior, the presence of disfluency biases their otherwise rational behavior.
+This highlights that individuals are attuned to the different ways in which a speaker's mental state is signalled in speech and demonstrates how non-verbal aspects of spoken messages can directly affect people's subsequent behaviours.
 

### 2024-12-12 manuscript/manuscript_eb.tex
tidy-stuff

@@
 
+% \usepackage{etoolbox}
 \makeatletter
-\usepackage{etoolbox}
-\patchcmd{\maketitle}
+\patchcmd{\HyOrg@maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\maketitle}
+\patchcmd{\HyOrg@maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 {}{\PatchFailed}
-\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 5173}
+\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 5367}
 \usepackage{lineno}
@@
 \settowidth{\cfttabnumwidth}{Table 10.\qquad}
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 \ifLuaTeX
@@
 \abstract{%
-Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking).
-The presence of disfluencies, such as filled pauses (e.g., \emph{uh} or \emph{um} in English), elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge.
-On the other hand, listeners consider alternative explanations for the speaker to be underinformative: Specifically, non-native speakers are more likely to be forgiven when they fail to be informative.
-However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear.
-In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge.
-This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous.
-Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness.
-Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.
+Whether an individual is perceived as knowledgeable by others can be biased by several potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking).
+Existing evidence for these effects tends to come from metalinguistic evaluations; here we examine the behavioral consequences of variations in the ways in which spoken messages are produced.
+Specifically,we investigate how attributions of knowledgeability are influenced by speech fluency, and by whether or not the speaker has a native accent, cues which have been previously shown to bias listeners' evaluations of speakers and what they are saying.
+We use a novel horse-race betting paradigm, in which participants have to place bets on horses which have been described in short spoken passages.
+By manipulating the fluency (fluent or disfluent) and accent (native or non-native) with which the descriptions are produced, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge (e.g., nativeness).
+Overall, our results align with a broader body of literature suggesting that the effects of hesitation phenomena are context-independent.
+Importantly, we demonstrate that individuals' meta-linguistic judgements can be measured through behavior, suggesting that these judgements have ecological importance beyond the laboratory.
 }
@@
 
-Impressions of other people arise naturally and automatically (Uleman, Adil Saribay, \& Gonzalez, 2008).
+Impressions of other people arise naturally and automatically (Uleman et al., 2008).
 Speakers can be evaluated not only by what they say but also by how they say it.
-For example, vocal features of speech can affect perceptions of confidence and persuasion (Guyer, Fabrigar, \& Vaughan-Johnston, 2019), status and solidarity (Pittam \& Gallois, 1986), or even attractiveness (Feinberg, Jones, Little, Burt, \& Perrett, 2005).
-One speech feature consistently found to bias evaluations of the speaker is speech fluency.
-Speech which includes disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995).
-Interestingly, speech produced with an accent different from one's own - particularly a \emph{foreign} accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek \& Dovidio, 2010; Gluszek, Newheiser, \& Dovidio, 2011; Lev-Ari \& Keysar, 2010; Rakić, Steffens, \& Mummendey, 2011).
-In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually.
-It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.
+For example, features of speech can affect perceptions of confidence and persuasion (Guyer et al., 2019), status and solidarity (Pittam \& Gallois, 1986), or even attractiveness (Feinberg et al., 2005).
+Similarly, speech which includes disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995).
+Interestingly, speech produced with an accent different from one's own---particularly a \emph{foreign} accent---can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek et al., 2011; Gluszek \& Dovidio, 2010; Lev-Ari \& Keysar, 2010; Rakić et al., 2011).
+Most of these studies, however, have relied on listeners' explicit judgements, which may not reflect everyday language comprehension (Armstrong et al., 1983): Do these judgements arise even when individuals are not asked to make them?.
+In this study we tested whether listeners' evaluations of a speaker affect their decision-making, and if the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually.
+In what follows, we briefly describe how speech fluency and accent have been shown to bias listeners' evaluations.
 
 There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability.
-Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener(Jiang \& Pell, 2015, 2016b, 2016a).
-Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil, Ponsot, Richardson, Reyes, \& Aucouturier, 2021).
-These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg, Bates, \& Stolcke, 1997; Shriberg \& Lickley, 1993).
+Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener (Jiang \& Pell, 2015, 2016b, 2016a).
+Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil et al., 2021).
+These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg et al., 1997; Shriberg \& Lickley, 1993).
 Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers' confidence in their knowledge.
-In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., \emph{feeling of another's knowing}, FOAK.
+In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., to rate their \emph{feeling of another's knowing}, FOAK.
 Among the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge.
 In contrast, non-answers (i.e., `I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause.
-Brennan and Williams (1995) took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question (see also Smith \& Clark, 1993).
+Brennan and Williams took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question (see also Smith \& Clark, 1993).
 
@@
 In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations.
-On the one hand, speakers with a foregin accent are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010).
-Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021).
-These negative effects triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, or a combination of both (Mai \& Hoffmann, 2013).
-
-On the other hand, there seem to be instances where being a non-native speaker is more advantageous.
-Fairchild, Mathis, and Papafragou (2020) examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness.
+On the one hand, speakers with a foreign accent are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Lev-Ari \& Keysar, 2010; Boduch-Graba \& Lev-Ari, 2021; but cf.~Souza \& Markan, 2013; Stocker, 2017; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Wetzel, Zufferey, \& Gygax, 2021; Barlow et al., 2024).
+These negative effects triggered by a speaker's non-nativeness have been primarily accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), whereby difficulties in understanding accented speech decreases processing fluency and consequently elicits negative evaluations about the source.
+
+On the other hand, there seem to be instances where being a non-native speaker is advantageous.
 Fairchild et al.
-(2020) isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identities.
-In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention.
-Native speakers who were underinformative were more likely to be rated as unwilling to share the information.
+(2020) examined whether and how failures to provide all relevant information (i.e., being under-informative) are interpreted differently as a function of speakers' nativeness.
+In four experiments, participants read stories where a speaker (native/non-native) provided a description.
+Crucially, these descriptions failed to provide all relevant information (e.g., not naming all elements on a display, failing to list all uses of an invention).
+Participants were then asked to provide an explanation for the speaker's under-informativeness.
+As descriptions were presented in the written modality, any differences in attributions of under-informativeness would be solely guided by the putative speakers' identities, rather than, for example, by processing fluency.
+Native speakers who were under-informative were more likely to be rated as unwilling to share the information than under-informative non-native speakers.
 The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp.
@@
 Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp.
-3 and 4) (for similar findings, see Fairchild \& Papafragou, 2018; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022).
+3 and 4) (for similar findings, see Fairchild \& Papafragou, 2018; Lorenzoni et al., 2022).
 Interestingly, this pattern of results holds even for auditory stimuli (Ip \& Papafragou, 2022), suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.
 
-One potential explanation is that non-native speakers are evaluated differently from native speakers due to expectations about their competence.
-Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015).
-This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted.
-Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker.
-In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018) or why non-native speech is processed more shallowly (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).
-
-Interestingly, stereotypes on linguistic competence may also affect how speech is expected to be delivered.
-For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019).
-Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it is possible that a speaker's nativeness leads to different interpretations of disfluencies.
-This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including non-native versus native speakers (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
-
-Recently, Matzinger, Pleyer, and Żywiczyński (2023) explored whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers.
-In their study, participants listened staged conversations where native and non-native speakers answered trivial questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
-Crucially, Matzinger et al.
-(2023) manipulated speakers' fluency by manipulating inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses.
-For requests, long pauses were less likely to be associated with unwillingness for non-native compared to native speakers.
+One potential explanation for Fairchild et al.'s (2020) results is that non-native speakers are evaluated differently from native speakers due to expectations about their competence.
+Non-native speakers' accents may invoke stereotypes that suggests that these speakers are less competent linguistically than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015).
+This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect the ways in which their speech is comprehended and interpreted.
+For example, in the case of under-informativeness, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors, such as ill will, when produced by a native speaker.
+In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi et al., 2022; Caffarra et al., 2018), or how syntactic errors are processed (Hanuíková et al., 2012).
+
+Given that speakers producing speech in their second language are more disfluent (Bergmann et al., 2015; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget et al., 2014), it is possible that a speaker's non-nativeness leads to different interpretations of disfluencies.
+This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold et al., 2007; Barr \& Seyfeddinipur, 2010; Heller et al., 2015), including non-native versus native speakers (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.
+
+Recently, Matzinger et al.
+(2023) investigated whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers.
+In their study, participants listened to staged conversations in which native and non-native speakers answered trivia questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request.
+Crucially, speakers' fluency was manipulated by having different inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses.
+For requests, long pauses were more likely to be associated with unwillingness for native compared to non-native speakers.
 However, FOAK ratings did not differ between speakers: Long pauses produced by either speaker were likely to be taken as reflecting low confidence and low knowledge.
-Matzinger et al.
-(2023) attribute this pattern to different conversational contexts: Requests tap into speakers' cooperativeness, and thus in this context, tuning to the interlocutor's mental state and stereotyping might be more relevant than evaluating the speaker's competence (i.e., knowledge).
+Matzinger et al.~attributed this pattern to the degree with which a speaker's mental state is relevant across conversational contexts.
 
 As is the case for Matzinger et al.
-(2023), most studies evaluating the effects of manner of speech on pereptions of the speaker have used explicit ratings.
+(2023), most studies evaluating the effects of manner of speech on perceptions of the speaker have used explicit ratings.
 Participants are asked to rate particular traits of speakers or what they say on a scale.
-Further, these ratings are elicited in non-social contexts, where participants do not have anything at stake.
-Although these experiments demonstrate that listeners show sensitivity to aspects of speech such as fluency and accent when asked to make explicit judgements about the speaker, they may not explain how listeners evaluate speech implicitly, when to do so is consequential.Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm.
+Explicit measures as those are more likely to be affected by factors such as self-presentation and less likely to reflect how individuals would behave (Greenwald et al., 2002).
+In contrast, implicit measures overcome these obstacles while still being able to predict behaviours: For example the Implicit Association Test can predict racist behaviours (McConnell \& Leibold, 2001; although see Payne \& Hannay, 2021 for whether IAT scores are better conceptualised as an aggregation rather than at the individual level).
+In the case of evaluations about the speaker, they tend to be elicited in non-social contexts: Participants are either overhearers (e.g., Matzinger et al., 2023) or simply attend to a previously recorded speaker (Brennan \& Williams, 1995; Ip \& Papafragou, 2022; e.g., Lev-Ari \& Keysar, 2010).
+Further, in these experiments, participants have nothing at stake i.e., they are evaluating the speaker, but they do not have to perform any behaviour following the utterance they just heard.
+While experiments eliciting metalinguistic judgements shed light on what factors may affect how a speaker is perceived, the lack of interaction on participant's behalf entails that these findings may not explain how listeners evaluate speech implicitly, when to do so is consequential.
+
+Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm.
 In this task, participants listen to a set of speakers provide descriptions of horses, and are asked to distribute virtual tokens as `bets' on each horse's likelihood of winning a putative race.
 This approach presents two advantages over previous experiments.
-First, in the horse-race paradigm, participants are not explicitly asked to evaluate a certain trait of the speaker (in this case, how knowledgeable they are).
+First, in the horse-race paradigm, participants are not explicitly asked to evaluate a specific trait of the speaker (in this case, how knowledgeable they are).
 Instead, we take participants' allocations of `betting money' as an indirect measurement of their perceptions of speakers' knowledge.
 Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets (Butterworth, 2019).
-Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing or its technical vocabulary).
-
-In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent.
+Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are not familiar with the world of horse racing or its technical vocabulary).
+
+In a pre-registered study, we set up to test whether and how perceptions of knowledgeability are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent.
 We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently.
-If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners' lower trust in, or lower FOAK, for the speaker.
-However, disfluent descriptions provided by a non-native speaker may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge.
+If listeners are sensitive to speaker identity when making judgements about knowledge and confidence following disfluent speech, then descriptions peppered with disfluencies provided by a native speaker should result in less money bet, reflecting listeners' lower trust in, or lower FOAK, for this speaker compared to disfluent descriptions provided by a non-native speaker.
+The non-native disfluent descriptions may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge.
 To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker.
@@
 
-All experimental stimuli can be found at \url{https://osf.io/zsut7/}.
+Our pre-registration, all experimental stimuli and scripts can be found at \url{https://osf.io/zsut7/}. Deviations from the original pre-registration (e.g., additional analysis) are marked as such.
 
@@
 
-A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (F(7) = 0.5, \emph{p} = .83).
+A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (\(F(7, 72) = 0.50\), \(p = .832\), \(\hat{\eta}^2_G = .046\), 90\% CI \([.000, .050]\)).
 An ordinal logistic regression showed that none of the horses were more likely to be ranked differently from the others (all \textbar t\textbar{} \textless{} 2).
@@
 
-Based on these results, we further edited the descriptions as some descriptions were more likely to be rated as winning horses.
-A new sample fo 30 British English speaker rated the edited passages.
-A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, \emph{p} = .52), nor in the order in which they were ranked (all \textbar t\textbar{} \textless{} 2).
+A one-way repeated measures ANOVA showed that some descriptions were more likely to be rated as winning horses (\(F(3, 116) = 10.64\), \(p < .001\), \(\hat{\eta}^2_G = .216\), 90\% CI \([.104, .311]\)).
+Therefore, we edited those passages and had a new sample of 30 British English speaker rate them.
+A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (\(F(3, 116) = 0.76\), \(p = .516\), \(\hat{\eta}^2_G = .019\), 90\% CI \([.000, .057]\)), nor in the order in which they were ranked (all \textbar t\textbar{} \textless{} 2).
 The final set of descriptions for the experiment can be found in Table \ref{tab:tab-horse-description-text}.
@@
 The impression given in both runs is that Fire Walker should handle the demands of the extra furlong and Charlie Hills is looking forward to the test.
-The trainer said ''He's done really well for a little break, his work's been good and I couldn't be more pleased with him''.\\
+The trainer said ``He's done really well for a little break, his work's been good and I couldn't be more pleased with him''.\\
 Silver Sky & Silver Sky, a runner-up of a seven-furlong maiden at Naas on his debut last month, the son of Invincible Spirit ran crack French colt Persian King to a neck in the Group 3 Autumn Stakes over today's trip at Newmarket two weeks ago and his trainer believes he has done well since.
-O'Brien said ''Silver Sky is a fine big colt and a talented one''.\\
+O'Brien said ``Silver Sky is a fine big colt and a talented one''.\\
 Apocalypse & Apocalypse has put in a string of consistent performances, most recently finishing third to Norway in the Zetland.
-''He's had a very solid year'' said trainer Archie Watson.
-''He ran a good race in the Zetland, beaten only a length and a quarter, and I think the field here is of a similar level so I'm more than happy for him to take his chance''.\\
+``He's had a very solid year'' said trainer Archie Watson.
+``He ran a good race in the Zetland, beaten only a length and a quarter, and I think the field here is of a similar level so I'm more than happy for him to take his chance''.\\
 Black Blade & Black Blade proved the market all wrong as the complexion of the 6.5-furlong novice race changed dramatically in the final two furlongs, with the Rebel Racing premier-owned newcomer under Tom Queally collaring long-time leaded Monsieur Noir.
-Spencer said: ''He did it well.
+Spencer said: ``He did it well.
 He's a nice horse.
-We always thought had a bright future''.\\
+We always thought he had a bright future''.\\
 \bottomrule
@@
 To avoid differences between the descriptions provided by the speakers, they were allowed to look at the descriptions as they spoke if they could not remember the continuation.
-We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (see Table \ref{tab:tab-horse-description-disfluent}).
+We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (recordings can be found on OSF).
 To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the `Tempo' function.
@@
 
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab-horse-description-disfluent}Transcriptions of the disfluent horse descriptions.}
-
-\begin{tabular}{m{2cm}m{13cm}}
-\toprule
-Horse & \multicolumn{1}{c}{Description}\\
-\midrule
-Fire Walker & FP-um Fire Walker is looking SP strong thanks to his (elongation) SP come-from-behind success SP FP-er in the Acomb Stakes.
-FP-um The (elongation) impression given SP in both runs FP-uh is that Fire Walker should SP handle the demands of SP the extra furlong and FP-uh Charlie Hills is looking forward to the test.
-The trainer said ''He's done (elongation) FP-um really well for a little break, FP-uh his work's been good and I couldn't be more pleased with him''.\\
-Silver Sky & Silver Sky, FP-uh a runner-up of -a seven-furlong maiden at Naas on his (elongation) debut last month.
-FP-uh The son of Invincible Spirit SP\ \ ran (elongation) crack French colt Persian King\ \  to a neck in the FP-uh\ \ Group 3 Autumn Stakes.
-over today's trip at Newmarket two weeks ago FP-uh and his trainer believes he has done well since.
-O'Brien said FP-uh ''Silver Sky is a fine big colt and a talented one''.\\
-Apocalypse & FP Apocalypse has put in a (elongation-ish) string SP of consistent performances, FP most recently finishing third to SP Norway in the Zetland.
-FP ''He's had a very solid year'' said trainer SP FP Archie Watson.
-''He ran a SP good race in the Zetland, SP FP SP beaten only a length and a quarter, and I think the field here SP is of a similar level so I'm- I'm more than happy for him to (elongation-ish) take his chance''.\\
-Black Blade & FP-um Black SP Blade proved SP FP-uh the market all wrong as the complexion SP of the 6.5 furlong SP novice SP race FP-um changed dramatically in SP the final two furlong.
-SP FP-uh with the\ \ Rebel Racing SP premier-owned SP newcomer under Tom SP Queally FP-um SP collaring long-time leaded Monsieur Noir.
-FP-uh Spencer said: ''He did it well.
-FP-uh He's a nice horse.
-FP-uh We always thought he had a bright future''.\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 To ensure that the resulting descriptions were perceived to be natural (i.e., edits to the `fluent' audios were not obvious) and that they were perceived as differing in fluency (i.e., disfluent and `fluent' versions were distinguishable), we validated them in a sample of 48 British English participants, who did not take further part in the study.
 Participants were allocated to one of the 24 experimental lists, to ensure that our validation procedure was similar to how participants encountered stimuli in the actual experiment.
-Following Bosker, Quené, Sanders, and De Jong (2014)`s procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
-We instructed participants to rate fluency by considering silent and filled pauses, speed of speech, and repairs, and to ignore speakers' accents and the content of their speech.
+Following Bosker et al.'s procedure, participants were asked to rate each audio's fluency on a scale from 1 to 9 (1: not fluent at all, 9: very fluent).
+We instructed participants to rate fluency by considering silent and filled pauses, speech rate, and repairs, and to ignore speakers' accents and the content of their speech.
 Participants additionally rated on a 9-point scale each recording's naturalness (defined as how likely it was that the audio had been recorded in one go; 1: not unlikely at all; 9: very likely), and accentedness (while ignoring the perceived speaker's proficiency in the language; 1: not accented at all, 9: very accented).
@@
 Native Speaker & Fluent & 7.62 (1.59) & 5.44 (2.62) & 4.38 (2.22)\\
- & Disfluent & 6.44 (2.36) & 5.73 (2.57) & 4 (1.97)\\
+ & Disfluent & 6.44 (2.36) & 5.73 (2.57) & 4.00 (1.97)\\
 Non-native Speaker & Fluent & 6.25 (1.73) & 5.94 (1.83) & 7.02 (1.59)\\
@@
 An identical model for naturalness ratings showed no significant differences by fluency (\(\hat{\beta} = 0.29\), 95\% CI \([-0.52, 1.11]\), \(t = 0.70\)), speaker's linguistic background (\(\hat{\beta} = 0.50\), 95\% CI \([-0.27, 1.27]\), \(t = 1.27\)) or their interaction (\(\hat{\beta} = -0.40\), 95\% CI \([-1.49, 0.70]\), \(t = -0.71\)).
+Finally, an identical model for accentedness only showed a significant difference for speaker's linguistic background (\(\hat{\beta} = 2.65\), 95\% CI \([2.04, 3.26]\), \(t = 8.49\)).
 
@@
 
-Stimuli were presented using JsPsych (Leeuw, Gilbert, \& Luchterhandt, 2023), hosted on MindProbe (via JATOS, Lange, Kühn, \& Filevich, 2015).
+Stimuli were presented using JsPsych (Leeuw et al., 2023), hosted on MindProbe (via JATOS, Lange et al., 2015).
 The task began with a cover story introducing two horse racing tipsters.
@@
 All data pre-processing and analyses were carried out in R version 4.4.1 (R Core Team, 2024), using the packages \emph{tidyverse} version 2.0.0 (Wickham et al., 2019), \emph{ggplot} version 3.5.1 (Wickham, 2016), and \emph{wesanderson} version 0.3.7 for data wrangling and visualization.
-\emph{lme4} version 1.1-35.5 (Bates, Mächler, Bolker, \& Walker, 2015) was used for data analysis, and \emph{papaja} version 0.1.2 (Aust \& Barth, 2023) for manuscript write-up.
-Scripts can be found at \url{https://osf.io/zsut7/}
+\emph{lme4} version 1.1-35.5 (Bates et al., 2015) was used for data analysis, and \emph{papaja} version 0.1.2 (Aust \& Barth, 2023) for manuscript write-up.
+Scripts can be found at \url{https://osf.io/zsut7/}.
 
@@
 Table \ref{tab:tab-dist-money} shows the mean amount of money bet per speaker and fluency condition.
-On average, participants bet £25 on when information was provided fluently.
-This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally.
-However, disfluent instructions seem to lower the amount of money bet.
+On average, participants bet £24 on when information was provided fluently while disfluent instructions seem to lower the amount of money bet.
 
@@
 
-We modelled participants' betting behaviour in a linear mixed model.
+We modelled participants' betting behaviour using a linear mixed model.
 We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded.
 The model included fixed effects of fluency (sum-coded; fluent coded as -0.5, disfluent as +0.5), speaker's linguistic background (sum-coded, native coded as -0.5; non-native coded as +0.5), and their interaction.
-The maximal model (Barr, Levy, Scheepers, \& Tily, 2013), with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge.
+The maximal model (Barr et al., 2013), with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge.
 We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept.
-The final model included a random intercept by-item.
-
-Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t(1433) = -3.99\), \(p < .001\)).
-There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t(1433) = 1.15\), \(p = .251\)) and importantly, no interaction between manner of delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t(1433) = 1.28\), \(p = .200\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.92\), 95\% CI \([-3.91, -1.92]\), \(t(2557.08) = -5.75\), \(p < .001\)), and a main effect for speaker (\(\hat{\beta} = 1.21\), 95\% CI \([0.21, 2.20]\), \(t(2557.09) = 2.38\), \(p = .017\)), but no significant interaction (\(\hat{\beta} = 0.93\), 95\% CI \([-1.06, 2.92]\), \(t(2557.12) = 0.92\), \(p = .358\))}.
+The final model only included a random intercept by-item.
+
+Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t(1,433) = -3.99\), \(p < .001\)).
+There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t(1,433) = 1.15\), \(p = .251\)) and no interaction between manner of delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t(1,433) = 1.28\), \(p = .200\))\footnote{An identical model including the 281 excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.92\), 95\% CI \([-3.91, -1.92]\), \(t(2,557.08) = -5.75\), \(p < .001\)), and a main effect for speaker (\(\hat{\beta} = 1.21\), 95\% CI \([0.21, 2.20]\), \(t(2,557.09) = 2.38\), \(p = .017\)), but no significant interaction (\(\hat{\beta} = 0.93\), 95\% CI \([-1.06, 2.92]\), \(t(2,557.12) = 0.92\), \(p = .358\))}.
 
@@
 
-Table \ref{tab:tab5} depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
+Table \ref{tab:tab7} depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.
 Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score.
@@
 
-\caption{\label{tab:tab5}Average score (and standard deviation) in each dimension by speaker.}
-
-\begin{tabular}{lll}
+\caption{\label{tab:tab7}Average score (and standard deviation) in each dimension by speaker, and paired t-test for each dimension between speakers. }
+
+\begin{tabular}{llllll}
 \toprule
-Dimension & \multicolumn{1}{c}{Native Speaker} & \multicolumn{1}{c}{Non-native Speaker}\\
+Dimension & \multicolumn{1}{c}{Native Speaker} & \multicolumn{1}{c}{Non-native Speaker} & \multicolumn{1}{c}{p-value} & \multicolumn{1}{c}{d} & \multicolumn{1}{c}{t(359.00)}\\
 \midrule
-Comprehensibility & 7.62 (1.57) & 5.51 (2.14)\\
-Accentedness & 5.46 (2.1) & 6.84 (1.37)\\
-Fluency & 7.97 (1.43) & 6.11 (1.83)\\
-Affect & 5.77 (1.49) & 6.05 (1.32)\\
-Status & 5.95 (1.52) & 6.43 (1.31)\\
-Solidarity & 5.67 (1.48) & 6.41 (1.24)\\
-Trustworthy & 6 (1.61) & 6.36 (1.41)\\
+Comprehensibility & 7.62 (1.57) & 5.51 (2.14) & <.001 & 2.11 & 15.99\\
+Accentedness & 5.46 (2.1) & 6.84 (1.37) & <.001 & -1.39 & -11.51\\
+Fluency & 7.97 (1.43) & 6.11 (1.83) & <.001 & 1.87 & 17.15\\
+Affect & 5.77 (1.49) & 6.05 (1.32) & = 0.003 & -0.29 & -3.54\\
+Status & 5.95 (1.52) & 6.43 (1.31) & <.001 & -0.48 & -6.55\\
+Solidarity & 5.67 (1.48) & 6.41 (1.24) & <.001 & -0.74 & -9.63\\
+Trustworthiness & 6.00 (1.61) & 6.36 (1.41) & <.001 & -0.36 & -4.12\\
 \bottomrule
@@
 
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab6}Paired t test for each dimension between speakers.}
-
-\begin{tabular}{llll}
-\toprule
-Dimension & \multicolumn{1}{c}{t(359)} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{d}\\
-\midrule
-Comprehensibility & 15.99 & {}[1.85, 2.36] & 2.11\\
-Accent & -11.51 & {}[-1.62, -1.15] & -1.39\\
-Fluency & 17.15 & {}[1.65, 2.08] & 1.87\\
-Affect & -3.54 & {}[-0.44, -0.13] & -0.29\\
-Status & -6.55 & {}[-0.62, -0.33] & -0.48\\
-Solidarity & -9.63 & {}[-0.89, -0.59] & -0.74\\
-Trustworthy & -4.12 & {}[-0.53, -0.19] & -0.36\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Analyses showed that speakers were rated differently across all six dimensions (see Table \ref{tab:tab6}).
-The largest differences were, unsurprisingly, in comprehensibility and accentedness, where the non-native speaker received lower ratings.
-
-Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours.
-This second model improved model fit (\(\chi^2\)(7) = 24.77, \emph{p} \textless{} .01).
-The model showed a main effect of manner of delivery (\(\hat{\beta} = -2.71\), 95\% CI \([-4.03, -1.39]\), \(t(1436.00) = -4.03\), \(p < .001\)).
-Although affect (\(\hat{\beta} = 0.83\), 95\% CI \([0.15, 1.50]\), \(t(1436.09) = 2.41\), \(p = .016\)) and fluency (\(\hat{\beta} = -0.67\), 95\% CI \([-1.24, -0.10]\), \(t(1436.10) = -2.31\), \(p = .021\)) were significant, they did not survive Bonferroni correction.
+Analyses showed that speakers were rated differently across all seven dimensions (see Table \ref{tab:tab7}).
+The largest differences were, unsurprisingly, in the linguistic variables for comprehensibility, fluency and accentedness.
+The native speaker was rated as more comprehensible, more fluent and less accented.
+Following our pre-registered analysis, we included these seven variables and their interaction with speaker identity to our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours.
+This second model improved model fit (\(\chi^2\)(14) = 33.67, \emph{p} \textless{} .01).
+The model showed a main effect of manner of delivery (\(\hat{\beta} = -2.71\), 95\% CI \([-4.03, -1.40]\), \(t(1,436.00) = -4.04\), \(p < .001\)).
+Regarding the linguistic variables, the higher the ratings on comprehensibility, the more money bet (\(\hat{\beta} = 0.57\), 95\% CI \([0.03, 1.11]\), \(t(1,436.43) = 2.08\), \(p = .038\)) and paralleling the effect of manner of delivery, higher ratings of fluency yielded higher bets (\(\hat{\beta} = -0.61\), 95\% CI \([-1.19, -0.02]\), \(t(1,436.08) = -2.04\), \(p = .041\)).
+As to the non-linguistic variables, affect was marginally significant (\(\hat{\beta} = 0.67\), 95\% CI \([-0.01, 1.36]\), \(t(1,436.06) = 1.92\), \(p = .055\)).
+The model also showed an interaction between status and speaker identity (\(\hat{\beta} = -1.91\), 95\% CI \([-3.57, -0.24]\), \(t(1,436.04) = -2.25\), \(p = .025\)): For the native speaker, higher ratings in status yielded higher money bet, while the opposite pattern was found for the non-native speaker.
 
@@
 We additionally explored participants' preferences to learn from either speaker in the future.
-206 participants reported they would prefer to learn from the native spaker, and 154 preferred the non-native speaker.
+There was a slight preference to learn from the native speaker, with 206 participants choosing this speaker compared to 154 who preferred the non-native speaker.
 A \(\chi^2\) test of goodness of fit showed that this difference in preferences was reliable (\(\chi^2\)(1) = 7.51, \emph{p} \textless{} .01).
@@
 Following previous research suggesting the role of exposure to foreign-accented speech in its role to trust and comprehensibility, we explored whether exposure to native and non-native speakers played a role in participants' betting behaviour beyond that of speaker identity and manner of delivery.
-A similar linear mixed model to that employed in our main analysis, but with the addition of exposure, showed that it did not affect participants' betting behaviour ()
+A similar linear mixed model to that employed in our main analysis, but with the addition of the interaction between exposure and speaker, showed that it did not affect participants' betting behaviour (\(\hat{\beta} = -0.35\), 95\% CI \([-1.35, 0.66]\), \(t(1,431.10) = -0.68\), \(p = .499\)) nor was it a main effect (\(\hat{\beta} = 0.42\), 95\% CI \([-0.08, 0.92]\), \(t(1,431.25) = 1.63\), \(p = .103\)).
 
@@
 
-Listeners can attribute knowledgeability to a speaker based on a range of cues, such as voice pitch or amplitude.
 Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995).
-However, speakers can be disfluent for reasons other than lack of confidence: For example, speaking in one's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009).
-In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance (Lev-Ari, 2015), which consequently leads native listeners to ``forgive'' what otherwise would be lead to a negative evaluation (Fairchild et al., 2020; Lorenzoni et al., 2022).
-In the present experiment, we explored whether attributions of lack of knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse.
-Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.
-
-The pattern found aligns with the idea that listeners are sensitive to how an utterance is produced.
-Descriptions that included hesitation phenomena, in the form of filled pauses, led to smaller bets compared to their fluent counterparts.
-This aligns with Brennan and Williams (1995) findings wherein listeners were less likely to attribute confidence in their knowledge to a speaker when their answers included hesitation phenomena (i.e., Feeling of Another's Knowing).
-Brennan and Williams (1995) attributed participants' ratings to inferences made about the speaker's mental state - specifically, inferences about the degree of confidence a speaker has in their knowledge.
-In our experiment, since participants have little a priori knowledge that can guide their betting behaviour, and because utterances were semantically identical and acoustically identical apart from the excision of disfluencies and accent, an inference about a speaker's confidence based on those disfluencies is the most likely potential determinant of participants' decisions.
-
-The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions.
+However, speakers can be disfluent for reasons other than lack of confidence: For example, speaking in one's second language is also associated with an increase in disfluencies (De Jong et al., 2015; Derwing et al., 2009).
+In the present experiment, we investigated whether speaker disfluency would have behavioral consequences where measurement of their knowledgeability was implicit, and whether speaker nativeness would be taken into account when listeners made their choices.
+Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Participants placed lower bets on horses that were described disfluently, regardless of the accent of the speaker.
+
+These findings reinforce the idea that listeners are sensitive to how an utterance is produced.
+In Brennan and Williams' (1995) study, participants explicity rated factual responses which included hesitation phenomena as less likely to be correct, or in other words, made inferences about the degree of confidence the speaker had in their knowledge.
+In the present experiment, participants were selected to have little a priori knowledge that could have guided their betting behaviour.
+Moreover, the utterances they heard were semantically identical and, within speakers, acoustically matched apart from the excision of disfluencies.
+In the absence of other factors, a reasonable conclusion is that participants' betting decisions were predicated on inferences about the confidence with which each horse was described; and these inferences were affected by the speaker's disfluencies.
+
+There was no evidence that participants' decisions were swayed by the fact that a non-native speaker might be expected to be disfluent for other reasons.
 This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension (Arnold et al., 2007; e.g., Bosker, Quené, Sanders, \& De Jong, 2014; Heller et al., 2015), and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations (e.g., Fairchild et al., 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni et al., 2022) possibly because native listeners expect them to produce those (Lev-Ari, 2015).
@@
 
-Nonetheless, our results align with recent studies that have failed to find this an interaction between disfluencies and nativeness when it comes to speaker's attributions (Matzinger et al., 2023).
-Matzinger et al.
-(2023) accounted for their findings as a the results of the degree with which a listener needs to model the speaker: Assessing a speaker's knowledge is not as socially engaging as other communicative contexts (e.g., granting a request) and consequently, inferring an interlocutor's cognitive state is not relevant.
-Interestingly, there are several differences between their paradigm and ours that shed doubts on whether this explanation applies to our results.
-Specifically, in Matzinger et al.
-(2023) participants were overhearing a conversation, and given their task (i.e., explicitly rate their perception on speaker's knowledge or confidence), accurately ascribing the cause of disfluency did not have any consequences.
-In contrast, our participants listened to speakers talking in isolation and, most importantly, assessing speakers' knowledgeability was crucial for performing their task.
-
-One possibility for this lack of interaction has to do with the fact that our non-native speaker was introduced as a knowledgeable tipster.
-This introduction of the speaker as an authoritative figure may have overridden any other features of their identity, including their non-native speaker identity.
-Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty (Mol, Kuhlen, Van der Steen, \& Obbens, 2013).
-The preference to learn in future occasions for the native speaker may be more likely to reflect the ease of comprehending them, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of competence for non-native speakers.
-
-This experiment introduced a novel approach to measuring how certain the speaker is perceived to be.
-While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study offers a new set-up to explore how different factors bias individuals' evaluations indirectly, as well as the implications of those evaluations.
-However, a potential shortcoming of our design has to do with how people approached the betting system.
-Because of the nature of the task, in that we tested participants with no prior knowledge of horse races, our participants behaved rationally: The vast majority employed the hundred pounds allocated and distributed them fairly rationally in a way that maximizes their chances of winning (i.e., around £25 per horse).
-It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where individuals have more knowledge) or where they are rewarded for allocating money to the winning horse, how the speaker is perceived may yield a larger effect on participants' behaviours.
-
-Overall, our study shows that disfluency is a cue that listeners take as an index of speaker's knowledgeability.
-Importantly, in situations of uncertainty where individuals lack information to optimise their behaviour, the presence of disfluency biases their otherwise rational behaviour.
-This highlights individuals' tuning to the different ways in which a speaker's mental state is signalled in speech and how in turn it can affect their subsequent behaviours.
+Another recent study failed to find an interaction between disfluencies and nativeness when judging speaker knowledge, although an interaction was evident in ratings of willingness to grant a request (Matzinger et al., 2023).
+Matzinger et al.~attributed their findings to the degree with which a listener needs to model the speaker: Assessing a speaker's knowledge is not as socially engaging as other communicative contexts (e.g., granting a request) and consequently, inferring an interlocutor's cognitive state is not relevant.
+However, there are several differences between their paradigm and ours that cast doubt on whether this explanation applies to our results.
+Specifically, in Matzinger et al.~participants overheard a conversation, and were asked explicitly to rate their perceptions of each speaker's knowledge or confidence.
+In the present experiment, participants listened to speakers talking in isolation; most importantly, assessing speakers' knowledgeability was critical to task performance.
+
+An aspect of the current experiment that might have affected the outcome is that both speakers were introduced to participants as knowledgeable tipsters.
+The fact that the speakers were purported to be authoritative figures may have been more salient than other features of their identities, including that of being a native or non-native speaker of English.
+Indeed, beliefs about a speaker's expertise have been shown to guide perceptions of their certainty (Mol et al., 2013).
+The preference to learn in future occasions from the native speaker might reflect ease of comprehension, rather than an implicit negative bias towards the non-native speaker, and particularly, a diminished perception of any inference concerning the non-native speaker's competence.
+
+This experiment introduced a novel approach to measuring how knowledgeable the speaker is perceived to be.
+While previous studies had participants explicitly rate a speaker on different dimensions (e.g., knowledgeability, trust) in non-social contexts, the present study avoids explicit judgement and, instead, relies on behaviors which are highly likely to index an implicit judgement.
+However, a potential shortcoming of our design has to do with how people approached the betting system: Most participants followed a conservative approach and distributed their bets fairly evenly.
+It is, therefore, possible that in situations of less uncertainty (e.g., a scenario where speakers are deemed to have more knowledge) or where participants are rewarded only for allocating money to the winning horse, speaker perception could yield a larger effect on participants' behaviours.
+
+Overall, our study shows that disfluency is a cue that listeners take as an index of a speaker's (lack of) knowledgeability.
+Importantly, in situations of uncertainty where individuals may lack information to optimise their behavior, the presence of disfluency biases their otherwise rational behavior.
+This highlights that individuals are attuned to the different ways in which a speaker's mental state is signalled in speech and demonstrates how non-verbal aspects of spoken messages can directly affect people's subsequent behaviours.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-armstrongetal1983}{}}%
+Armstrong, S. L., Gleitman, L. R., \& Gleitman, H. (1983). What some concepts might not be. \emph{Cognition}, \emph{13}(3), 263--308.
+
 \leavevmode\vadjust pre{\hypertarget{ref-arnoldetal2007}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2023). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2023). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}
 
 \leavevmode\vadjust pre{\hypertarget{ref-barlowetal2024}{}}%
-Barlow, S., Beardsley, G., Bsharah, Z., Crofts, R., De La Rosa, C., Gutierrez, A., et al.others.
+Barlow, S., Beardsley, G., Bsharah, Z., Crofts, R., De La Rosa, C., Gutierrez, A., Highfill, C., Johnson, A.
+G.
+W., Johnson, C., Johnson, J., \& al., et.
 (2024).
-The effects of exposure and explicit stereotypes on veracity judgments of polish-accented english speech: A preregistered close replication and extension of boduch-grabka \& lev-ari (2021).
+The effects of exposure and explicit stereotypes on veracity judgments of {P}olish-accented {E}nglish speech: A preregistered close replication and extension of {B}oduch-{G}rabka \& {L}ev-{A}ri (2021).
 \emph{Studies in Second Language Acquisition}, 1--17.
+\url{https://doi.org/10.1017/S0272263124000123}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barrseyfeddinipur2010}{}}%
-Barr, D. J., \& Seyfeddinipur, M. (2010). The role of fillers in listener attributions for speaker disfluency. \emph{Language and Cognitive Processes}, \emph{25}(4), 441--455.
+Barr, D.
+J., \& Seyfeddinipur, M.
+(2010).
+The role of fillers in listener attributions for speaker disfluency.
+\emph{Language and Cognitive Processes}, \emph{25}(4), 441--455.
+\url{https://doi.org/10.1080/01690960903047122}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bazzietal2022}{}}%
-Bazzi, L., Brouwer, S., \& Foucart, A. (2022). The impact of foreign accent on irony and its consequences on social interaction. \emph{Journal of Multilingual and Multicultural Development}, 1--13.
+Bazzi, L., Brouwer, S., \& Foucart, A.
+(2022).
+The impact of foreign accent on irony and its consequences on social interaction.
+\emph{Journal of Multilingual and Multicultural Development}, 1--13.
+\url{https://doi.org/10.1080/01434632.2022.2126487}
 
 \leavevmode\vadjust pre{\hypertarget{ref-bergmannetal2015}{}}%
-Bergmann, C., Sprenger, S. A., \& Schmid, M. S. (2015). The impact of language co-activation on {L1} and {L2} speech fluency. \emph{Acta {Psychologica}}, \emph{161}, 25--35.
+Bergmann, C., Sprenger, S.
+A., \& Schmid, M.
+S.
+(2015).
+The impact of language co-activation on {L1} and {L2} speech fluency.
+\emph{Acta {Psychologica}}, \emph{161}, 25--35.
+\url{https://doi.org/10.1016/j.actpsy.2015.07.015}
 
@@
 (2021).
-Exposing individuals to foreign accent increases their trust in what nonnative speakers say.
+Exposing {I}ndividuals to {F}oreign {A}ccent {I}ncreases their {T}rust in {W}hat {N}onnative {S}peakers {S}ay.
 \emph{Cognitive Science}, \emph{45}(11), e13064.
@@
 (2014).
-Native 'um's elicit prediction of low-frequency referents, but non-native 'um's do not.
+Native `um's elicit prediction of low-frequency referents, but non-native `um's do not.
 \emph{Journal of Memory and Language}, \emph{75}, 104--116.
@@
 (1995).
-The feeling of another's knowing: Prosody and filled pauses as cues to listeners about the metacognitive states of speakers.
+The {F}eeling of {A}nother's {K}nowing: {P}rosody and {F}illed {P}auses as {C}ues to {L}isteners about the {M}etacognitive {S}tates of {S}peakers.
 \emph{Journal of Memory and Language}, \emph{34}(3), 383--398.
+\url{https://doi.org/10.1177/0261927X10387100}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-caballeropell2020}{}}%
-Caballero, J.
-A., \& Pell, M.
-D.
-(2020).
-Implicit effects of speaker accents and vocally-expressed confidence on decisions to trust.
-\emph{Decision}, \emph{7}(4), 314.
-\url{https://doi.org/10.1037/dec0000140}
-
 \leavevmode\vadjust pre{\hypertarget{ref-caffarraetal2018}{}}%
-Caffarra, S., Michell, E., \& Martin, C. D. (2018). The impact of foreign accent on irony interpretation. \emph{{PLoS} One}, \emph{13}(8), e0200939.
+Caffarra, S., Michell, E., \& Martin, C. D. (2018). The impact of foreign accent on irony interpretation. \emph{{PLoS} One}, \emph{13}(8), e0200939. \url{https://doi.org/10.1371/journal.pone.0200939}
 
 \leavevmode\vadjust pre{\hypertarget{ref-christenfeld1995}{}}%
-Christenfeld, N. (1995). Does it hurt to say um? \emph{Journal of Nonverbal Behavior}, \emph{19}, 171--186.
-
-\leavevmode\vadjust pre{\hypertarget{ref-davies2003}{}}%
-Davies, A. (2003). \emph{The native speaker: Myth and reality} (Vol. 38). Multilingual matters. \url{https://doi.org/10.21832/9781853596247}
+Christenfeld, N. (1995). Does it hurt to say um? \emph{Journal of Nonverbal Behavior}, \emph{19}, 171--186. \url{https://doi.org/10.1007/BF02175503}
 
@@
 (2015).
-Second language fluency: Speaking style or proficiency?
-Correcting measures of second language fluency for first language behavior.
+Second language fluency: {S}peaking style or proficiency{?} {C}orrecting measures of second language fluency for first language behavior.
 \emph{Applied Psycholinguistics}, \emph{36}(2), 223--243.
+\url{https://doi.org/10.1017/S0142716413000210}
 
@@
 \emph{Studies in Second Language Acquisition}, \emph{31}(4), 533--557.
+\url{https://doi.org/10.1017/S0272263109990015}
 
@@
 (2016).
-I don't like you because you're hard to understand: The role of processing fluency in the language attitudes process.
+I {D}on't like {Y}ou because {Y}ou're {H}ard to {U}nderstand: {T}he {R}ole of {P}rocessing {F}luency in the {L}anguage {A}ttitudes {P}rocess.
 \emph{Human Communication Research}, \emph{42}(3), 396--420.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fairchildetal2020}{}}%
-Fairchild, S., Mathis, A., \& Papafragou, A. (2020). Pragmatics and social meaning: Understanding under-informativeness in native and non-native speakers. \emph{Cognition}, \emph{200}, 104171.
+Fairchild, S., Mathis, A., \& Papafragou, A.
+(2020).
+Pragmatics and social meaning: Understanding under-informativeness in native and non-native speakers.
+\emph{Cognition}, \emph{200}, 104171.
+\url{https://doi.org/10.1016/j.cognition.2019.104171}
 
 \leavevmode\vadjust pre{\hypertarget{ref-fairchildpapafragou2018}{}}%
-Fairchild, S., \& Papafragou, A. (2018). Sins of omission are more likely to be forgiven in non-native speakers. \emph{Cognition}, \emph{181}, 80--92.
+Fairchild, S., \& Papafragou, A.
+(2018).
+Sins of omission are more likely to be forgiven in non-native speakers.
+\emph{Cognition}, \emph{181}, 80--92.
+\url{https://doi.org/10.1016/j.cognition.2018.08.010}
 
@@
 \emph{Animal Behaviour}, \emph{69}(3), 561--568.
+\url{https://doi.org/10.1016/j.anbehav.2004.06.012}
 
@@
 \emph{Neuropsychologia}, \emph{158}, 107902.
+\url{https://doi.org/10.1016/j.neuropsychologia.2021.107902}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gkalitsiouwerle2023}{}}%
-Gkalitsiou, Z., \& Werle, D. (2023). Speech disfluencies in bilingual greek-english young adults. \emph{Journal of Fluency Disorders}, \emph{78}, 106001.
+Gkalitsiou, Z., \& Werle, D.
+(2023).
+Speech disfluencies in bilingual {G}reek-{E}nglish young adults.
+\emph{Journal of Fluency Disorders}, \emph{78}, 106001.
+\url{https://doi.org/10.1016/j.jfludis.2023.106001}
 
@@
 (2010).
-The way they speak: A social psychological perspective on the stigma of nonnative accents in communication.
+The {W}ay {T}hey {S}peak: {A} {S}ocial {P}sychological {P}erspective on the {S}tigma of {N}onnative {A}ccents in {C}ommunication.
 \emph{Personality and Social Psychology Review}, \emph{14}(2), 214--237.
+\url{https://doi.org/10.1177/108886830935928}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gluszeketal2011}{}}%
-Gluszek, A., Newheiser, A.-K., \& Dovidio, J. F. (2011). Social psychological orientations and accent strength. \emph{Journal of Language and Social Psychology}, \emph{30}(1), 28--45.
+Gluszek, A., Newheiser, A.-K., \& Dovidio, J.
+F.
+(2011).
+Social {P}sychological {O}rientations and {A}ccent {S}trength.
+\emph{Journal of Language and Social Psychology}, \emph{30}(1), 28--45.
+\url{https://doi.org/10.1177/0261927X10387100}
 
@@
 \emph{Nature Communications}, \emph{12}(1), 861.
+\url{https://doi.org/10.1038/s41467-020-20649-4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-greenwaldetal2002}{}}%
+Greenwald, A.
+G., Banaji, M.
+R., Rudman, L.
+A., Farnham, S.
+D., Nosek, B.
+A., \& Mellott, D.
+S.
+(2002).
+A unified theory of implicit attitudes, stereotypes, self-esteem, and self-concept.
+\emph{Psychological Review}, \emph{109}(1), 3.
+\url{https://doi.org/10.1037/0033-295X.109.1.3}
 
@@
 \emph{Phonetica}, \emph{31}(3-4), 144--184.
+\url{https://doi.org/10.1159/000259667}
 
@@
 (2019).
-Speech rate, intonation, and pitch: Investigating the bias and cue effects of vocal confidence on persuasion.
+Speech {R}ate, {I}ntonation, and {P}itch: {I}nvestigating the {B}ias and {C}ue {E}ffects of {V}ocal {C}onfidence on {P}ersuasion.
 \emph{Personality and Social Psychology Bulletin}, \emph{45}(3), 389--405.
+\url{https://doi.org/10.1177/0146167218787805}
 
@@
 (2012).
-When one person{\textquotesingle}s mistake is another{\textquotesingle}s standard usage: The effect of foreign accent on syntactic processing.
+When {O}ne {P}erson's {M}istake {I}s {A}nother's {S}tandard {U}sage: {T}he {E}ffect of {F}oreign {A}ccent on {S}yntactic {P}rocessing.
 \emph{Journal of Cognitive Neuroscience}, \emph{24}(4), 878--887.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-helleretal2015}{}}%
-Heller, D., Arnold, J. E., Klein, N., \& Tanenhaus, M. K. (2015). Inferring difficulty: Flexibility in the real-time processing of disfluency. \emph{Language and Speech}, \emph{58}(2), 190--203.
+Heller, D., Arnold, J.
+E., Klein, N., \& Tanenhaus, M.
+K.
+(2015).
+Inferring {D}ifficulty: {F}lexibility in the {R}eal-time {P}rocessing of {D}isfluency.
+\emph{Language and Speech}, \emph{58}(2), 190--203.
+\url{https://doi.org/10.1177/0023830914528107}
 
@@
 (2022).
-Integrating non-native speaker identity in semantic and pragmatic processing.
+Integrating {N}on-{N}ative {S}peaker {I}dentity in {S}emantic and {P}ragmatic {P}rocessing.
 \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{44}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jiangetal2019}{}}%
-Jiang, X., Gossack-Keenan, K., \& Pell, M.
+\url{https://doi.org/escholarship.org/uc/item/1qk4z377}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2015}{}}%
+Jiang, X., \& Pell, M. D. (2015). On how the brain decodes vocal cues about speaker confidence. \emph{Cortex}, \emph{66}, 9--34. \url{https://doi.org/10.1016/j.cortex.2015.02.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2016b}{}}%
+Jiang, X., \& Pell, M.
 D.
-(2019).
-To believe or not to believe?
-{How voice and accent information in speech alter listener impressions of trust}.
-\emph{Quarterly Journal of Experimental Psychology}, \emph{73}(1), 55--79.
-\url{https://doi.org/10.1177/1747021819865833}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2015}{}}%
-Jiang, X., \& Pell, M. D. (2015). On how the brain decodes vocal cues about speaker confidence. \emph{Cortex}, \emph{66}, 9--34.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jiangpell2016b}{}}%
-Jiang, X., \& Pell, M. D. (2016a). Neural responses towards a speaker's feeling of (un) knowing. \emph{Neuropsychologia}, \emph{81}, 79--93.
+(2016a).
+Neural responses towards a speaker's feeling of (un) knowing.
+\emph{Neuropsychologia}, \emph{81}, 79--93.
+\url{https://doi.org/10.1016/j.neuropsychologia.2015.12.008}
 
@@
 \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{42}(9), 1412.
+\url{https://doi.org/10.1037/xhp0000240}
 
 \leavevmode\vadjust pre{\hypertarget{ref-jiangpell2017}{}}%
-Jiang, X., \& Pell, M. D. (2017). The sound of confidence and doubt. \emph{Speech Communication}, \emph{88}, 106--126.
+Jiang, X., \& Pell, M. D. (2017). The sound of confidence and doubt. \emph{Speech Communication}, \emph{88}, 106--126. \url{https://doi.org/10.1016/j.specom.2017.01.011}
 
@@
 (2015).
-" just another tool for online studies''(JATOS): An easy solution for setup and management of web servers supporting online studies.
+"{J}ust another tool for online studies'' (JATOS): An easy solution for setup and management of web servers supporting online studies.
 \emph{PloS One}, \emph{10}(6), e0130834.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-levari2015}{}}%
-Lev-Ari, S. (2015). Comprehending non-native speakers: Theory and evidence for adjustment in manner of processing. \emph{Frontiers in Psychology}, \emph{5}, 1546.
+Lev-Ari, S.
+(2015).
+Comprehending non-native speakers: Theory and evidence for adjustment in manner of processing.
+\emph{Frontiers in Psychology}, \emph{5}, 1546.
+\url{https://doi.org/10.3389/fpsyg.2014.01546}
 
@@
 (2010).
-Why don{\textquotesingle}t we believe non-native speakers?
+Why don't we believe non-native speakers?
 {The influence of accent on credibility}.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-levarikeysar2012}{}}%
-Lev-Ari, S., \& Keysar, B. (2012). Less-detailed representation of non-native language: Why non-native speakers' stories seem more vague. \emph{Discourse Processes}, \emph{49}(7), 523--538.
-
 \leavevmode\vadjust pre{\hypertarget{ref-lorenzonietal2022}{}}%
-Lorenzoni, A., Pagliarini, E., Vespignani, F., \& Navarrete, E. (2022). Pragmatic and knowledge range lenience towards foreigners. \emph{Acta Psychologica}, \emph{226}, 103572.
-
-\leavevmode\vadjust pre{\hypertarget{ref-maihoffmann2014}{}}%
-Mai, R., \& Hoffmann, S.
-(2013).
-Accents in business communication: An integrative model and propositions for future research.
-\emph{Journal of Consumer Psychology}, \emph{24}(1), 137--158.
-\url{https://doi.org/10.1016/j.jcps.2013.09.004}
+Lorenzoni, A., Pagliarini, E., Vespignani, F., \& Navarrete, E.
+(2022).
+Pragmatic and knowledge range lenience towards foreigners.
+\emph{Acta Psychologica}, \emph{226}, 103572.
+\url{https://doi.org/10.1016/j.actpsy.2022.103572}
 
@@
 (2023).
-Pause length and differences in cognitive state attribution in native and non-native speakers.
+Pause {L}ength and {D}ifferences in {C}ognitive {S}tate {A}ttribution in {N}ative and {N}on-{N}ative {S}peakers.
 \emph{Languages}, \emph{8}(1), 26.
 \url{https://doi.org/10.3390/languages8010026}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcconellleibold2001}{}}%
+McConnell, A.
+R., \& Leibold, J.
+M.
+(2001).
+{R}elations among the {I}mplicit {A}ssociation {T}est, {D}iscriminatory {B}ehavior, and {E}xplicit {M}easures of {R}acial {A}ttitudes.
+\emph{Journal of Experimental Social Psychology}, \emph{37}(5), 435--442.
+\url{https://doi.org/10.1006/jesp.2000.1470}
 
@@
 \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{35}.
+\url{https://doi.org/escholarship.org/uc/item/8w03w4ch}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nortonhogan1980}{}}%
-Norton-Ford, J. D., \& Hogan, D. R. (1980). Role of nonverbal behaviors in social judgments of peers' assertiveness. \emph{Psychological Reports}, \emph{46}(3\_suppl), 1085--1086.
+Norton-Ford, J.
+D., \& Hogan, D.
+R.
+(1980).
+Role of {N}onverbal {B}ehaviors in {S}ocial {J}udgments of {P}eers' {A}ssertiveness.
+\emph{Psychological Reports}, \emph{46}(3\_suppl), 1085--1086.
+\url{https://doi.org/10.2466/pr0.1980.46.3c.1085}
+
+\leavevmode\vadjust pre{\hypertarget{ref-paynehannay2021}{}}%
+Payne, B. K., \& Hannay, J. W. (2021). Implicit bias reflects systemic racism. \emph{Trends in Cognitive Sciences}, \emph{25}(11), 927--936. \url{https://doi.org/10.1016/j.tics.2021.08.001}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pittamgallois198}{}}%
-Pittam, J., \& Gallois, C. (1986). Predicting impressions of speakers from voice quality: Acoustic and perceptual measures. \emph{Journal of Language and Social Psychology}, \emph{5}(4), 233--247.
+Pittam, J., \& Gallois, C.
+(1986).
+Predicting {I}mpressions of {S}peakers from {V}oice {Q}uality: {A}coustic and {P}erceptual {M}easures.
+\emph{Journal of Language and Social Psychology}, \emph{5}(4), 233--247.
+\url{https://doi.org/10.1177/0261927X8600500401}
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2024). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+R Core Team. (2024). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
@@
 \emph{British Journal of Psychology}, \emph{102}(4), 868--883.
+\url{https://doi.org/10.1111/j.2044-8295.2011.02051.x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-shribergetal1997}{}}%
-Shriberg, E. E., Bates, R., \& Stolcke, A. (1997). A prosody only decision-tree model for disfluency detection. \emph{Fifth European Conference on Speech Communication and Technology}.
+Shriberg, E.
+E., Bates, R., \& Stolcke, A.
+(1997).
+A prosody only decision-tree model for disfluency detection.
+\emph{Fifth European Conference on Speech Communication and Technology}.
+\url{https://doi.org/10.21437/eurospeech.1997-626}
 
 \leavevmode\vadjust pre{\hypertarget{ref-shriberglickley1993}{}}%
-Shriberg, E. E., \& Lickley, R. J. (1993). Intonation of clause-internal filled pauses. \emph{Phonetica}, \emph{50}(3), 172--179.
+Shriberg, E. E., \& Lickley, R. J. (1993). Intonation of {C}lause-{I}nternal {F}illed {P}auses. \emph{Phonetica}, \emph{50}(3), 172--179. \url{https://doi.org/10.1159/000261937}
 
 \leavevmode\vadjust pre{\hypertarget{ref-smithclark1993}{}}%
-Smith, V. L., \& Clark, H. H. (1993). On the course of answering questions. \emph{Journal of Memory and Language}, \emph{32}(1), 25--38.
+Smith, V. L., \& Clark, H. H. (1993). On the {C}ourse of {A}nswering {Q}uestions. \emph{Journal of Memory and Language}, \emph{32}(1), 25--38. \url{https://doi.org/10.1006/jmla.1993.1002}
 
 \leavevmode\vadjust pre{\hypertarget{ref-souzamarkman2013}{}}%
-Souza, A. L., \& Markman, A. B. (2013). Foreign accent does not influence cognitive judgments. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{35}.
+Souza, A.
+L., \& Markman, A.
+B.
+(2013).
+Foreign accent does not influence cognitive judgments.
+\emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{35}.
+\url{https://doi.org/escholarship.org/uc/item/8hd9v4ff}
 
 \leavevmode\vadjust pre{\hypertarget{ref-stocker2017}{}}%
-Stocker, L. (2017). The impact of foreign accent on credibility: An analysis of cognitive statement ratings in a swiss context. \emph{Journal of Psycholinguistic Research}, \emph{46}, 617--628.
+Stocker, L.
+(2017).
+The {I}mpact of {F}oreign {A}ccent on {C}redibility: {A}n {A}nalysis of {C}ognitive {S}tatement {R}atings in a {S}wiss {C}ontext.
+\emph{Journal of Psycholinguistic Research}, \emph{46}, 617--628.
+\url{https://doi.org/10.1007/s10936-016-9455-x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ulemanetal2008}{}}%
-Uleman, J. S., Adil Saribay, S., \& Gonzalez, C. M. (2008). Spontaneous inferences, implicit impressions, and implicit theories. \emph{Annu. Rev. Psychol.}, \emph{59}, 329--360.
+Uleman, J.
+S., Adil Saribay, S., \& Gonzalez, C.
+M.
+(2008).
+Spontaneous {I}nferences, {I}mplicit {I}mpressions, and {I}mplicit {T}heories.
+\emph{Annu.
+Rev.
+Psychol.}, \emph{59}, 329--360.
+\url{https://doi.org/10.1146/annurev.psych.59.103006.093707}
 
@@
 \emph{Journal of Articles in Support of the Null Hypothesis}, \emph{17}(2).
+https://doi.org/\href{https://doi.org/\%0910.48350/152025}{10.48350/152025}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
 
@@
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., \ldots{} Yutani, H.
+D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
+L., Miller, E., Bache, S.
+M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
+P., Spinu, V., \ldots{} Yutani, H.
 (2019).

### 2024-12-12 analysis/data-analysis.R

@@ -138,7 +138,7 @@ tests_questionnaires[[4]] <- t.test(langatt_native$affect, langatt_nonnative$aff
 tests_questionnaires[[5]] <- t.test(langatt_native$status, langatt_nonnative$status, paired = TRUE)
 tests_questionnaires[[6]] <- t.test(langatt_native$solidarity, langatt_nonnative$solidarity, paired = TRUE)
 tests_questionnaires[[7]] <- t.test(langatt_native$trustworthy, langatt_nonnative$trustworthy, paired = TRUE)
-names(tests_questionnaires) <- c("Comprehensibility", "Accent", "Fluency", "Affect", "Status", "Solidarity", "Trustworthy")
+names(tests_questionnaires) <- c("Comprehensibility", "Accentedness", "Fluency", "Affect", "Status", "Solidarity", "Trustworthiness")
 
 # # table for report
 # # idea from https://stackoverflow.com/questions/21840021/grabbing-certain-results-out-of-multiple-t-test-outputs-to-create-a-table
@@ -151,13 +151,15 @@ tab6 <- sapply(tests_questionnaires, function(x) {
     p.value = x$p.value,
     x$estimate)
 }) %>% t() %>% cbind(tests = dimnames(.)[[1]]) %>% as_tibble() %>%
-  mutate(across(1:6,as.numeric)) %>% mutate(across(1:6,round, 2)) %>% mutate(p.value = "< .001") %>%
+  mutate(across(1:6,as.numeric))  %>% mutate(p.value = as.numeric(p.value*7)) %>% 
+  mutate(across(c(1:4,6),~round(.,2) %>% format(., nsmall=2))) %>%  mutate(across(5,~round(.,3))) %>%
+  mutate(p.value = ifelse(p.value==0, "<.001", paste0("= ", p.value))) %>%                                                                                 
   mutate(
     col_name = paste("t(", df, ")", sep = ""),
     `95% CI` = paste("[", ci.lower, ", ", ci.upper, "]", sep = "")
   ) %>%
   pivot_wider(names_from = col_name, values_from = t) %>%
-  select(-c(df, ci.lower, ci.upper)) %>% gt() %>%
+  dplyr::select(-c(df, ci.lower, ci.upper)) %>% gt() %>%
   cols_move(
     columns = c(p.value, `95% CI`, `mean difference`),
     after = starts_with("t(")
[…]

### 2024-12-12 analysis/data-visualization.R

@@ -21,9 +21,10 @@ library(wesanderson)
 # re doing this code to be able to use apa_table and also to refer to it in-text
 
 tab5 <- dexp1lang_prereg %>%
-  select(c(18:24,38,39)) %>% mutate(speaker = ifelse(speaker=='native', 'Native Speaker', 'Non-native Speaker')) %>%
+  dplyr::select(c(18:24,38,39)) %>% mutate(speaker = ifelse(speaker=='native', 'Native Speaker', 'Non-native Speaker')) %>%
+  rename(trustworthiness = trustworthy) %>%
   rename_with(str_to_title) %>%
-  select(c("Speaker", "Easy", "Strong", "Affect", "Status", "Solidarity", "Trustworthy", "Fluent")) %>%
+  dplyr::select(c("Speaker", "Easy", "Strong", "Affect", "Status", "Solidarity", "Trustworthiness", "Fluent")) %>%
   rename(Comprehensibility = Easy,
          Accentedness = Strong,
          Fluency = Fluent
@@ -42,8 +43,8 @@ tab5 <- dexp1lang_prereg %>%
     sd_stat = sd(as.numeric(Status)),
     avg_sol = mean(as.numeric(Solidarity)),
     sd_sol = sd(as.numeric(Solidarity)),
-    avg_trust = mean(as.numeric(Trustworthy)),
-    sd_trust = sd(as.numeric(Trustworthy))
+    avg_trust = mean(as.numeric(Trustworthiness)),
+    sd_trust = sd(as.numeric(Trustworthiness))
   ) %>% 
   dplyr::mutate(
     Comprehensibility = paste(round(avg_easy, 2), paste("(", round(sd_easy,2), ")", sep = ""), sep = " "),
@@ -52,8 +53,8 @@ tab5 <- dexp1lang_prereg %>%
     Affect = paste(round(avg_aff, 2), paste("(", round(sd_aff,2), ")", sep = ""), sep = " "),
     Status = paste(round(avg_stat, 2), paste("(", round(sd_stat,2), ")", sep = ""), sep = " "),
     Solidarity = paste(round(avg_sol, 2), paste("(", round(sd_sol,2), ")", sep = ""), sep = " "),
-    Trustworthy = paste(round(avg_trust, 2), paste("(", round(sd_trust,2), ")", sep = ""), sep = " ")) %>%
[…]

### 2024-12-12 analysis/data-wrangling.R

@@ -47,7 +47,7 @@ library(here)
 
 # load all anonymised data
 
-dexp1 <- read_csv("../data/exp1/horse_race_exp1_rawdata.csv") %>% select(-c(1))
+dexp1 <- read_csv("../data/exp1/horse_race_exp1_rawdata.csv") %>% dplyr::select(-c(1))
 
 # wrangle separately bet data from questionnaire data
 
@@ -96,7 +96,7 @@ dexp1lang <- dexp1lang %>%
   pivot_longer(c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29, 31, 33, 35, 37, 39, 41, 43, 45, 47, 49), names_to = 'column', values_to = 'item') %>%
   pivot_longer(c(3:26), names_to = 'blah', values_to = 'score') %>%
   mutate(column = gsub('_question','',column), blah = gsub('_answer','',blah)) %>%
-  filter(column == blah) %>% filter(!score== 'null') %>% select(!c(column, blah)) %>%
+  filter(column == blah) %>% filter(!score== 'null') %>% dplyr::select(!c(column, blah)) %>%
   pivot_wider(names_from = item, values_from = score) %>%
   mutate(across(c(9:28), as.numeric)) %>%
   mutate(speaker = ifelse(speaker == 'native', 'native', 'nonnative'))
@@ -120,7 +120,7 @@ dexp1lang <- dexp1lang %>%
   )
 
 dexp1lang <- dexp1lang %>% 
-  select(!c(horse0, horse1, horse2, horse3, trial_type, trial_index))
+  dplyr::select(!c(horse0, horse1, horse2, horse3, trial_type, trial_index))
 
 # ppt 257 filled the questionnaire the other way around (native for non-native)
 # ppt 550 answered all questions as if for non-native (remove their data)
@@ -155,7 +155,7 @@ dexp1survey <- dexp1survey %>%
   pivot_longer(c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30, 32), names_to = 'column', values_to = 'item') %>%
   pivot_longer(c(2:17), names_to = 'blah', values_to = 'score') %>%
   mutate(column = gsub('_question','',column), blah = gsub('_answer','',blah)) %>%
-  filter(column == blah) %>% filter(!score== 'null') %>% select(!c(column, blah)) %>%
[…]

### 2024-12-12 analysis/data-analysis.R
tidy scripts

@@ -37,28 +37,6 @@ t.test(langatt_native$exposure, langatt_nonnative$exposure, paired = TRUE) # exp
 ## so the average is 25
 ## fix: do not include it
 ## additionally: we want to model nonetheless the variance by effect
-## lme4 does not work well with sum coding, RSO stats UGent offers the following alternative:
-
-
-# dexp1bet_prereg$flue_nat <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
-#                                       dexp1bet_prereg$speaker == "native")
-# dexp1bet_prereg$flue_non <- 1 * (dexp1bet_prereg$delivery == "fluent" & 
-#                                       dexp1bet_prereg$speaker == "nonnative")
-# dexp1bet_prereg$dis_nat <- 1 * (dexp1bet_prereg$delivery != "fluent" & 
-#                                       dexp1bet_prereg$speaker == "native")
-# 
-# exp1_mdlbet_max <- lmer(
-#   raw_money ~ delivery_cont * speaker_cont +
-#     (-1 + flue_nat + flue_non + dis_nat | ppt) +
-#     (1 | horse),
-#   data = dexp1bet_prereg, 
-#   control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=2e5))
-# )
-# 
-# summary(exp1_mdlbet_max)
-# hist(resid(exp1_mdlbet_max))
-
-# singular fit
 
 mdlbet_m1 <- lmerTest::lmer(
   raw_money ~ delivery_cont * speaker_cont +
@@ -151,8 +129,8 @@ tab6 <- sapply(tests_questionnaires, function(x) {
     p.value = x$p.value,
     x$estimate)
 }) %>% t() %>% cbind(tests = dimnames(.)[[1]]) %>% as_tibble() %>%
-  mutate(across(1:6,as.numeric))  %>% mutate(p.value = as.numeric(p.value*7)) %>% 
-  mutate(across(c(1:4,6),~round(.,2) %>% format(., nsmall=2))) %>%  mutate(across(5,~round(.,3))) %>%
+  mutate(across(1:6,as.numeric))  %>% mutate(p.value = as.numeric(p.value*7)) %>%  # p-value correction
+  mutate(across(c(1:4,6),~round(.,2) %>% format(., nsmall=2))) %>%  mutate(across(5,~round(.,3))) %>% 
[…]

### 2024-12-12 analysis/data-visualization.R

@@ -1,7 +1,7 @@
 # Note: if running on its own, remove one period
 # Otherwise, it is set for running on the manuscript
 source('../analysis/data-wrangling.R')
-source('../analysis/utils.R') # for violin plot graphs
+source('../analysis/utils.R') # for violin plot graphs, from Glasgow TeachR team
 
 library(psych)
 library(optimx)
@@ -187,55 +187,39 @@ tab4[c(2,4), 1] <- ""
 
 # viz for poster presentations
 
-fig1 <- dexp1bet_prereg %>%
-  mutate(delivery = ifelse(delivery == 'fluent', 'Fluent', 'Disfluent'), speaker = ifelse(speaker == 'native', 'Native', 'Non-native'))%>%
-  ggplot(., aes (x = delivery, y = as.numeric(scaled_money), fill = speaker)) +
-  geom_split_violin(alpha = .4, trim = FALSE)  +
-  geom_boxplot(width = .2, alpha = .6, fatten = NULL, show.legend = FALSE) +
-  stat_summary(fun.data = "mean_se", geom = "pointrange", show.legend = F, 
-               position = position_dodge(.175))  +
-  scale_x_discrete(name = "Manner of Delivery", labels = c("Disfluent", "Fluent")) +
-  scale_y_continuous(name = "Money bet",
-                     breaks = seq(0, 100, 20), 
-                     limits = c(0, 100)) +
-  scale_fill_brewer(palette = "Dark2", name = "Speaker's linguistic background") + # need to decide color palette based on poster palette
-  theme_minimal()
+# fig1 <- dexp1bet_prereg %>%
+#   mutate(delivery = ifelse(delivery == 'fluent', 'Fluent', 'Disfluent'), speaker = ifelse(speaker == 'native', 'Native', 'Non-native'))%>%
+#   ggplot(., aes (x = delivery, y = as.numeric(scaled_money), fill = speaker)) +
+#   geom_split_violin(alpha = .4, trim = FALSE)  +
+#   geom_boxplot(width = .2, alpha = .6, fatten = NULL, show.legend = FALSE) +
+#   stat_summary(fun.data = "mean_se", geom = "pointrange", show.legend = F, 
+#                position = position_dodge(.175))  +
+#   scale_x_discrete(name = "Manner of Delivery", labels = c("Disfluent", "Fluent")) +
+#   scale_y_continuous(name = "Money bet",
+#                      breaks = seq(0, 100, 20), 
[…]

### 2024-12-12 analysis/data-wrangling.R

@@ -64,14 +64,6 @@ dexp1bet <- dexp1 %>%
   pivot_longer(c(8:11), names_to = "order", values_to = "raw_money") %>%
   filter(order == order_filter)
 
-# RSO stats help UGent suggests scaling money bet (previous issue: 0 variance for participant in LME, arguably because everyone is spending 100)
-
-dexp1bet <- dexp1bet %>%
-  group_by(ppt) %>%
-  mutate(total_spent = sum(as.numeric(raw_money))) %>%
-  mutate(scaled_money = ((raw_money * 100)/total_spent))
-
-
 # LANGUAGE ATTITUDES QUESTIONNAIRE
 
 

### 2024-12-12 stimuli/frequency-check.R
remove old files

@@ -1,20 +1,0 @@
-# checks for our stimuli created
-
-stimuli <- read_excel('./stimuli/stimuli-creation.xlsx', sheet = 'ENG-version')
-stimuli <- stimuli %>%
-  filter(language == 'DUT') %>%
-  select(., c(`noun-predictable`)) %>%
-  mutate(Word = gsub("een ", "", `noun-predictable`))
-
-stimuli_freqs <- left_join(stimuli, subtlex, by = 'Word') %>% select(., c(Word, Zipf))
-
-stimuli_freqs %>%
-  summarise(
-    avg = mean(Zipf, na.rm = TRUE),
-    maximum = max(Zipf, na.rm = TRUE),
-    minimum = min(Zipf, na.rm = TRUE),
-    sd = sd(Zipf, na.rm = TRUE)
-  )
-
-plot(density(stimuli_freqs$Zipf, na.rm = TRUE))
-  

### 2024-12-12 analysis/data-wrangling.R
organise

@@ -47,7 +47,7 @@ library(here)
 
 # load all anonymised data
 
-dexp1 <- read_csv("../data/exp1/horse_race_exp1_rawdata.csv") %>% dplyr::select(-c(1))
+dexp1 <- read_csv("../data/horse_race_exp1_rawdata.csv") %>% dplyr::select(-c(1))
 
 # wrangle separately bet data from questionnaire data
 

### 2024-12-12 analysis/data-visualization.R
anonymise

@@ -129,7 +129,7 @@ dexp1lang_prereg %>%
 # proportion money distributed
 
 tab4 <- dexp1bet_prereg %>%
-  dplyr::select(c(4,11,51)) %>%
+  dplyr::select(c(4,11,49)) %>%
   rename_with(str_to_title) %>%
   rename(Money = Raw_money) %>%
   mutate(Delivery = factor(Delivery, levels = c("fluent", "disfluent"))) %>%
